### 2018-02-05 latex/paper.tex
initial commit

\documentclass[12pt, twoside, letterpaper]{article}
\usepackage[margin=0.7in]{geometry}
\usepackage[parfill]{parskip}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{authblk}
\usepackage{charter}
\usepackage[numbers]{natbib}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{titlesec}

\bibliographystyle{unsrtapalike}

% title font size
\titleformat*{\section}{\normalsize\bfseries}
\titleformat*{\subsection}{\normalsize\bfseries}

% line spacing
\renewcommand{\baselinestretch}{1.1}

% new commands
\newcommand{\PIP}{PIP\textsubscript{2}}
\newcommand{\sigd}{$\beta$\textit{2tub}-SigD}
\newcommand{\sktl}{\textit{sktl}}
\renewcommand*{\Affilfont}{\footnotesize \normalfont}
\renewcommand*{\Authfont}{\normalsize}

\title{\bfseries\large Phosphatidylinositol 4,5-bisphosphate regulates cilium transition zone maturation in Drosophila}
\author[1,2]{Alind Gupta}
\author[1,2]{Julie A. Brill}
\affil[1]{Department of Molecular Genetics, University of Toronto, Toronto, ON M5S 1A8, Canada}
\affil[2]{Program in Cell Biology, Hospital for Sick Children, Toronto, ON M5G 1X8, Canada}
\date{}

\begin{document}
\maketitle
\raggedright
\begin{abstract}
  \vspace*{-0.7em}
  Cilia are sensory organelles that are important for human development
  and physiology.
  A large number of genetic disorders affecting cilia are associated with
  mutations in proteins that localize to the transition zone (TZ),
  a structure at the base of cilia required for ciliogenesis and
  regulation of trafficking in and out of the cilium.
  Here, we report that the membrane lipid phosphatidylinositol
  4,5-bisphosphate(\PIP{}) is essential for proper maturation and function
  of TZs in the male \textit{Drosophila melanogaster} germline.
  Reduction of cellular \PIP{} levels by expression of the
  \textit{Salmonella} phosphoinositide phosphatase SigD or mutation of
  the type I phosphatidylinositol phosphate kinase Skittles (Sktl)
  induces hyperelongation of TZs following their docking at the plasma
  membrane.
  We provide evidence showing that these hyperelongated TZs are functionally
  defective, and that the Exo84 mutant \textit{onion rings} decouples the
  transition zone hyperelongation from the role for \PIP{} in cilium-membrane
  tethering.
  Our observations reveals a requirement for \PIP{} at the base of cilia
  in regulating TZ length and function.
\end{abstract}

\section{Introduction}
Cilia are sensory organelles present on almost all cells in the human body
\citep{satir2010primary}.
They function primarily by providing sensory inputs to cells, but can
also function as motile propellers in certain cells
\citep{bloodgood2010sensory}.
Consistent with their pervasiveness and importance in cell signalling,
defects in cilium formation are associated with various genetic disorders
known collectively as ciliopathies, which can manifest as
neurological disorders \citep{valente2014primary},
skeletal abnormalities \citep{hammarsjo2017novel, waters2011ciliopathies}
and infertility \citep{inaba2016sperm}.

A large number of ciliopathies are linked to mutations in proteins that
localize to the cilium transition zone (referred to herein as TZ).
The TZ is the proximal-most compartment of the cilium which
acts as a diffusion barrier that regulates the
bi-directional transport of protein and lipid cargo at the base of the cilium,
and is essential for cilium formation and function in cell signalling.
The conserved TZ protein CEP290, for example, is mutated in at least
five distinct ciliopathies, and is essential for cilium formation in both humans
and Drosophila.
Although the composition of TZs is well understood, processes underlying
transition zone maturation and cell membrane anchoring are not as well-studied.
In particular, why mutations in the same TZ protein can give rise to a plethora
of phenotypic outputs is less understood, and may point at modifier mutations
or mutations that are not as severe as to entirely abolish ciliogenesis.

In the male Drosophila germline, nascent TZs first assemble on basal bodies
during early pre-meiotic G2 phase (spermatocytes), anchor directly to the plasma membrane.
This is followed by establishment of cilium-membrane connections and a
ciliary membrane that persists during meiosis \citep{riparbelli2012assembly}
through a poorly understood mechanism
involving microtubule rearrangements \citep{gottardo2013cilium}.
Ciliogenesis begins with the assembly of TZ proteins at the tips of
the nascent basal body.
This is followed by the anchoring of the TZ to the membrane and
establishment of a compartmentalized space bounded by the ciliary membrane
and the TZ.
TZ maturation has been described in
\textit{Paramecium} \citep{aubusson2015transition}
\textit{Caenorrhabditis elegans} \citep{serwas2017centrioles} and
\textit{D. melanogaster} \citep{gottardo2013cilium}
and involves TZ elongation.
Possibly, this is similar to the initial steps of TZ assembly and reorganization
in well-studied vertebrate cilia.

Here, we show that the lipid phosphatidylinositol 4,5-bisphosphate (\PIP{})
is essential for proper TZ maturation in developing \textit{Drosophila melanogaster}
male germ cells.
Reduction of cellular \PIP{} by expression of the bacterial PIP phosphatase SigD
or by inactivation of the PIP 5-kinase Skittles (Sktl) that localizes to cilia
induces longer than normal TZs.
These hyperelongated TZs show hallmarks of aberrant function similar to those
found in previously studied TZ mutants, including loss of cilium-membrane associations.
We also find that the \textit{onion rings} allele of
ciliopathy-associated exocyst protein Exo84/EXOC8 decouples TZ hyperelongation
from loss of cilium-membrane contacts.
Our results suggest that the plasma membrane lipid \PIP{} regulates TZ length,
maturation and function, acting to support ciliogenesis.

\section{Results}

\subsection{\PIP{} is essential for transition zone maturation}
To investigate whether reduction of cellular \PIP{} affects ciliogenesis in the
Drosophila male germline,
we used transgenic flies expressing the Salmonella phosphoinositide phosphatase SigD
under $\beta$2-tubulin promoter (referred to herein as \sigd{}),
which is uniquely expressed in spermatocytes
\citep{wei2008depletion, fabian2010phosphatidylinositol}.
We previously showed that expression of this construct
induced male sterility due in part to defects in flagellar biosynthesis \citep{wei2008depletion}.
We examined the localization of fluorescently-labelled centriolar/basal body protein
Ana1 (Cep295) \citep{goshima2007genes, blachon2009proximal}
and the TZ protein Cep290 \citep{basiri2014migrating}
in wild-type control and \sigd{} spermatocytes.
As shown in Figure 1A, nascent TZs marked with Cep290-GFP assemble normally in \sigd{} cells
but grow to much longer lengths compared to wild-type control cells.
TZ hyperelongation was a highly penetrant phenotype (\textgreater 90\%)
and showed high intra-cyst correlation.
This phenotype was not specific to Cep290;
all TZ markers examined showed hyperelongation, including
acetylated tubulin \citep{gottardo2013cilium},
Chibby \citep{enjolras2012drosophila} and
MKS \citep{slaats2015mks1, vieillard2016transition} proteins (Figure 1).
Hyperelongated transition zones persisted through meiosis.
Despite TZ hyperlongation, however, axonemes were able to elongate post-meiosis (Figure 1).
As we showed previously, the ultrastructure of these axonemes was frequently aberrant,
either lacking symmetry completely or containing triplet microtubules instead of doublets
\citep{wei2008depletion}.

\subsection{The type I PIP kinase Skittles localizes to centrioles and regulates TZ length}
Although numerous studies have shown that \PIP{} is the major substrate for SigD
when expressed in eukaryotic cells
\citep{terebiznik2002elimination, zhou2001salmonella, sengupta2013depletion},
SigD can dephosphorylate other PIPs \textit{in vitro}
\citep{norris1998sopb}.
To address whether TZ hyperelongation observed in \sigd{} represented
a physiologically relevant phenotype in response to decreased \PIP{},
we attempted to rescue it by
co-expressing fluorescently-tagged full-length Skittles (Sktl) with SigD
under the same promoter.
We found that Sktl expression was able to suppress TZ elongation in a cilium-autonomous
manner (Figure 2).
We also found that \textit{sktl} clones showed penetrant TZ hyperelongation when
marked with Unc-GFP, a ciliary marker \citep{baker2004mechanosensory}.

Since Sktl expression lead to cilium-autonomous rescue,
we investigated whether Sktl could localize to centrioles or cilia in the Drosophila germline.
Similar to the human PIPKI$\gamma$ isoform \citep{xu2014pipkigamma},
we found that Skittles localizes to basal bodies in the Drosophila male germline.
As shown in Figure 2, Drosophila PIP5Ks arose from the recent duplication of
the ancestral PIP5K gene, and are not orthologous to specific vertebrate PIP5K isoforms.
Skittles has diverged more than the paralogous PIP5K59B gene, and seems
to be functionally related to PIPKI$\gamma$ in its roles at cilia.
However, unlike the human PIPKI$\gamma$, which functions to license TZ assembly
by promoting CP110 uncapping from basal bodies \citep{xu2016phosphatidylinositol},
our results suggest that Skittles functions in
regulating TZ length in the Drosophila male germline
but is dispensable for its assembly.
The localization of Cp110 is unaffected in \sigd{} (supplementary figure 1).

\subsection{Hyperelongated transition zones show signs of functional defects}
While shorter spermatocyte TZs have been observed in Drosophila mutants of TZ proteins
\citep{vieillard2016transition, pratt2016drosophila},
no genetic manipulation has been reported to induce hyperelongated TZs. 
We sought to examine whether TZ hyperelongation due to SigD expression
affected TZ function.
During germ cell elongation following meiosis, the TZ detaches from
the basal body and migrates along the growing axoneme, maintaining a ciliary compartment
at the distal-most ~5$\mu$m where tubulin is presumably incorporated into the axoneme.
We found that
TZs that assembled in \sigd{} cells are non-migratory despite the growth of the
axoneme and the cell membrane, as shown by Unc and Cep290 localization.
We previously described ``comet-shaped'' localization of Unc-GFP in these cells,
and we find that these hyperelongated Unc signals persist into cellular elongation.

Another phenotype that is consistent with this hypothesis is
the observation of the centriolar protein Ana1 localizing to the distal tips of
hyperelongated TZs.
TZ-distal Ana1 localization is observed at a relatively low penetrance
and high intra-cyst correlation.
This is possibly related to stochastic SigD expression in cysts.
We found that treatment of germ cells with Paclitaxel as in \citep{riparbelli2013unique}
could increase the penetrance of this phenotype.
Paclitaxel treatment stabilizes microtubules and is thought to disrupt TZ maturation
by interrupting microtubule rearrangements, and similarly induces much longer cilia.
Paclitaxel treatment alone did not induce this phenotype in wild-type controls in our hands
at varying concentrations (binomial probability < 0.001 with 5\% penetrance),
suggesting that loss of \PIP{} acts upstream of or prior to microtubule rearrangement.
Although we can not show a definitive reason for this, we expect that this is due to
the axoneme maintaining some centriolar fate.
We had previously shown the presence of microtubule triplets in axonemes assembled in \sigd{}
cells.
These are also observed in Taxol-treated cells \citep{riparbelli2013unique}.
It is possible that the TZ defect allows C-tubules and some centriolar proteins
to migrate with it to the distal end.
We did not observe this behaviour with Asterless,
a migratory protein that localizes to the outer
ring of centrioles (Figure 3).

\subsection{The \textit{onion rings} mutant decouples defects found in cells with reduced levels of \PIP{}}
A heterozygous mutation in the human \textit{EXOC8},
the human ortholog of yeast Exo84, is linked to
Joubert syndrome \citep{dixon2012exome}.
We previously showed that male flies homozygous for the \textit{onion rings}
(\textit{onr}) mutant of Drosophila Exo84 were sterile, with phenotypes
similar to \sigd{} \citep{wei2008depletion}.
Exo84 is a component of the octameric exocyst complex, which binds
\PIP{} and regulates membrane trafficking at the plasma membrane.
We found that the \textit{onr} mutant did not display hyperelongated TZs (Figure 5).

Since exocyst regulates membrane trafficking and cilium formation,
we examined whether cilium-associated membrane dynamics were affected in \sigd{}
or \textit{onr} mutants similar to \textit{dila; cby} mutants
\citep{vieillard2016transition}.
We found that while TZs in \sigd{} and \textit{onr} cells anchored properly
to the plasma membrane, they were unable to either establish or maintain
membrane connections, and were rendered cytoplasmic (Figure 5) similar to
\textit{dila; cby} mutants.
Although we were not able to determine the localization of the Exo84 due to the
lack of available antibodies,
we found that Sec6 localized to the plasma membrane as expected.
Our results suggest that the exocyst may act downstream of \PIP{} to
enhance cilium-membrane associations, and that TZ hyperelongation and loss of
membrane-cilium association are genetically separable phenotypes.

\section{Discussion}

In this study, we show that the lipid \PIP{} is essential for proper
transition zone maturation in the male Drosophila germline.
Reduction of cellular \PIP{} by expression of the bacterial PIP
phosphatase SigD or inactivation of the type I PIP kinase Skittles
causes developing TZs to elongate excessively.

We had previously shown that reduction of \PIP{} by SigD expression
affected flagellar biogenesis and axoneme structure
\citep{wei2008depletion}.
We also showed aberrant ``comet-shaped'' localization of Unc that
failed to assemble TZ-associated puncta in some cases.
Here, we show that this occurs prior to meiosis,
is not an artefact due to cytokinesis defects
and do not represent an inability of the axoneme to grow.
Rather,

It has previously been suggested that LCCS3 might represent a ciliopathy.
PIPKI$\gamma$ is linked to LCCS3 with many features reminiscent
of ciliopathies, such as micrognathia, and a role for the LCCS1 protein
Gle3 in cilia.
In addition, all three human PIPKI isoforms are highly expressed in testes
and PIPKI$\alpha$ and PIPKI$\beta$ are important for fertility in mice
\citep{hasegawa2012phosphatidylinositol}.

\section{Methods}
\subsection{Transgenic flies}
Drosophila stocks were cultured on cornmeal molasses agar medium at 25$^{\circ}$C
and 50\% humidity.
Stocks expressing $\beta$\textit{2tub}::SigD and $\beta$\textit{2tub}::YFP-Sktl
were described previously \citep{wei2008depletion, fabian2010phosphatidylinositol}.
$\beta$\textit{2tub}::mCherry-Sktl\textsuperscript{kinase-dead}
was generated by Gordon Polevoy.
Ana1-tdTomato (chromosome 2) and Cep290-GFP (chromosome 3) were provided
by T. Avidor-Reiss \citep{basiri2014migrating}.
Unc-GFP was originally provided by M. Kernan \citep{baker2004mechanosensory}.
Stocks expressing GFP-tagged Chibby, B9d1, B9d2, Cc2d2a and Mks1 were generously
provided by B. Durand \citep{enjolras2012drosophila, vieillard2016transition}.
The \textit{onr} mutant was described previously \citep{giansanti2015exocyst}.
Stocks for generating \textit{sktl}\textsuperscript{2.3} clones were originally provided by
A. Guichet \citep{gervais2008pip5k}.
\textit{w}\textsuperscript{1118} was used as the wild-type control.

\subsection{Antibodies}
The following primary antibodies were used for immunofluorescence
at the indicated concentrations - 
rabbit $\alpha$-Tulp (gift from W. McGinnis \citep{ronshaugen2002structure}), 1:500; 
chicken $\alpha$-GFP IgY (abcam) 1:1000;
rat $\alpha$-RFP IgG (5F8, ChromoTek), 1:1000;
rabbit $\alpha$-Sktl (courtesy of P. Raghu), 1:500;
Secondary antibodies were Alexa 488- and Alexa 568-conjugated
$\alpha$-mouse, $\alpha$-rabbit and $\alpha$-chicken
IgG (Molecular Probes) at 1:1000.
DAPI was used to label chromatin at 1:1000.

\subsection{Fluorescence microscopy}
For live imaging, testes were dissected in phosphate bufferd saline (PBS),
transferred to a polylysine-coated glass slide in a drop of PBS,
ruptured using a syringe needle and
squashed under a glass coverslip using Kimwipes.
The edges of the coverslip were sealed with nail polish
and the specimen was visualized immediately using a fluorescence microscope.

For immunochemistry, testes were dissected in PBS,
transferred to a polylysine-coated gladd slide in a drop of PBS,
ruptured with a needle, squashed and frozen in liquid nitrogen for 5 minutes.
The slides were transferred to ice-cold methanol for 5-10 minutes.
For staining with the $\alpha$-skittles antibody, pre-fixation in methanol
was omitted to preserve cellular membranes.
Samples were fixed in 4\% paraformaldehyde in PBS,
permeabilized and blocked in PBS with 0.1\% Triton-X and 0.3\% bovine
serum albumin and incubated with primary antibodies overnight at 4$^{\circ}$C.
followed by three 5-minute washes with PBS and 1 hour incubation
with secondary antibodies and three 5-minute washes with PBS.
Samples were mounted in Dako (Agilent) and imaged with Leica widefield microscope
or Nikon A1R scanning confocal microscope (SickKids imaging facility).

\subsection{Statistical methods}
Statistical analysis and graphing was performed using R.
Statistical tests for ``absence of phenotype'' were computed under a
hypothesis assuming binomial likelihood.
All $t$-tests were unpaired and two-sided.
A significance level of 0.01 was fixed \textit{a priori} for all analysis.

\section{Author contributions}
A.G. and J.A.B. conceived the project.
A.G. performed all the experiments and wrote the manuscript.
J.A.B. supervised the project.

\section{Acknowledgements}
We thank Brian Ciruna for input on results.

\bibliography{bibttc}

\end{document}

### 2018-02-05 latex/make.sh

@@ -1,0 +1,5 @@
+pdflatex paper.tex > /dev/null  
+bibtex paper > /dev/null
+pdflatex paper.tex > /dev/null 
+pdflatex paper.tex > /dev/null 
+date

### 2018-02-06 figures/figure-1/plot1.R
initial commit

@@ -1,0 +1,89 @@
+#png(filename="germlate.png", width=6.5, height=6,units="in", res=600)
+
+# import data
+df <- read.csv('fig1quantification.csv', header=TRUE)
+df <- cbind(df[,6], df[,5], df[,8], df[,7])
+
+addNoise <- function(mtx) {
+    if (!is.matrix(mtx)) mtx <- matrix(mtx, byrow = TRUE, nrow = 1)
+    random.stuff <- matrix(runif(prod(dim(mtx)), min = -0.0001, max = 0.01), nrow = dim(mtx)[1])
+    random.stuff + mtx
+}
+
+df <- addNoise(df)
+
+library(RColorBrewer)
+
+cols <- brewer.pal(9,"Set1")[c(1,2)]
+
+par(bty="n",
+    mar=c(4, 4, 3, 3),  # plot margins b-l-t-r
+    las=1,              # horizontal labels
+    tcl=-.25,           # tick length
+    font.main=1,        # plain font
+    mgp=c(2.5, 0.5, 0),  # axis spacings
+    cex.lab=1.1,
+    cex.axis=1.1,
+    ps=12
+)
+
+
+xat <- c(1,
+         2,
+         3,
+         4)
+b <- boxplot(df,
+             xaxt="n",       # no x-axis
+             yaxt="n",
+             boxwex=0.45,    # boxwidth
+             lty=1,          # line type, 1 = solid
+             staplewex=0,    # no staples
+             log="",         # no log scaling
+             ylim=c(0.6, 1.65),
+             at=xat,
+             border=cols,
+             lwd=2,
+             outline=FALSE)          # line weight
+
+stripchart(apply(df, 2, as.list),
+           vertical=TRUE,
+           method="jitter",
+           add=TRUE,
+           pch=20,
+           cex=0.4,
+           col=cols,
+           at=xat,
+           jitter=0.05)
+
+title("Cep290 and Ana1 lengths (late G2 phase)", font.main=1, cex.main=1.3, line=0.7)
+title(ylab=expression(paste("Length (",italic("μ"), "m)", sep="")), line=2.2)
+
+tlab=c(1.6, 3.7)+0.3
+
[…]

### 2018-02-06 figures/figure-1/plot2.R

@@ -1,0 +1,82 @@
+#png(filename="germlate.png", width=6.5, height=6,units="in", res=600)
+
+# import data
+df <- read.csv('fig1quantification.csv', header=TRUE)
+df <- cbind(df[,2], df[,1], df[,4], df[,3])
+
+addNoise <- function(mtx) {
+    if (!is.matrix(mtx)) mtx <- matrix(mtx, byrow = TRUE, nrow = 1)
+    random.stuff <- matrix(runif(prod(dim(mtx)), min = -0.001, max = 0.05), nrow = dim(mtx)[1])
+    random.stuff + mtx
+}
+
+df <- addNoise(df)
+
+library(RColorBrewer)
+
+cols <- brewer.pal(9,"Set1")[c(1,2)]
+
+par(bty="n",
+    mar=c(3, 4, 3, 3),  # plot margins b-l-t-r
+    las=1,              # horizontal labels
+    tcl=-.25,           # tick length
+    font.main=1,        # plain font
+    mgp=c(2.5, 0.5, 0),  # axis spacings
+    cex.lab=1.1,
+    cex.axis=1.1,
+    ps=12
+)
+
+
+xat <- c(1,
+         2,
+         3,
+         4)
+b <- boxplot(df,
+             xaxt="n",       # no x-axis
+             yaxt="n",
+             boxwex=0.45,    # boxwidth
+             lty=1,          # line type, 1 = solid
+             staplewex=0,    # no staples
+             log="",         # no log scaling
+             ylim=c(0.3, 0.6),
+             at=xat,
+             border=cols,
+             lwd=2,
+             outline=FALSE)          # line weight
+
+stripchart(apply(df, 2, as.list),
+           vertical=TRUE,
+           method="jitter",
+           add=TRUE,
+           pch=20,
+           cex=0.4,
+           col=cols,
+           at=xat,
+           jitter=0.05)
+
+title("Cep290 and Ana1 lengths (early G2 phase)", font.main=1, cex.main=1.3, line=0.7)
+title(ylab=expression(paste("Length (",italic("μ"), "m)", sep="")), line=2.2)
+
+tlab=c(1.6, 3.7)+0.3
+
[…]

### 2018-02-06 figures/figure-2/plot.R

@@ -1,0 +1,87 @@
+#png(filename="cepgerm.png", width=6.5, height=6,units="in", res=600)
+
+# import data
+df <- read.csv('quantification.csv', header=TRUE)
+df <- cbind(df[,2], df[,4], df[,6], df[,1], df[,3], df[,5])
+
+addNoise <- function(mtx) {
+    if (!is.matrix(mtx)) mtx <- matrix(mtx, byrow = TRUE, nrow = 1)
+    random.stuff <- matrix(runif(prod(dim(mtx)), min = -0.0001, max = 0.01), nrow = dim(mtx)[1])
+    random.stuff + mtx
+}
+
+df <- addNoise(df)
+
+library(RColorBrewer)
+
+cols <- brewer.pal(9,"Set1")[c(1,2,3)]
+
+par(bty="n",
+    mar=c(3, 4, 3, 3),  # plot margins b-l-t-r
+    las=1,              # horizontal labels
+    tcl=-.25,           # tick length
+    font.main=1,        # plain font
+    mgp=c(2.5, 0.5, 0),  # axis spacings
+    cex.lab=1.1,
+    cex.axis=1.1,
+    ps=12
+)
+
+
+xat <- c(1,
+         2,
+         3,
+         4.5,
+         5.5,
+         6.5)
+b <- boxplot(df,
+             xaxt="n",       # no x-axis
+             yaxt="n",
+             boxwex=0.45,    # boxwidth
+             lty=1,          # line type, 1 = solid
+             staplewex=0,    # no staples
+             log="",         # no log scaling
+             ylim=c(0.5, 1.7),
+             at=xat,
+             border=cols,
+             lwd=2,
+             outline=FALSE
+)          # line weight
+
+stripchart(apply(df, 2, as.list),
+           vertical=TRUE,
+           method="jitter",
+           add=TRUE,
+           pch=20,
+           cex=0.4,
+           col=cols,
+           at=xat,
+           jitter=0.05)
+
+title("Cep290 and Ana1 lengths in spermatocytes\n (late G2 phase)", font.main=1, cex.main=1.3, line=0.2)
+title(ylab=substitute(paste("Length (μm)")), line=2.2)
+
[…]

### 2018-02-06 figures/figure-2/plot.R
updated

@@ -59,12 +59,12 @@ stripchart(apply(df, 2, as.list),
            jitter=0.05)
 
 title("Cep290 and Ana1 lengths in spermatocytes\n (late G2 phase)", font.main=1, cex.main=1.3, line=0.2)
-title(ylab=substitute(paste("Length (μm)")), line=2.2)
+title(ylab=expression(paste("Length (",italic("μ"), "m)", sep="")), line=2.2)
 
-axis(2, at=seq(0.6, 2, 0.2), labels=TRUE, col=NA, col.ticks=1, lwd=1)
-axis(1, labels=c("Cep290-GFP", "Ana1-tdTomato"), at=c(2, 0.92*(xat[5]+xat[6])/2), lwd.ticks=0)
-axis(1, at=c(0, ((xat[3] + xat[4])/2)), labels=FALSE, tck=-0.05)
-box(bty='L')
+axis(2, at=seq(0.6, 2, 0.2), labels=TRUE, col.ticks=1, lwd=1)
+axis(1, labels=c("Cep290-GFP", "Ana1-tdTomato"), at=c(2, 0.92*(xat[5]+xat[6])/2), lwd.ticks=0, lty=0, line=-0.8)
+axis(1, at=c(0, ((xat[3] + xat[4])/2)), labels=FALSE, tck=-0.05, col=0, lty=0)
+#box(bty='L')
 
 temp.labels = c("Control", "SigD", "SigD + Sktl")
 legend("topright", cex=0.9, col=cols, lty=1, lwd=2, temp.labels, bty="n")
@@ -82,6 +82,14 @@ lines(c(xat[4], xat[6]), c(yat, yat))
 lines(c(xat[4], xat[4]), c(yat+offset, yat))
 lines(c(xat[6], xat[6]), c(yat+offset, yat))
 text((xat[4] + xat[6])/2, yat-2*offset, expression(italic('N.S.')), cex=0.8)
+
+lines(xat[1:2], b$stats[3,1:2], lwd=0.7)
+lines(xat[2:3], b$stats[3,2:3], lwd=0.7)
+lines(xat[4:5], b$stats[3,4:5], lwd=0.7)
+lines(xat[5:6], b$stats[3,5:6], lwd=0.7)
+
+lines(c(xat[1], xat[3]), c(0.5,0.5))
+lines(c(xat[4], xat[6]), c(0.5,0.5))
 
 #dev.off()
 

### 2018-02-06 figures/figure-1/plot1.R
minor change to label placement

@@ -58,7 +58,7 @@ stripchart(apply(df, 2, as.list),
 title("Cep290 and Ana1 lengths (late G2 phase)", font.main=1, cex.main=1.3, line=0.7)
 title(ylab=expression(paste("Length (",italic("μ"), "m)", sep="")), line=2.2)
 
-tlab=c(1.6, 3.7)+0.3
+tlab=c(1.6, 3.7)+0.2
 
 axis(2, at=seq(0.6, 1.8, 0.2), labels=TRUE, col.ticks=1, lwd=1, lwd.ticks=1)
 
@@ -76,10 +76,10 @@ segments(xat[1], df[,1], xat[2], df[,2], lwd=0.1)
 segments(xat[3], df[,3], xat[4], df[,4], lwd=0.1)
 
 
-lines(c(xat[1], xat[3]), c(yat, yat))
-lines(c(xat[1], xat[1]), c(yat-offset, yat))
-lines(c(xat[3], xat[3]), c(yat-offset, (yat)))
-text((xat[1] + xat[3])/2, yat+2*offset, expression(italic('N.S.')), cex=0.8)
+#lines(c(xat[1], xat[3]), c(yat, yat))
+#lines(c(xat[1], xat[1]), c(yat-offset, yat))
+#lines(c(xat[3], xat[3]), c(yat-offset, (yat)))
+#text((xat[1] + xat[3])/2, yat+2*offset, expression(italic('N.S.')), cex=0.8)
 
 lines(c(xat[1]-0.25, xat[2]+0.25), c(0.52, 0.52), xpd=TRUE)
 lines(c(xat[3]-0.25, xat[4]+0.25), c(0.52, 0.52), xpd=TRUE)

### 2018-02-06 figures/figure-1/plot2.R

@@ -58,7 +58,7 @@ stripchart(apply(df, 2, as.list),
 title("Cep290 and Ana1 lengths (early G2 phase)", font.main=1, cex.main=1.3, line=0.7)
 title(ylab=expression(paste("Length (",italic("μ"), "m)", sep="")), line=2.2)
 
-tlab=c(1.6, 3.7)+0.3
+tlab=c(1.6, 3.7)+0.2
 
 axis(2, at=seq(0.3, 0.6, 0.1), labels=TRUE, col.ticks=1, lwd=1, lwd.ticks=1)
 

### 2018-02-06 figures/figure-2/plot.R

@@ -58,7 +58,7 @@ stripchart(apply(df, 2, as.list),
            at=xat,
            jitter=0.05)
 
-title("Cep290 and Ana1 lengths in spermatocytes\n (late G2 phase)", font.main=1, cex.main=1.3, line=0.2)
+title("Cep290 and Ana1 lengths\n (late G2 phase)", font.main=1, cex.main=1.3, line=0.2)
 title(ylab=expression(paste("Length (",italic("μ"), "m)", sep="")), line=2.2)
 
 axis(2, at=seq(0.6, 2, 0.2), labels=TRUE, col.ticks=1, lwd=1)

### 2018-02-07 latex/paper.tex
updated

@@
 
-In the male Drosophila germline, nascent TZs first assemble on basal bodies
+In the Drosophila male germline, nascent TZs first assemble on basal bodies
 during early pre-meiotic G2 phase (spermatocytes), anchor directly to the plasma membrane.
@@
 found in previously studied TZ mutants, including loss of cilium-membrane associations.
-We also find that the \textit{onion rings} allele of
-ciliopathy-associated exocyst protein Exo84/EXOC8 decouples TZ hyperelongation
-from loss of cilium-membrane contacts.
+We also find that the \textit{onion rings} allele of the
+ciliopathy-associated \textit{EXOC8} gene encoding the human Exo84
+decouples TZ hyperelongation from loss of cilium-membrane contacts.
 Our results suggest that the plasma membrane lipid \PIP{} regulates TZ length,
@@
 \textit{dila; cby} mutants.
-Although we were not able to determine the localization of the Exo84 due to the
+Although we were not able to determine the localization of Exo84 due to the
 lack of available antibodies,
-we found that Sec6 localized to the plasma membrane as expected.
+we found that Sec6 and Exo70 localized to the plasma membrane as expected,
+but were not enriched at the cilium.
 Our results suggest that the exocyst may act downstream of \PIP{} to
@@
 In this study, we show that the lipid \PIP{} is essential for proper
-transition zone maturation in the male Drosophila germline.
+transition zone maturation in the Drosophila male germline.
 Reduction of cellular \PIP{} by expression of the bacterial PIP
@@
 and do not represent an inability of the axoneme to grow.
-Rather,
+
+The type I phosphatidylinositol 4-phosphate kinase (PIPKI) Skittles
+suppresses TZ elongation in \sigd{} cells in a cilium-autonomous
+manner.
+We also found that cells mutant for \textit{sktl} contained hyperelongated
+TZs similar to SigD-expressing cells.
+Sktl also localizes to centrioles.
 
@@
 
+Members of the exocyst complex, such as Sec10 and Sec6, have been shown
+to be important for cilium formation in cultured cell lines and zebrafish
+\citep{zuo2009exocyst, lobo2017exocyst, seixas2016arl13b}.
+A mutation in \textit{EXOC8} has been linked
+to Joubert syndrome \citep{dixon2012exome}.
+The exocyst is known to bind to \PIP{}, and we previously described that
+the \textit{onr} allele of Drosophila \textit{Exo84} phenocopied
+male germline defects observed in \sigd{}.
+
 \section{Methods}
@@
 were described previously \citep{wei2008depletion, fabian2010phosphatidylinositol}.
-$\beta$\textit{2tub}::mCherry-Sktl\textsuperscript{kinase-dead}
-was generated by Gordon Polevoy.
 Ana1-tdTomato (chromosome 2) and Cep290-GFP (chromosome 3) were provided
@@
 \subsection{Fluorescence microscopy}
-For live imaging, testes were dissected in phosphate bufferd saline (PBS),
-transferred to a polylysine-coated glass slide in a drop of PBS,
+For live imaging, testes were dissected in phosphate bufferd saline (PBS).
+If staining for chromatin, intact testes were incubated in PBS with
+Hoechst (1:5000) for 5 minutes at this point.
+Testes were transferred to a polylysine-coated glass slide in a drop of PBS,
 ruptured using a syringe needle and

### 2018-02-08 latex/paper.tex
updated

@@
 \documentclass[12pt, twoside, letterpaper]{article}
-\usepackage[margin=0.7in]{geometry}
+\usepackage[margin=0.6in]{geometry}
 \usepackage[parfill]{parskip}
@@
 \title{\bfseries\large Phosphatidylinositol 4,5-bisphosphate regulates cilium transition zone maturation in Drosophila}
-\author[1,2]{Alind Gupta}
-\author[1,2]{Julie A. Brill}
+\author[1,2]{Alind Gupta \thanks{\url{alind.gupta@mail.utoronto.ca}}}
+\author[1,2]{Julie A. Brill \thanks{\url{julie.brill@sickkids.ca} (Corresponding author)}}
 \affil[1]{Department of Molecular Genetics, University of Toronto, Toronto, ON M5S 1A8, Canada}
@@
 
-In this study, we show that the lipid \PIP{} is essential for proper
-transition zone maturation in the Drosophila male germline.
-Reduction of cellular \PIP{} by expression of the bacterial PIP
-phosphatase SigD or inactivation of the type I PIP kinase Skittles
-causes developing TZs to elongate excessively.
+Cilia are essential for proper human development, and their disruption
+can cause genetic disorders which display severity ranging from congenital
+lethality to adult onset.
+A large number of ciliopathies are associated with genes that encode for
+proteins that function at the cilium transition zone (TZ).
+Often, a single gene is linked to multiple ciliopathies with variable phenotypes
+and severities.
+For example, the conserved TZ protein CEP290 is linked to at least six different
+cilium-associated disorders, suggesting that many of these encode for mutant proteins
+that are hypomorphic in nature whose function may
+be affected by modifier mutations and genetic environment.
+Animal models with mild perturbations of TZ function may therefore provide
+insight on intermediate phenotypes associated with human disease.
+Here, we found that reduced levels of the membrane lipid \PIP{},
+which is known to be enriched at the base of cilia,
+affects TZ maturation, but not assembly,
+leading to hyperelongated TZs that show signs of functional defects, and
+may represent one such modifier for TZ function.
 
-We had previously shown that reduction of \PIP{} by SigD expression
-affected flagellar biogenesis and axoneme structure
-\citep{wei2008depletion}.
-We also showed aberrant ``comet-shaped'' localization of Unc that
-failed to assemble TZ-associated puncta in some cases.
-Here, we show that this occurs prior to meiosis,
-is not an artefact due to cytokinesis defects
-and do not represent an inability of the axoneme to grow.
+In the Drosophila male germline, TZ maturation follows the initial
+assembly of TZ proteins on the nascent basal body in the cytoplasm
+followed by anchoring at the plasma membrane.
+TZ maturation involves microtubule rearrangements and TZ elongation,
+which leads to cilium-membrane attachment.
+Loss of \PIP{}, a membrane lipid largely at the plasma membrane,
+disrupts this process.
+It causes excessive lengthening of the TZ,
+and disrupts membrane-cilium connections.
 
@@
 TZs similar to SigD-expressing cells.
-Sktl also localizes to centrioles.
-
+Sktl also localizes to centrioles,
+and our results suggest that Skittles act locally at cilia to
+regulate TZ length.
+The protein CEP135, human ortholog of the Drosophila protein
+Asterless, has been show to bind PIPKI$\gamma$ in cell lines.
+PIPKI$\gamma$ is linked to lethal congenital contractural syndrome
+type 3 (LCCS3).
 It has previously been suggested that LCCS3 might represent a ciliopathy.
@@
 \citep{zuo2009exocyst, lobo2017exocyst, seixas2016arl13b}.
-A mutation in \textit{EXOC8} has been linked
-to Joubert syndrome \citep{dixon2012exome}.
 The exocyst is known to bind to \PIP{}, and we previously described that
@@
 male germline defects observed in \sigd{}.
+In this paper, we show that the \textit{onr} allele of the Drosophila Exo84
+phenocopies the loss of cilium-membrane contacts in \sigd{},
+but not TZ hyperelongation.
+Proper TZ function is required for membrane tethering, as \textit{dila; cby}
+mutants, which contain abnormal TZs also show cytoplasmic cilia similar to
+\sigd{}.
+Our results suggest that the exocyst is required after the initial stages
+of TZ assembly and maturation for TZ function.
 
@@
 Statistical analysis and graphing was performed using R.
+A Gaussian jitter was applied when plotting
+results in Figures 1 and 2,
+but raw data was used for all analysis.
 Statistical tests for ``absence of phenotype'' were computed under a
-hypothesis assuming binomial likelihood.
+hypothesis assuming binomial likelihood (i.e. assuming a fixed probability of the
+phenotype occurring).
 All $t$-tests were unpaired and two-sided.
-A significance level of 0.01 was fixed \textit{a priori} for all analysis.
+A significance level of 0.01 was fixed \textit{a priori} for all classical analysis.
+Bayesian analysis was performed in Stan.
+All raw data and code for analysis and plotting can be found online
+at \url{http://www.github.com/alindgupta/germline-paper/}.
+
+\subsection{Phylogenetic analysis}
+Candidate orthologs of \textit{sktl} or \textit{pip5k59b} were queried from Inparanoid and FlyBase.
+Poorly annotated protein sequences were manually curated to ensure
+these represented type I phosphatidylinositol phosphate
+kinases using reciprocal BLAST search.
+Phylogeny.fr (\url{http://www.phylogeny.fr}) was used for
+phylogenetic reconstruction with T-Coffee for multiple alignment
+and MrBayes for tree construction.
+The output was converted to a vector image in Illustrator
+and colours were added for the purposes of illustration.
 
@@
 \section{Acknowledgements}
-We thank Brian Ciruna for input on results.
+We thank Brian Ciruna for his input on the project
+and B. Durand for graciously providing unpublished fly stocks.
 

### 2018-02-11 figures/figure-1/plot.R
initial commit, merged plot1.R and plot2.R into one plot

@@ -1,0 +1,98 @@
+png(filename="fig1.png", width=7, height=6,units="in", res=600)
+
+library(RColorBrewer)
+library(plotrix)
+
+addNoise <- function(mtx) {
+    if (!is.matrix(mtx)) {
+        mtx <- matrix(mtx, byrow=TRUE, nrow=1)
+    }
+    random.stuff <- matrix(runif(prod(dim(mtx)), min=-0.0001, max=0.03), 
+                           nrow=dim(mtx)[1])
+    return(random.stuff + mtx)
+}
+
+df <- read.csv('fig1quantification.csv', header=TRUE)
+df <- cbind(df[,2], df[,1], df[,4], df[,3], df[,6], df[,5], df[,8], df[,7])
+
+df <- addNoise(df)
+
+cols <- brewer.pal(9,"Set1")[c(9,4)]
+
+par(bty="n",
+    mar=c(3, 4, 3, 0),  # plot margins b-l-t-r
+    las=1,              # horizontal labels
+    tcl=-.25,           # tick length
+    font.main=1,        # plain font
+    mgp=c(2.5, 0.5, 0),  # axis spacings
+    cex.lab=1.6,
+    cex.axis=1.4,
+    ps=12
+)
+
+xat <- c(0.5, 1, 1.5, 2, 2.5, 3, 3.5, 4)
+
+b <- boxplot(df,
+             xaxt="n",       # no x-axis
+             yaxt="n",
+             boxwex=0.45,    # boxwidth
+             lty=1,          # line type, 1 = solid
+             staplewex=0,    # no staples
+             ylim=c(0.3, 1.7),
+             at=xat,
+             border=cols,
+             lwd=2,
+             outline=FALSE)
+
+stripchart(apply(df, 2, as.list),
+           vertical=TRUE,
+           method="jitter",
+           add=TRUE,
+           pch=20,
+           cex=0.4,
+           col=cols,
+           at=xat,
+           jitter=0.05)
+
+title("Ana1 and Cep290 lengths", font.main=1, cex.main=1.6, line=0.7)
+title(ylab=expression(paste("Length (",italic("μ"), "m)", sep="")), line=2.2)
+
+tlab=c(1.6, 3.7)+0.2
+
[…]

### 2018-02-11 latex/paper.tex
updated

@@
 % title font size
-\titleformat*{\section}{\normalsize\bfseries}
+\titleformat*{\section}{\large\bfseries}
 \titleformat*{\subsection}{\normalsize\bfseries}
@@
 \newcommand{\PIP}{PIP\textsubscript{2}}
-\newcommand{\sigd}{$\beta$\textit{2tub}-SigD}
+\newcommand{\sigd}{$\beta$\textit{2t}-SigD}
 \newcommand{\sktl}{\textit{sktl}}
@@
 
-\title{\bfseries\large Phosphatidylinositol 4,5-bisphosphate regulates cilium transition zone maturation in Drosophila}
+\title{\bfseries\large Phosphatidylinositol 4,5-bisphosphate regulates cilium transition zone maturation in \textit{Drosophila melanogaster}}
 \author[1,2]{Alind Gupta \thanks{\url{alind.gupta@mail.utoronto.ca}}}
 \author[1,2]{Julie A. Brill \thanks{\url{julie.brill@sickkids.ca} (Corresponding author)}}
-\affil[1]{Department of Molecular Genetics, University of Toronto, Toronto, ON M5S 1A8, Canada}
-\affil[2]{Program in Cell Biology, Hospital for Sick Children, Toronto, ON M5G 1X8, Canada}
+\affil[1]{\small Department of Molecular Genetics, University of Toronto, Toronto, ON M5S 1A8, Canada}
+\affil[2]{\small Program in Cell Biology, Hospital for Sick Children, Toronto, ON M5G 1X8, Canada}
 \date{}
@@
 \begin{document}
+
 \maketitle
 \raggedright
+
 \begin{abstract}
@@
   \textit{Salmonella} phosphoinositide phosphatase SigD or mutation of
-  the type I phosphatidylinositol phosphate kinase Skittles (Sktl)
+  the type I phosphatidylinositol phosphate kinase (PIPKI) Skittles (Sktl)
   induces hyperelongation of TZs following their docking at the plasma
   membrane.
-  We provide evidence showing that these hyperelongated TZs are functionally
-  defective, and that the Exo84 mutant \textit{onion rings} decouples the
-  transition zone hyperelongation from the role for \PIP{} in cilium-membrane
+  We provide evidence that these hyperelongated TZs are functionally
+  defective, and that the Exo84 mutant \textit{onion rings} decouples
+  TZ hyperelongation from the role for \PIP{} in cilium-membrane
   tethering.
@@
 defects in cilium formation are associated with various genetic disorders
-known collectively as ciliopathies, which can manifest as
-neurological disorders \citep{valente2014primary},
+known collectively as ciliopathies, which can display
+neurological defects \citep{valente2014primary},
 skeletal abnormalities \citep{hammarsjo2017novel, waters2011ciliopathies}
@@
 localize to the cilium transition zone (referred to herein as TZ).
-The TZ is the proximal-most compartment of the cilium which
+The TZ is the proximal-most region of the cilium and
 acts as a diffusion barrier that regulates the
-bi-directional transport of protein and lipid cargo at the base of the cilium,
-and is essential for cilium formation and function in cell signalling.
+bi-directional transport of protein and lipid cargo at the base of the cilium.
+The TZ is essential for cilium formation (ciliogenesis) and cilium-associated
+signalling.
 The conserved TZ protein CEP290, for example, is mutated in at least
-five distinct ciliopathies, and is essential for cilium formation in both humans
-and Drosophila.
-Although the composition of TZs is well understood, processes underlying
-transition zone maturation and cell membrane anchoring are not as well-studied.
-In particular, why mutations in the same TZ protein can give rise to a plethora
-of phenotypic outputs is less understood, and may point at modifier mutations
-or mutations that are not as severe as to entirely abolish ciliogenesis.
+five different ciliopathies, and is essential for cilium formation in both humans
+and Drosophila \citep{basiri2014migrating}.
+Although the protein composition of TZs has been investigated in various
+studies ranging from single gene analysis to proteomics,
+processes underlying TZ maturation are not as well-studied.
 
@@
 \textit{Caenorrhabditis elegans} \citep{serwas2017centrioles} and
-\textit{D. melanogaster} \citep{gottardo2013cilium}
-and involves TZ elongation.
+\textit{Drosophila melanogaster} \citep{gottardo2013cilium}
+and is most readily observed by an increase in TZ length from nascent to mature.
 Possibly, this is similar to the initial steps of TZ assembly and reorganization
@@
 Here, we show that the lipid phosphatidylinositol 4,5-bisphosphate (\PIP{})
-is essential for proper TZ maturation in developing \textit{Drosophila melanogaster}
-male germ cells.
+is essential for proper TZ maturation in developing male germ cells in \textit{D. melanogaster}.
 Reduction of cellular \PIP{} by expression of the bacterial PIP phosphatase SigD
 or by inactivation of the PIP 5-kinase Skittles (Sktl) that localizes to cilia
-induces longer than normal TZs.
+induces longer than normal TZs without affecting TZ assembly.
 These hyperelongated TZs show hallmarks of aberrant function similar to those
@@
 \section{Results}
-
 \subsection{\PIP{} is essential for transition zone maturation}
@@
 We examined the localization of fluorescently-labelled centriolar/basal body protein
-Ana1 (Cep295) \citep{goshima2007genes, blachon2009proximal}
+Ana1 (CEP295 homolog) \citep{goshima2007genes, blachon2009proximal}
 and the TZ protein Cep290 \citep{basiri2014migrating}
@@
 MKS \citep{slaats2015mks1, vieillard2016transition} proteins (Figure 1).
-Hyperelongated transition zones persisted through meiosis.
+Hyperelongated TZs persisted through meiosis.
 Despite TZ hyperlongation, however, axonemes were able to elongate post-meiosis (Figure 1).
@@
 we attempted to rescue it by
-co-expressing fluorescently-tagged full-length Skittles (Sktl) with SigD
+co-expressing fluorescently-tagged full-length Sktl (Sktl) with SigD
 under the same promoter.
@@
 Similar to the human PIPKI$\gamma$ isoform \citep{xu2014pipkigamma},
-we found that Skittles localizes to basal bodies in the Drosophila male germline.
-As shown in Figure 2, Drosophila PIP5Ks arose from the recent duplication of
-the ancestral PIP5K gene, and are not orthologous to specific vertebrate PIP5K isoforms.
-Skittles has diverged more than the paralogous PIP5K59B gene, and seems
+we found that Sktl localizes to basal bodies in the Drosophila male germline.
+As shown in Figure 2, Drosophila PIPKIs arose from the recent duplication of
+the ancestral PIPKI gene, and are not orthologous to specific vertebrate PIPKI isoforms.
+Sktl has diverged more than the paralogous PIP5K59B gene, and seems
 to be functionally related to PIPKI$\gamma$ in its roles at cilia.
@@
 by promoting CP110 uncapping from basal bodies \citep{xu2016phosphatidylinositol},
-our results suggest that Skittles functions in
+our results suggest that Sktl functions in
 regulating TZ length in the Drosophila male germline
 but is dispensable for its assembly.
-The localization of Cp110 is unaffected in \sigd{} (supplementary figure 1).
+Cp110 is dispensable for cilium formation in Drosophila \citep{franz2013cp110}
+and we found its localization to be unaffected in \sigd{} (supplementary figure 1).
 
@@
 \section{Discussion}
-
 Cilia are essential for proper human development, and their disruption
@@
 and disrupts membrane-cilium connections.
+Thus, intermediate steps during TZ maturation require \PIP{}.
 
@@
 and 50\% humidity.
-Stocks expressing $\beta$\textit{2tub}::SigD and $\beta$\textit{2tub}::YFP-Sktl
+Stocks expressing $\beta$\textit{2tubulin}::\textit{Styp}\textbackslash{SigD} (chromosome \textit{3})
+and $\beta$\textit{2tub}::YFP-Sktl (chromosome \textit{2})
 were described previously \citep{wei2008depletion, fabian2010phosphatidylinositol}.
-Ana1-tdTomato (chromosome 2) and Cep290-GFP (chromosome 3) were provided
+$\beta$\textit{2tub}::mCherry-Sktl was made as in \citep{wei2008depletion},
+and a \textit{P}-element insertion on chromosome \textit{2} was used for rescue using the low-level
+expression vector \textit{tv3} \citep{wong2005pip2}.
+Ana1-tdTomato (chromosome \textit{2}) and Cep290-GFP (chromosome \textit{3}) were provided
 by T. Avidor-Reiss \citep{basiri2014migrating}.
-Unc-GFP was originally provided by M. Kernan \citep{baker2004mechanosensory}.
+\textit{Sp}/\textit{CyO}; Unc-GFP was originally provided by M. Kernan \citep{baker2004mechanosensory}.
 Stocks expressing GFP-tagged Chibby, B9d1, B9d2, Cc2d2a and Mks1 were generously
@@
 at the indicated concentrations - 
-rabbit $\alpha$-Tulp (gift from W. McGinnis \citep{ronshaugen2002structure}), 1:500; 
-chicken $\alpha$-GFP IgY (abcam) 1:1000;
-rat $\alpha$-RFP IgG (5F8, ChromoTek), 1:1000;
-rabbit $\alpha$-Sktl (courtesy of P. Raghu), 1:500;
+rabbit anti-Tulp (gift from W. McGinnis \citep{ronshaugen2002structure}), 1:500; 
+chicken anti-GFP IgY (abcam) 1:1000;
+rat anti-RFP IgG (5F8, ChromoTek), 1:1000;
+rabbit anti-Sktl (courtesy of P. Raghu), 1:500;
+rabbit anti-\textit{d}Sec6 (courtesy of U. Tepass), 1:500;
+mouse anti-acetylated $\alpha$-tubulin 6-11-B (Sigma-Aldrich), 1:1000.
 Secondary antibodies were Alexa 488- and Alexa 568-conjugated
-$\alpha$-mouse, $\alpha$-rabbit and $\alpha$-chicken
+anti-mouse, anti-rabbit and anti-chicken
 IgG (Molecular Probes) at 1:1000.
@@
 
+For Taxol treatments, testes from larvae or pupae expressing
+Ana1-tdTomato; Cep290-GFP were
+dissected into Shields and Sang M3 medium (Sigma-Aldrich) supplemented
+with a predefined
+concentration of Taxol and incubated overnight in a humidified sterile
+chamber in the dark at room temperature. They were then squashed
+in PBS and visualized immediately.
+
+For CellMask staining, cells were spilled from testes in M3 medium onto
+a sterilized glass-bottom dish that was pre-treated with sterile polylysine solution
+to enable cells to adhere.
+CellMask Deep Red (Invitrogen) solution (20 $\mu$g/mL) was added to the medium dropwise
+immediately before visualization under a confocal microscope.
+
 For immunochemistry, testes were dissected in PBS,
-transferred to a polylysine-coated gladd slide in a drop of PBS,
+transferred to a polylysine-coated glass slide in a drop of PBS,
 ruptured with a needle, squashed and frozen in liquid nitrogen for 5 minutes.
-The slides were transferred to ice-cold methanol for 5-10 minutes.
-For staining with the $\alpha$-skittles antibody, pre-fixation in methanol
+The slides were transferred to ice-cold methanol for 5-10 minutes for pre-fixation.
+For staining with the anti-Sktl antibody, this pre-fixation step
 was omitted to preserve cellular membranes.
@@
 with secondary antibodies and three 5-minute washes with PBS.
-Samples were mounted in Dako (Agilent) and imaged with Leica widefield microscope
+Samples were mounted in Dako (Agilent) and imaged with
+a Leica widefield microscope
 or Nikon A1R scanning confocal microscope (SickKids imaging facility).
@@
 A Gaussian jitter was applied when plotting
-results in Figures 1 and 2,
+results in Figures 1 and 2 for clearer visualization of trends,
 but raw data was used for all analysis.
@@
 A significance level of 0.01 was fixed \textit{a priori} for all classical analysis.
-Bayesian analysis was performed in Stan.
 All raw data and code for analysis and plotting can be found online
@@
 \subsection{Phylogenetic analysis}
-Candidate orthologs of \textit{sktl} or \textit{pip5k59b} were queried from Inparanoid and FlyBase.
-Poorly annotated protein sequences were manually curated to ensure
-these represented type I phosphatidylinositol phosphate
+Candidate orthologs of Skittles or PIP5K9B were queried
+from Inparanoid and FlyBase (version 8.0).
+Poorly annotated protein sequences were confirmed
+to encode type I phosphatidylinositol phosphate
 kinases using reciprocal BLAST search.
@@
 The output was converted to a vector image in Illustrator
-and colours were added for the purposes of illustration.
+and colours were added for the purpose of illustration.
 
@@
 A.G. and J.A.B. conceived the project.
-A.G. performed all the experiments and wrote the manuscript.
+A.G. performed all the experiments and analysis, and wrote the manuscript.
 J.A.B. supervised the project.
@@
 We thank Brian Ciruna for his input on the project
-and B. Durand for graciously providing unpublished fly stocks.
+and Bénédicte Durand for providing unpublished fly stocks.
+This work was supported by a grant from the Canadian Institute for Health Research
+(CIHR) to J.A.B.
 

### 2018-02-11 figures/figure-1/plot1.R

@@ -1,4 +1,4 @@
-#png(filename="germlate.png", width=6.5, height=6,units="in", res=600)
+#png(filename="germlate.png", width=6, height=3,units="in", res=300)
 
 # import data
 df <- read.csv('fig1quantification.csv', header=TRUE)
@@ -14,10 +14,10 @@ df <- addNoise(df)
 
 library(RColorBrewer)
 
-cols <- brewer.pal(9,"Set1")[c(1,2)]
+cols <- brewer.pal(9,"Set1")[c(1,3)]
 
 par(bty="n",
-    mar=c(4, 4, 3, 3),  # plot margins b-l-t-r
+    mar=c(0, 2, 0, 0),  # plot margins b-l-t-r
     las=1,              # horizontal labels
     tcl=-.25,           # tick length
     font.main=1,        # plain font
@@ -55,20 +55,20 @@ stripchart(apply(df, 2, as.list),
            at=xat,
            jitter=0.05)
 
-title("Cep290 and Ana1 lengths (late G2 phase)", font.main=1, cex.main=1.3, line=0.7)
-title(ylab=expression(paste("Length (",italic("μ"), "m)", sep="")), line=2.2)
+#title("Cep290 and Ana1 lengths (late G2 phase)", font.main=1, cex.main=1.3, line=0.7)
+#title(ylab=expression(paste("Length (",italic("μ"), "m)", sep="")), line=2.2)
 
 tlab=c(1.6, 3.7)+0.2
 
 axis(2, at=seq(0.6, 1.8, 0.2), labels=TRUE, col.ticks=1, lwd=1, lwd.ticks=1)
 
-lab=c('Control', expression(italic('β2t')~'::'~'SigD'))
+#lab=c('Control', expression(italic('β2t')*'-SigD'))
 
-text(x=tlab, y=par()$usr[3]-0.1*(par()$usr[4]-par()$usr[3]-0.3),
-     labels=lab, srt=0, adj=1, xpd=TRUE, cex=1)
+#text(x=tlab, y=par()$usr[3]-0.1*(par()$usr[4]-par()$usr[3]-0.3),
+#     labels=lab, srt=0, adj=1, xpd=TRUE, cex=1)
 
-temp.labels = c("Cep290-GFP", "Ana1-tdTomato")
[…]

### 2018-02-11 figures/figure-1/plot2.R

@@ -1,4 +1,4 @@
-#png(filename="germlate.png", width=6.5, height=6,units="in", res=600)
+png(filename="germearly.png", width=6, height=3,units="in", res=300)
 
 # import data
 df <- read.csv('fig1quantification.csv', header=TRUE)
@@ -14,10 +14,10 @@ df <- addNoise(df)
 
 library(RColorBrewer)
 
-cols <- brewer.pal(9,"Set1")[c(1,2)]
+cols <- brewer.pal(9,"Set1")[c(1,3)]
 
 par(bty="n",
-    mar=c(3, 4, 3, 3),  # plot margins b-l-t-r
+    mar=c(0, 2, 0, 0),  # plot margins b-l-t-r
     las=1,              # horizontal labels
     tcl=-.25,           # tick length
     font.main=1,        # plain font
@@ -55,28 +55,28 @@ stripchart(apply(df, 2, as.list),
            at=xat,
            jitter=0.05)
 
-title("Cep290 and Ana1 lengths (early G2 phase)", font.main=1, cex.main=1.3, line=0.7)
-title(ylab=expression(paste("Length (",italic("μ"), "m)", sep="")), line=2.2)
+#title("Cep290 and Ana1 lengths (early G2 phase)", font.main=1, cex.main=1.3, line=0.7)
+#title(ylab=expression(paste("Length (",italic("μ"), "m)", sep="")), line=2.2)
 
 tlab=c(1.6, 3.7)+0.2
 
 axis(2, at=seq(0.3, 0.6, 0.1), labels=TRUE, col.ticks=1, lwd=1, lwd.ticks=1)
+lab=c('Control', expression(italic('β2t')*'-SigD'))
 
-lab=c('Control', expression(italic('β2t')~'::'~'SigD'))
-text(x=tlab, y=par()$usr[3]-0.1*(par()$usr[4]-par()$usr[3]-0.3),
-     labels=lab, srt=0, adj=1, xpd=TRUE, cex=1)
+#text(x=tlab, y=par()$usr[3]-0.1*(par()$usr[4]-par()$usr[3]-0.3),
+#     labels=lab, srt=0, adj=1, xpd=TRUE, cex=1)
 
-temp.labels = c("Ana1-tdTomato", "Cep290-GFP")
[…]

### 2018-02-11 figures/figure-2/plot.R
updated

@@ -1,4 +1,4 @@
-#png(filename="cepgerm.png", width=6.5, height=6,units="in", res=600)
+png(filename="rescuelength.png", width=7, height=6,units="in", res=600)
 
 # import data
 df <- read.csv('quantification.csv', header=TRUE)
@@ -14,16 +14,16 @@ df <- addNoise(df)
 
 library(RColorBrewer)
 
-cols <- brewer.pal(9,"Set1")[c(1,2,3)]
+cols <- brewer.pal(9,"Set1")[c(9,4,5)]
 
 par(bty="n",
-    mar=c(3, 4, 3, 3),  # plot margins b-l-t-r
+    mar=c(2, 4, 3, 0),  # plot margins b-l-t-r
     las=1,              # horizontal labels
     tcl=-.25,           # tick length
     font.main=1,        # plain font
     mgp=c(2.5, 0.5, 0),  # axis spacings
-    cex.lab=1.1,
-    cex.axis=1.1,
+    cex.lab=1.6,
+    cex.axis=1.4,
     ps=12
 )
 
@@ -58,8 +58,8 @@ stripchart(apply(df, 2, as.list),
            at=xat,
            jitter=0.05)
 
-title("Cep290 and Ana1 lengths\n (late G2 phase)", font.main=1, cex.main=1.3, line=0.2)
-title(ylab=expression(paste("Length (",italic("μ"), "m)", sep="")), line=2.2)
+title("Cep290 and Ana1 lengths\n (late G2 phase)", font.main=1, cex.main=1.6, line=0)
+title(ylab=expression(paste("Length (", "μ", "m)", sep="")), line=2.2)
 
 axis(2, at=seq(0.6, 2, 0.2), labels=TRUE, col.ticks=1, lwd=1)
 axis(1, labels=c("Cep290-GFP", "Ana1-tdTomato"), at=c(2, 0.92*(xat[5]+xat[6])/2), lwd.ticks=0, lty=0, line=-0.8)
@@ -67,29 +67,29 @@ axis(1, at=c(0, ((xat[3] + xat[4])/2)), labels=FALSE, tck=-0.05, col=0, lty=0)
 #box(bty='L')
 
 temp.labels = c("Control", "SigD", "SigD + Sktl")
[…]

### 2018-02-14 latex/paper.tex
updated

@@
 \usepackage[numbers]{natbib}
-\usepackage{graphicx}
+\usepackage[draft]{graphicx}  %% remove [draft] to compile with pictures
+\graphicspath{{../figures/}}
+\usepackage{enumitem}
 \usepackage{hyperref}
@@
 defects in cilium formation are associated with various genetic disorders
-known collectively as ciliopathies, which can display
+known collectively as ciliopathies, which can 
 neurological defects \citep{valente2014primary},
-skeletal abnormalities \citep{hammarsjo2017novel, waters2011ciliopathies}
-and infertility \citep{inaba2016sperm}.
+skeletal abnormalities \citep{hammarsjo2017novel, waters2011ciliopathies},
+and infertility \citep{inaba2016sperm} in addition to other phenotypes.
 
@@
 we used transgenic flies expressing the Salmonella phosphoinositide phosphatase SigD
-under $\beta$2-tubulin promoter (referred to herein as \sigd{}),
-which is uniquely expressed in spermatocytes
+under the $\beta$2-tubulin promoter (referred to herein as \sigd{}),
+which is expressed exclusively in spermatocytes
 \citep{wei2008depletion, fabian2010phosphatidylinositol}.
-We previously showed that expression of this construct
-induced male sterility due in part to defects in flagellar biosynthesis \citep{wei2008depletion}.
-We examined the localization of fluorescently-labelled centriolar/basal body protein
+We previously showed that \sigd{} induces male sterility
+due in part to defects in flagellar biosynthesis \citep{wei2008depletion}.
+To understand whether this was due to aberrant TZ function,
+we examined the localization of fluorescently-labelled
+centriolar/basal body protein
 Ana1 (CEP295 homolog) \citep{goshima2007genes, blachon2009proximal}
 and the TZ protein Cep290 \citep{basiri2014migrating}
-in wild-type control and \sigd{} spermatocytes.
-As shown in Figure 1A, nascent TZs marked with Cep290-GFP assemble normally in \sigd{} cells
-but grow to much longer lengths compared to wild-type control cells.
-TZ hyperelongation was a highly penetrant phenotype (\textgreater 90\%)
-and showed high intra-cyst correlation.
+during early steps of cilium assembly in spermatocytes in both
+wild-type controls and \sigd{}.
+As shown in Figure 1A, Cep290 grew to much longer lengths in \sigd{}
+compared to wild-type controls.
+Ana1 lengths were not affected, and we did not observe an inverse
+correlation between Cep290 and Ana1 length.
 This phenotype was not specific to Cep290;
@@
 MKS \citep{slaats2015mks1, vieillard2016transition} proteins (Figure 1).
+TZ hyperelongation was a highly penetrant phenotype (\textgreater 90\%)
+and showed high intra-cyst correlation (\textgreater 0.95) suggestive
+of a dosage-based response to a shared cellular factor.
 Hyperelongated TZs persisted through meiosis.
-Despite TZ hyperlongation, however, axonemes were able to elongate post-meiosis (Figure 1).
-As we showed previously, the ultrastructure of these axonemes was frequently aberrant,
+Despite TZ hyperlongation, however, axonemes were able to
+elongate post-meiosis (Figure 1).
+As we showed previously, the ultrastructure of these axonemes
+was frequently aberrant,
 either lacking symmetry completely or containing triplet microtubules instead of doublets
@@
 \subsection{The type I PIP kinase Skittles localizes to centrioles and regulates TZ length}
-Although numerous studies have shown that \PIP{} is the major substrate for SigD
-when expressed in eukaryotic cells
+While \PIP{} is the major substrate for SigD in eukaryotic cells \textit{in vivo}
 \citep{terebiznik2002elimination, zhou2001salmonella, sengupta2013depletion},
-SigD can dephosphorylate other PIPs \textit{in vitro}
+SigD can also dephosphorylate other PIPs \textit{in vitro}
 \citep{norris1998sopb}.
-To address whether TZ hyperelongation observed in \sigd{} represented
-a physiologically relevant phenotype in response to decreased \PIP{},
+To address whether TZ hyperelongation observed in \sigd{} represented a
+physiologically relevant phenotype in response to decreased \PIP{},
 we attempted to rescue it by
@@
 We found that Sktl expression was able to suppress TZ elongation in a cilium-autonomous
-manner (Figure 2).
-We also found that \textit{sktl} clones showed penetrant TZ hyperelongation when
-marked with Unc-GFP, a ciliary marker \citep{baker2004mechanosensory}.
+manner (Figure 2A and B).
+We also found that \textit{sktl} clones using Flp/FRT-based mitotic recombination
+showed penetrant TZ hyperelongation (Figure 2C).
 
-Since Sktl expression lead to cilium-autonomous rescue,
+Since Sktl expression suppressed TZ hyperelongation,
 we investigated whether Sktl could localize to centrioles or cilia in the Drosophila germline.
@@
 the ancestral PIPKI gene, and are not orthologous to specific vertebrate PIPKI isoforms.
-Sktl has diverged more than the paralogous PIP5K59B gene, and seems
+Sktl has diverged more than its paralog PIP5K59B, and seems
 to be functionally related to PIPKI$\gamma$ in its roles at cilia.
 However, unlike the human PIPKI$\gamma$, which functions to license TZ assembly
-by promoting CP110 uncapping from basal bodies \citep{xu2016phosphatidylinositol},
+by promoting CP110 removal from basal bodies \citep{xu2016phosphatidylinositol},
 our results suggest that Sktl functions in
 regulating TZ length in the Drosophila male germline
-but is dispensable for its assembly.
+but not its assembly.
 Cp110 is dispensable for cilium formation in Drosophila \citep{franz2013cp110}
@@
 \subsection{Hyperelongated transition zones show signs of functional defects}
-While shorter spermatocyte TZs have been observed in Drosophila mutants of TZ proteins
+While shorter spermatocyte TZs have been reported in mutants of TZ proteins in Drosophila
 \citep{vieillard2016transition, pratt2016drosophila},
@@
 We previously described ``comet-shaped'' localization of Unc-GFP in these cells,
-and we find that these hyperelongated Unc signals persist into cellular elongation.
+and we find that these hyperelongated Unc signals persist into cellular elongation
+despite elongation of the axoneme.
 
-Another phenotype that is consistent with this hypothesis is
-the observation of the centriolar protein Ana1 localizing to the distal tips of
-hyperelongated TZs.
-TZ-distal Ana1 localization is observed at a relatively low penetrance
+%% reword this, paragraph is garbage
+We previously described the presence of occasional triplet microtubules
+in electron micrographs of axonemes from \sigd{} \citep{wei2008depletion}.
+While centrioles and basal bodies contain microtubule triplets,
+restriction of the C-tubule at the TZ causes the axoneme to
+consist of microtubule doublets rather than triplets throughout its length.
+Consistent with a defect in TZ barrier formation and presence of
+microtubule triplets in axonemes,
+we observed that a subset of cilia in \sigd{}
+contained puncta of Ana1, a core centriolar protein, at the tips
+of TZs marked with Cep290.
+This TZ-distal Ana1 localization is observed at a relatively low penetrance
 and high intra-cyst correlation.
-This is possibly related to stochastic SigD expression in cysts.
 We found that treatment of germ cells with Paclitaxel as in \citep{riparbelli2013unique}
@@
 Paclitaxel treatment alone did not induce this phenotype in wild-type controls in our hands
-at varying concentrations (binomial probability < 0.001 with 5\% penetrance),
+at varying concentrations ($p$ <0.01 with 5\% penetrance),
 suggesting that loss of \PIP{} acts upstream of or prior to microtubule rearrangement.
-Although we can not show a definitive reason for this, we expect that this is due to
-the axoneme maintaining some centriolar fate.
-We had previously shown the presence of microtubule triplets in axonemes assembled in \sigd{}
-cells.
-These are also observed in Taxol-treated cells \citep{riparbelli2013unique}.
+Triplet microtubules within the axoneme are also observed in Taxol-treated cells \citep{riparbelli2013unique}.
 It is possible that the TZ defect allows C-tubules and some centriolar proteins
@@
 a migratory protein that localizes to the outer
-ring of centrioles (Figure 3).
+ring of centrioles ($p$ <0.01).
 
@@
 Joubert syndrome \citep{dixon2012exome}.
+EXOC8, the human ortholog of Exo84, is a component of the octameric exocyst complex, which binds
+\PIP{} and regulates membrane trafficking at the plasma membrane.
 We previously showed that male flies homozygous for the \textit{onion rings}
@@
 similar to \sigd{} \citep{wei2008depletion}.
-Exo84 is a component of the octameric exocyst complex, which binds
-\PIP{} and regulates membrane trafficking at the plasma membrane.
-We found that the \textit{onr} mutant did not display hyperelongated TZs (Figure 5).
+To investigate whether defects in TZ hyperelongation could be explained by
+defective Exo84 function, we examined TZs in \textit{onr} mutants.
+We found that the \textit{onr} mutant did not display hyperelongated TZs (Figure 5),
+suggesting that Exo84 is dispensable for TZ maturation.
 
-Since exocyst regulates membrane trafficking and cilium formation,
+Due to the involvement of exocyst in membrane trafficking at the plasma membrane,
 we examined whether cilium-associated membrane dynamics were affected in \sigd{}
@@
 we found that Sec6 and Exo70 localized to the plasma membrane as expected,
-but were not enriched at the cilium.
+but were not enriched at the cilium (Figure 5C).
 Our results suggest that the exocyst may act downstream of \PIP{} to
@@
 \section{Acknowledgements}
-We thank Brian Ciruna for his input on the project
+We thank Brian Ciruna for insightful comments on the project
 and Bénédicte Durand for providing unpublished fly stocks.
@@
 
+\newpage
+\section{Figures}
+
+%%
+%    FIGURE 1
+%
+\textbf{Figure 1. SigD expression induces transition zone hyperelongation.} 
+\begin{enumerate}[label={(\Alph*)}, nolistsep]
+\item \sigd{} expression induces Cep290 hyperelongation in mature (late G2 phase) cilia.  
+\item Paired Ana1-Cep290 lengths in nascent and mature cilia ($n$ \textgreater 30). 
+\item \sigd{} expression induces hyperelongation of other TZ markers, such as Cby, Mks
+  and acetylated tubulin.
+\item TZ hyperelongation persists through meiosis but does not affect
+  axoneme outgrowth.
+\end{enumerate}
+
+\begin{figure}[ht]
+  \includegraphics[scale=0.9]{figure-1/figure1.png}
+\end{figure}
+\newpage
+
+%%
+%    FIGURE 2
+%
+\textbf{Figure 2. Sktl is important for transition zone maturation and localizes to basal bodies.} 
+\begin{enumerate}[label={(\Alph*)}, nolistsep]
+\item Expression of full-length Sktl suppresses \sigd{}-induced TZ hyperelongation.
+\item Quantification of Cep290 and Ana1 lengths from control, \sigd{} and Sktl; \sigd{} ($n$\textgreater 60) from (A).
+\item \textit{sktl}$^{2.3}$ clones exhibit TZ hyperelongation.
+\item Phylogenetic tree of PIP5Ks showing conservation of cilium-associated functions.
+  The scale bar represents expected amino acid substitutions per site and branch support values are shown in red (a value of 1 indicates maximum support).
+Abbreviations: Cele (\textit{Caenorhabditis elegans}), Spur (\textit{Strongylocentrotus purpuratus}), Amel (\textit{Apis mellifera}), Aaeg (\textit{Aedes aegypti}), Dana (\textit{Drosophila ananassae}), Dmel (\textit{Drosophila melanogaster}), Hsap (\textit{Homo sapiens}), Mmus (\textit{Mus musculus}), Xtro (\textit{Xenopus tropicalis}), Cint (\textit{Ciona intestinalis}), Scer (\textit{Saccharomyces cerevisiae}).
+\end{enumerate}
+
+\begin{figure}[ht]
+  \includegraphics[scale=0.9]{figure-2/figure2.png}
+\end{figure}
+\newpage
+
+%%
+%    FIGURE 3
+%
+\textbf{Figure 3. Hyperelongated transition zones display functional defects.}
+\begin{enumerate}[label={(\Alph*)}, nolistsep]
+\item
+\item 
+\item 
+\item 
+\end{enumerate}
+
+%\begin{figure}[ht]
+%  \includegraphics[scale=0.9]{figure-3/figure2.png}
+%\end{figure}
+%\newpage
+
+%%%
+%%    FIGURE 4
+%%
+\textbf{Figure 4. The \textit{onion rings} (\textit{onr}) allele of \textit{d}Exo84 decouples TZ hyperlongation from loss of plasma membrane contacts.}
+\begin{enumerate}[label={(\Alph*)}, nolistsep]
+\item Cells mutant for \textit{onr} do not display hyperelongated TZs marked with acetylated tubulin.
+\item Quantification from (A).
+\item Cells mutant for \textit{onr} display loss of plasma membrane tethering.
+\end{enumerate}
+
+%\begin{figure}[ht]
+%  \includegraphics[scale=0.9]{figure-4/figure2.png}
+%\end{figure}
+%\newpage
+
 \end{document}

### 2018-02-15 latex/paper.tex
updated

@@
 In the Drosophila male germline, nascent TZs first assemble on basal bodies
-during early pre-meiotic G2 phase (spermatocytes), anchor directly to the plasma membrane.
-This is followed by establishment of cilium-membrane connections and a
-ciliary membrane that persists during meiosis \citep{riparbelli2012assembly}
+during early G2 phase in spermatocytes and anchor directly to the plasma membrane.
+This is followed by establishment of cilium-membrane connections
 through a poorly understood mechanism
-involving microtubule rearrangements \citep{gottardo2013cilium}.
+involving microtubule rearrangements \citep{gottardo2013cilium} and a
+ciliary membrane that persists through meiosis \citep{riparbelli2012assembly}.
 Ciliogenesis begins with the assembly of TZ proteins at the tips of
@@
 proteins that function at the cilium transition zone (TZ).
-Often, a single gene is linked to multiple ciliopathies with variable phenotypes
+Often, a single gene is linked to multiple ciliopathies with distinct phenotypes
 and severities.
-For example, the conserved TZ protein CEP290 is linked to at least six different
-cilium-associated disorders, suggesting that many of these encode for mutant proteins
-that are hypomorphic in nature whose function may
-be affected by modifier mutations and genetic environment.
-Animal models with mild perturbations of TZ function may therefore provide
+For example, \textit{CEP290} is linked to at least six different
+cilium-associated disorders.
+It is likely that these mutations do not completely abolish CEP290
+function, and may be affected by genetic modifiers in an affected individual
+\citep{zaghloul2010functional}.
+Animal models with partial loss of TZ function may therefore provide
 insight on intermediate phenotypes associated with human disease.
@@
 Sktl also localizes to centrioles,
-and our results suggest that Skittles act locally at cilia to
+and our results suggest that Skittles acts locally at cilia to
 regulate TZ length.
-The protein CEP135, human ortholog of the Drosophila protein
-Asterless, has been show to bind PIPKI$\gamma$ in cell lines.
 PIPKI$\gamma$ is linked to lethal congenital contractural syndrome
@@
 It has previously been suggested that LCCS3 might represent a ciliopathy.
-PIPKI$\gamma$ is linked to LCCS3 with many features reminiscent
-of ciliopathies, such as micrognathia, and a role for the LCCS1 protein
+PIPKI$\gamma$ is linked to LCCS3 with features reminiscent
+of ciliopathies such as micrognathia, and a role for the LCCS1 protein
 Gle3 in cilia.
@@
 \citep{zuo2009exocyst, lobo2017exocyst, seixas2016arl13b}.
-The exocyst is known to bind to \PIP{}, and we previously described that
+The exocyst is known to bind to \PIP{}
+\citep{he2007exo70, zhang2008membrane}, and we previously described that
 the \textit{onr} allele of Drosophila \textit{Exo84} phenocopied
-male germline defects observed in \sigd{}.
+male germline defects observed in \sigd{} \citep{fabian2010phosphatidylinositol}.
 In this paper, we show that the \textit{onr} allele of the Drosophila Exo84
@@
 mutants, which contain abnormal TZs also show cytoplasmic cilia similar to
-\sigd{}.
+\sigd{} \citep{vieillard2016transition}.
 Our results suggest that the exocyst is required after the initial stages

### 2018-02-20 latex/paper.tex
update
updated

@@
 \citep{bloodgood2010sensory}.
-Consistent with their pervasiveness and importance in cell signalling,
-defects in cilium formation are associated with various genetic disorders
-known collectively as ciliopathies, which can 
+Consistent with their importance in cell signalling,
+defects in cilium formation are associated with genetic disorders
+known collectively as ciliopathies, which can display
 neurological defects \citep{valente2014primary},
@@
 acts as a diffusion barrier that regulates the
-bi-directional transport of protein and lipid cargo at the base of the cilium.
+bi-directional transport of protein and lipid cargo at the base of the cilium
+\citep{reiter2012base, szymanska2012transition}.
 The TZ is essential for cilium formation (ciliogenesis) and cilium-associated
@@
 The conserved TZ protein CEP290, for example, is mutated in at least
-five different ciliopathies, and is essential for cilium formation in both humans
+six different ciliopathies, and is essential for cilium formation in both humans
 and Drosophila \citep{basiri2014migrating}.
@@
 and is most readily observed by an increase in TZ length from nascent to mature.
-Possibly, this is similar to the initial steps of TZ assembly and reorganization
-in well-studied vertebrate cilia.
+This are probably similar to the initial steps of TZ assembly and reorganization
+in vertebrates.
 
@@
 is essential for proper TZ maturation in developing male germ cells in \textit{D. melanogaster}.
-Reduction of cellular \PIP{} by expression of the bacterial PIP phosphatase SigD
+\PIP{} is a membrane lipid and one of seven phosphoinositides (PIPs)
+present in eukaryotic cells.
+It is primarily enriched at the plasma membrane and the base of cilia,
+but its functions in ciliogenesis have not been studied.
+We found that reduction of cellular \PIP{}
+by expression of the bacterial PIP phosphatase SigD
 or by inactivation of the PIP 5-kinase Skittles (Sktl) that localizes to cilia
@@
 These hyperelongated TZs show hallmarks of aberrant function similar to those
-found in previously studied TZ mutants, including loss of cilium-membrane associations.
+found in previously studied TZ mutants,
+including loss of cilium-membrane associations.
 We also find that the \textit{onion rings} allele of the
@@
 Joubert syndrome \citep{dixon2012exome}.
-EXOC8, the human ortholog of Exo84, is a component of the octameric exocyst complex, which binds
+Exo84 is a component of the octameric exocyst complex, which binds
 \PIP{} and regulates membrane trafficking at the plasma membrane.
@@
 Cilia are essential for proper human development, and their disruption
-can cause genetic disorders which display severity ranging from congenital
-lethality to adult onset.
+can cause genetic disorders with severities ranging from congenital-
+lethal \citep{}
+to late onset \citep{}.
 A large number of ciliopathies are associated with genes that encode for
@@
 \item Quantification of Cep290 and Ana1 lengths from control, \sigd{} and Sktl; \sigd{} ($n$\textgreater 60) from (A).
-\item \textit{sktl}$^{2.3}$ clones exhibit TZ hyperelongation.
+\item \textit{sktl}$^{2.3}$ clones exhibit TZ hyperelongation. Cilia are marked using
+  Unc-GFP.
 \item Phylogenetic tree of PIP5Ks showing conservation of cilium-associated functions.
@@
 %\end{figure}
-%\newpage
+\newpage
 

### 2018-02-20 latex/paper.tex
updated

@@
 For example, \textit{CEP290} is linked to at least six different
-cilium-associated disorders.
+cilium-associated human disorders.
 It is likely that these mutations do not completely abolish CEP290
@@
 
-The type I phosphatidylinositol 4-phosphate kinase (PIPKI) Skittles
+We found that the type I phosphatidylinositol 4-phosphate kinase (PIPKI) Skittles
 suppresses TZ elongation in \sigd{} cells in a cilium-autonomous
@@
 
-%\begin{figure}[ht]
-%  \includegraphics[scale=0.9]{figure-3/figure2.png}
-%\end{figure}
+\begin{figure}[ht]
+  \includegraphics[scale=0.8]{figure-3/figure3.png}
+\end{figure}
 \newpage
@@
 
-%\begin{figure}[ht]
-%  \includegraphics[scale=0.9]{figure-4/figure2.png}
-%\end{figure}
-%\newpage
+\begin{figure}[ht]
+  \includegraphics[scale=0.9]{figure-4/figure4.png}
+\end{figure}
+\newpage
 

### 2018-02-20 figures/figure-2/plot.R

@@ -1,3 +1,6 @@
+#' Plotting for rescue
+#' Same data as figure 1 quantification
+
 png(filename="rescuelength.png", width=7, height=6,units="in", res=600)
 
 # import data

### 2018-02-20 figures/figure-2/plot2.R
initial commit

@@ -1,0 +1,86 @@
+#' Plotting Unc-GFP lengths
+#' n = 30-60
+
+#png(filename="unc.png", width=7, height=6,units="in", res=600)
+
+# import data
+df <- read.csv('unc.csv', header=TRUE)
+df <- cbind(df[,1], df[,3], df[,2])
+    
+addNoise <- function(mtx) {
+    if (!is.matrix(mtx)) mtx <- matrix(mtx, byrow = TRUE, nrow = 1)
+    random.stuff <- matrix(runif(prod(dim(mtx)), min = -0.0001, max = 0.01), nrow = dim(mtx)[1])
+    random.stuff + mtx
+}
+
+df <- addNoise(df)
+
+library(RColorBrewer)
+
+cols <- brewer.pal(9,"Set1")[c(9,4,5)]
+
+par(bty="n",
+    mar=c(2, 4, 3, 0),  # plot margins b-l-t-r
+    las=1,              # horizontal labels
+    tcl=-.25,           # tick length
+    font.main=1,        # plain font
+    mgp=c(2.5, 0.5, 0),  # axis spacings
+    cex.lab=1.6,
+    cex.axis=1.4,
+    ps=12
+)
+
+
+xat <- c(1,
+         2,
+         3)
+b <- boxplot(df,
+             xaxt="n",       # no x-axis
+             yaxt="n",
+             boxwex=0.45,    # boxwidth
+             lty=1,          # line type, 1 = solid
+             staplewex=0,    # no staples
+             log="",         # no log scaling
+             ylim=c(1, 4),
+             at=xat,
+             border=cols,
+             lwd=2,
+             outline=FALSE
+)          # line weight
+
+stripchart(apply(df, 2, as.list),
+           vertical=TRUE,
+           method="jitter",
+           add=TRUE,
+           pch=20,
+           cex=0.4,
+           col=cols,
+           at=xat,
+           jitter=0.05)
+
+title("Unc lengths\n (late G2 phase)", font.main=1, cex.main=1.6, line=0)
+title(ylab=expression(paste("Length (", "μ", "m)", sep="")), line=2.2)
+
+axis(2, at=seq(1, 4, 0.5), labels=TRUE, col.ticks=1, lwd=1)
+
[…]

### 2018-02-24 latex/paper.tex
Updates, fixes from editing

@@
 \usepackage{titlesec}
+
+%% \usepackage{xcolor}
+%% \pagecolor[RGB]{42,47,56}
+%% \color[RGB]{189,189,161}
 
@@
   We provide evidence that these hyperelongated TZs are functionally
-  defective, and that the Exo84 mutant \textit{onion rings} decouples
-  TZ hyperelongation from the role for \PIP{} in cilium-membrane
-  tethering.
+  defective, and that the Exo84 mutant \textit{onion rings}
+  \textit{onr} decouples TZ hyperelongation from the role for
+  \PIP{} in cilium-membrane tethering.
   Our observations reveals a requirement for \PIP{} at the base of cilia
@@
 In the Drosophila male germline, nascent TZs first assemble on basal bodies
-during early G2 phase in spermatocytes and anchor directly to the plasma membrane.
+during G2 phase in spermatocytes and anchor to the plasma membrane.
 This is followed by establishment of cilium-membrane connections
@@
 and 50\% humidity.
-Stocks expressing $\beta$\textit{2tubulin}::\textit{Styp}\textbackslash{SigD} (chromosome \textit{3})
-and $\beta$\textit{2tub}::YFP-Sktl (chromosome \textit{2})
+Stocks expressing $\beta$\textit{2t}::\textit{Styp}\textbackslash{SigD} (chromosome \textit{3})
+and $\beta$\textit{2t}::YFP-Sktl (chromosome \textit{2})
 were described previously \citep{wei2008depletion, fabian2010phosphatidylinositol}.
-$\beta$\textit{2tub}::mCherry-Sktl was made as in \citep{wei2008depletion},
+$\beta$\textit{2t}::mCherry-Sktl was made as in \citep{wei2008depletion},
 and a \textit{P}-element insertion on chromosome \textit{2} was used for rescue using the low-level
@@
 \textit{Sp}/\textit{CyO}; Unc-GFP was originally provided by M. Kernan \citep{baker2004mechanosensory}.
-Stocks expressing GFP-tagged Chibby, B9d1, B9d2, Cc2d2a and Mks1 were generously
+Stocks expressing GFP-tagged Chibby, B9d1, B9d2, Cc2d2a and Mks1 were
 provided by B. Durand \citep{enjolras2012drosophila, vieillard2016transition}.
@@
 The edges of the coverslip were sealed with nail polish
-and the specimen was visualized immediately using a fluorescence microscope.
+and the specimen was visualized immediately using an epifluorescence microscope.
 
@@
 chamber in the dark at room temperature. They were then squashed
-in PBS and visualized immediately.
+in PBS and imaged live.
 
@@
 \subsection{Statistical methods}
-Statistical analysis and graphing was performed using R.
+Statistical analysis and graphing was performed using R (version 3.4)
+\citep{r}.
 A Gaussian jitter was applied when plotting

### 2018-02-24 figures/figure-2/plot2.R
Updates for plots
1. Reduced width to allow panel placement in figure
2. Matched colour for "sigd" to purple for consistency between plots

@@ -1,7 +1,7 @@
 #' Plotting Unc-GFP lengths
 #' n = 30-60
 
-#png(filename="unc.png", width=7, height=6,units="in", res=600)
+png(filename="unc.png", width=3.5, height=6,units="in", res=600)
 
 # import data
 df <- read.csv('unc.csv', header=TRUE)
@@ -17,7 +17,7 @@ df <- addNoise(df)
 
 library(RColorBrewer)
 
-cols <- brewer.pal(9,"Set1")[c(9,4,5)]
+cols <- brewer.pal(9,"Set1")[c(9,2,4)]
 
 par(bty="n",
     mar=c(2, 4, 3, 0),  # plot margins b-l-t-r
@@ -80,7 +80,5 @@ lines(c(xat[1], xat[1]), c(yat+offset, yat))
 lines(c(xat[2], xat[2]), c(yat+offset, yat))
 text((xat[1] + xat[2])/2, yat-2*offset, expression(italic('p')<0.01), cex=1)
 
-
-
-#dev.off()
+dev.off()
 

### 2018-02-25 latex/paper.tex
Updates from edits

@@
 \usepackage{titlesec}
-
-%% \usepackage{xcolor}
-%% \pagecolor[RGB]{42,47,56}
-%% \color[RGB]{189,189,161}
 
@@
 neurological defects \citep{valente2014primary},
-skeletal abnormalities \citep{hammarsjo2017novel, waters2011ciliopathies},
-and infertility \citep{inaba2016sperm} in addition to other phenotypes.
+skeletal abnormalities \citep{hammarsjo2017novel},
+and infertility \citep{inaba2016sperm} in addition to other phenotypes
+\citep{waters2011ciliopathies}.
 
@@
 The TZ is the proximal-most region of the cilium and
-acts as a diffusion barrier that regulates the
+functions as a diffusion barrier that regulates the
 bi-directional transport of protein and lipid cargo at the base of the cilium
 \citep{reiter2012base, szymanska2012transition}.
-The TZ is essential for cilium formation (ciliogenesis) and cilium-associated
+The TZ is essential for cilium formation (ciliogenesis) and cilium-based
 signalling.
 The conserved TZ protein CEP290, for example, is mutated in at least
-six different ciliopathies, and is essential for cilium formation in both humans
+six different ciliopathies with a spectrum of clinical features and severities
+, and is important for cilium formation
+and function in both humans \citep{shimada2017vitro, stowe2012centriolar}
 and Drosophila \citep{basiri2014migrating}.
@@
 
+Ciliogenesis begins with the assembly of TZ proteins at the tips of
+the basal body.
+This nascent TZ undergoes maturation, where the structure and protein
+composition changes, allowing for anchoring of the TZ to the membrane and
+establishment of a compartmentalized space bounded by the ciliary membrane
+and the TZ.
 In the Drosophila male germline, nascent TZs first assemble on basal bodies
@@
 through a poorly understood mechanism
-involving microtubule rearrangements \citep{gottardo2013cilium} and a
+involving microtubule rearrangements \citep{gottardo2013cilium}, and a
 ciliary membrane that persists through meiosis \citep{riparbelli2012assembly}.
-Ciliogenesis begins with the assembly of TZ proteins at the tips of
-the nascent basal body.
-This is followed by the anchoring of the TZ to the membrane and
-establishment of a compartmentalized space bounded by the ciliary membrane
-and the TZ.
 TZ maturation has been described in
@@
 \textit{Drosophila melanogaster} \citep{gottardo2013cilium}
-and is most readily observed by an increase in TZ length from nascent to mature.
-This are probably similar to the initial steps of TZ assembly and reorganization
+and is most readily observed by an increase in TZ length.
+We expect that this process is analogous to the initial steps of TZ assembly
+through sequential recruitment of TZ proteins and reorganization
 in vertebrates.
 
-Here, we show that the lipid phosphatidylinositol 4,5-bisphosphate (\PIP{})
-is essential for proper TZ maturation in developing male germ cells in \textit{D. melanogaster}.
-\PIP{} is a membrane lipid and one of seven phosphoinositides (PIPs)
-present in eukaryotic cells.
-It is primarily enriched at the plasma membrane and the base of cilia,
-but its functions in ciliogenesis have not been studied.
-We found that reduction of cellular \PIP{}
-by expression of the bacterial PIP phosphatase SigD
+Here, we show that the membrane lipid phosphatidylinositol 4,5-bisphosphate (\PIP{})
+is essential for proper TZ maturation in developing male germ cells
+in \textit{D. melanogaster}.
+\PIP{} is relatively enriched within the plasma membrane and the base of cilia
+in the male germline.
+We show that expression of the bacterial PIP phosphatase SigD
 or by inactivation of the PIP 5-kinase Skittles (Sktl) that localizes to cilia
@@
 Our results suggest that the plasma membrane lipid \PIP{} regulates TZ length,
-maturation and function, acting to support ciliogenesis.
+maturation and function, thereby acting to support ciliogenesis.
 
@@
 wild-type controls and \sigd{}.
-As shown in Figure 1A, Cep290 grew to much longer lengths in \sigd{}
+As shown in Figure 1A,
+while Cep290 on nascent TZs look similar in wild-type and \sigd{}, 
+it grew to significantly longer lengths in \sigd{}
 compared to wild-type controls.
@@
 correlation between Cep290 and Ana1 length.
-This phenotype was not specific to Cep290;
+This hyperelongation phenotype was not specific to Cep290;
 all TZ markers examined showed hyperelongation, including
@@
 and showed high intra-cyst correlation (\textgreater 0.95) suggestive
-of a dosage-based response to a shared cellular factor.
+of a dosage-based response to a shared cellular factor,
+presumably SigD.
 Hyperelongated TZs persisted through meiosis.
@@
 was frequently aberrant,
-either lacking symmetry completely or containing triplet microtubules instead of doublets
-\citep{wei2008depletion}.
+either lacking symmetry completely or containing triplet microtubules
+instead of doublets \citep{wei2008depletion}.
 
@@
 proteins that function at the cilium transition zone (TZ).
-Often, a single gene is linked to multiple ciliopathies with distinct phenotypes
-and severities.
+Often, a single gene is linked to multiple ciliopathies with
+a spectrum of phenotypes and severities.
 For example, \textit{CEP290} is linked to at least six different
@@
 function, and may be affected by genetic modifiers in an affected individual
-\citep{zaghloul2010functional}.
+\citep{zaghloul2010functional, khanna2009common, leitch2008hypomorphic}.
 Animal models with partial loss of TZ function may therefore provide
@@
 \begin{enumerate}[label={(\Alph*)}, nolistsep]
-\item \sigd{} expression induces Cep290 hyperelongation in mature (late G2 phase) cilia.
+\item \sigd{} expression induces Cep290 hyperelongation in mature cilia.
+  Stages correspond to descriptions in \citep{cenci1994chromatin}.
 \item Paired Ana1-Cep290 lengths in nascent and mature cilia ($n$ \textgreater 30).

### 2018-02-25 figures/figure-3/plot.R
Initial commit

@@ -1,0 +1,72 @@
+#' Plotting Unc-GFP lengths
+#' n = 30-60
+
+png(filename="taxol.png", width=6, height=3,units="in", res=600)
+
+# import data
+df <- read.csv('taxol.csv', header=TRUE)
+df <- cbind(df[,5], df[,6], df[,3], df[,4], df[,1], df[,2])
+df[df < 0.5] <- NA
+    
+addNoise <- function(mtx) {
+    if (!is.matrix(mtx)) mtx <- matrix(mtx, byrow = TRUE, nrow = 1)
+    random.stuff <- matrix(runif(prod(dim(mtx)), min = -0.0001, max = 0.01), nrow = dim(mtx)[1])
+    random.stuff + mtx
+}
+
+df <- addNoise(df)
+
+library(RColorBrewer)
+
+cols <- brewer.pal(9,"Set1")[c(9,4)]
+
+par(bty="n",
+    mar=c(2, 4, 3, 0),  # plot margins b-l-t-r
+    las=1,              # horizontal labels
+    tcl=-.25,           # tick length
+    font.main=1,        # plain font
+    mgp=c(2.5, 0.5, 0),  # axis spacings
+    cex.lab=1.6,
+    cex.axis=1.4,
+    ps=12
+)
+
+
+xat <- c(1,
+         2,
+         3, 4, 5, 6)
+b <- boxplot(df,
+             xaxt="n",       # no x-axis
+             yaxt="n",
+             boxwex=0.45,    # boxwidth
+             lty=1,          # line type, 1 = solid
+             staplewex=0,    # no staples
+             log="",         # no log scaling
+             ylim=c(0, 3),
+             at=xat,
+             border=cols,
+             lwd=2,
+             outline=FALSE
+)          # line weight
+
+stripchart(apply(df, 2, as.list),
+           vertical=TRUE,
+           method="jitter",
+           add=TRUE,
+           pch=20,
+           cex=0.4,
+           col=cols,
+           at=xat,
+           jitter=0.05)
+
+title("Cep290 lengths\n (late G2 phase)", font.main=1, cex.main=1.6, line=0)
+title(ylab=expression(paste("Length (", "μ", "m)", sep="")), line=2.2)
+
+axis(2, at=seq(0, 3, 0.5), labels=TRUE, col.ticks=1, lwd=1)
+
+temp.labels = c("Control", "SigD")
+legend("topleft", cex=1.3, col=cols, lty=1, lwd=2, temp.labels, bty="n")
+
+
+dev.off()
+

### 2018-02-25 figures/figure-3/plotbayes.R

@@ -1,0 +1,39 @@
+#' Perform fully Bayesian linear regression
+#' and plot Monte Carlo draws
+#'
+
+library(rstan)
+library(shinystan)
+library(magrittr)
+
+rstan_options(auto_write = TRUE)
+options(mc.cores = parallel::detectCores())
+
+df <- read.csv("taxolglm.csv")
+
+# Simple linear regression model
+lm.a <- df$length ~ df$pip2 + df$taxol
+
+# Linear regression model with interaction term
+lm.b <- df$length ~ df$pip2 + df$taxol + df$taxol*df$pip2
+
+#' Run Monte Carlo simulation
+#' @param y response variable,
+#'   which is Cep290 length in our case
+#' @param X model matrix
+#' 
+runStan <- function(y, X) {
+  stan("bayeslm.stan",
+       data = list(
+         y = y,
+         X = X,
+         J = nrow(X),
+         K = ncol(X)),
+       chains = 4,
+       iter = 2000)
+}
+
+fit.a <- runStan(df$length, lm.a %>% model.matrix)
+fit.b <- runStan(df$length, lm.b %>% model.matrix)
+
+# TODO plotting

### 2018-02-26 latex/paper.tex
Various edits

@@
 the basal body.
-This nascent TZ undergoes maturation, where the structure and protein
+This nascent TZ undergoes maturation, during which its structure and protein
 composition changes, allowing for anchoring of the TZ to the membrane and
@@
 In the Drosophila male germline, nascent TZs first assemble on basal bodies
-during G2 phase in spermatocytes and anchor to the plasma membrane.
-This is followed by establishment of cilium-membrane connections
-through a poorly understood mechanism
-involving microtubule rearrangements \citep{gottardo2013cilium}, and a
+during early G2 phase in spermatocytes and anchor to the plasma membrane.
+This is followed by anchoring of cilia to the plasma membrane,
+rearrangment of microtubules in the axoneme \citep{gottardo2013cilium},
+and establishment of a
 ciliary membrane that persists through meiosis \citep{riparbelli2012assembly}.
@@
 \textit{Drosophila melanogaster} \citep{gottardo2013cilium}
-and is most readily observed by an increase in TZ length.
-We expect that this process is analogous to the initial steps of TZ assembly
-through sequential recruitment of TZ proteins and reorganization
-in vertebrates.
+and is most readily observed by an increase in TZ length
+in the Drosophila male germline.
 
@@
 We show that expression of the bacterial PIP phosphatase SigD
-or by inactivation of the PIP 5-kinase Skittles (Sktl) that localizes to cilia
+or inactivation of the PIP 5-kinase Skittles (Sktl) that localizes to cilia
 induces longer than normal TZs without affecting TZ assembly.
@@
 due in part to defects in flagellar biosynthesis \citep{wei2008depletion}.
-To understand whether this was due to aberrant TZ function,
+To examine whether this may be caused by aberrant TZ function,
 we examined the localization of fluorescently-labelled
@@
 and the TZ protein Cep290 \citep{basiri2014migrating}
-during early steps of cilium assembly in spermatocytes in both
+during early steps of cilium assembly in spermatocytes in
 wild-type controls and \sigd{}.
-As shown in Figure 1A,
+As shown in Figure 1,
 while Cep290 on nascent TZs look similar in wild-type and \sigd{}, 
@@
 Chibby \citep{enjolras2012drosophila} and
-MKS \citep{slaats2015mks1, vieillard2016transition} proteins (Figure 1).
+MKS \citep{slaats2015mks1, vieillard2016transition} proteins (Figure 1D).
 TZ hyperelongation was a highly penetrant phenotype (\textgreater 90\%)
@@
 Despite TZ hyperlongation, however, axonemes were able to
-elongate post-meiosis (Figure 1).
+elongate post-meiosis (Figure 1E).
 As we showed previously, the ultrastructure of these axonemes
@@
 under the same promoter.
-We found that Sktl expression was able to suppress TZ elongation in a cilium-autonomous
-manner (Figure 2A and B).
+We found that Sktl expression was able to suppress TZ elongation
+in a cilium-autonomous manner (Figure 2A and B).
 We also found that \textit{sktl} clones using Flp/FRT-based mitotic recombination
-showed penetrant TZ hyperelongation (Figure 2C).
+showed TZ hyperelongation (Figure 2C).
 
 Since Sktl expression suppressed TZ hyperelongation,
-we investigated whether Sktl could localize to centrioles or cilia in the Drosophila germline.
+we investigated whether Sktl could localize to centrioles or cilia
+in the Drosophila germline.
 Similar to the human PIPKI$\gamma$ isoform \citep{xu2014pipkigamma},
@@
 As shown in Figure 2, Drosophila PIPKIs arose from the recent duplication of
-the ancestral PIPKI gene, and are not orthologous to specific vertebrate PIPKI isoforms.
+the ancestral PIPKI gene,
+and are not orthologous to specific vertebrate PIPKI isoforms.
 Sktl has diverged more than its paralog PIP5K59B, and seems
-to be functionally related to PIPKI$\gamma$ in its roles at cilia.
+to be functionally related to PIPKI$\gamma$ in its roles at cilia,
+as well as the \textit{C. elegans} PPK-1 \citep{xu2014pipkigamma}.
 However, unlike the human PIPKI$\gamma$, which functions to license TZ assembly
@@
 Cp110 is dispensable for cilium formation in Drosophila \citep{franz2013cp110}
-and we found its localization to be unaffected in \sigd{} (supplementary figure 1).
+and we found its localization to be unaffected in \sigd{} (Supplementary figure 1).
 
-\subsection{Hyperelongated transition zones show signs of functional defects}
+\subsection{Hyperelongated transition zones exhibit signs of functional defects}
 While shorter spermatocyte TZs have been reported in mutants of TZ proteins in Drosophila
 \citep{vieillard2016transition, pratt2016drosophila},
-no genetic manipulation has been reported to induce hyperelongated TZs.
+no genetic manipulation has been shown to induce hyperelongated TZs.
 We sought to examine whether TZ hyperelongation due to SigD expression
@@
 the basal body and migrates along the growing axoneme, maintaining a ciliary compartment
-at the distal-most ~5$\mu$m where tubulin is presumably incorporated into the axoneme.
+at the distal-most {\raise.17ex\hbox{$\scriptstyle\sim$}}5$\mu$m where tubulin
+is presumably incorporated into the axoneme.
 We found that
@@
 and we find that these hyperelongated Unc signals persist into cellular elongation
-despite elongation of the axoneme.
+despite elongation of the axoneme (Figure 3).
 
-%% reword this, paragraph is garbage
 We previously described the presence of occasional triplet microtubules
@@
 and high intra-cyst correlation.
-We found that treatment of germ cells with Paclitaxel as in \citep{riparbelli2013unique}
+We found that treatment of germ cells with Taxol as in \citep{riparbelli2013unique}
 could increase the penetrance of this phenotype.
-Paclitaxel treatment stabilizes microtubules and is thought to disrupt TZ maturation
-by interrupting microtubule rearrangements, and similarly induces much longer cilia.
-Paclitaxel treatment alone did not induce this phenotype in wild-type controls in our hands
+Taxol treatment stabilizes microtubules and is thought to disrupt TZ maturation
+by interrupting microtubule rearrangements, and similarly induces much longer cilia
+\citep{riparbelli2012assembly}.
+Taxol treatment alone did not induce this phenotype in wild-type controls in our hands
 at varying concentrations ($p$ <0.01 with 5\% penetrance),
@@
 It is possible that the TZ defect allows C-tubules and some centriolar proteins
-to migrate with it to the distal end.
-We did not observe this behaviour with Asterless,
-a migratory protein that localizes to the outer
-ring of centrioles ($p$ <0.01).
+to migrate to the distal end.
+We did not observe this behaviour with Asterless (CEP152)
+\citep{dzhindzhev2010asterless, blachon2008drosophila},
+another centriolar protein ($p$ <0.01), suggesting that these TZ-distal
+sites are not fully centriolar in protein composition.
 
 \subsection{The \textit{onion rings} mutant decouples defects found in cells with reduced levels of \PIP{}}
-A heterozygous mutation in the human \textit{EXOC8},
-the human ortholog of yeast Exo84, is linked to
-Joubert syndrome \citep{dixon2012exome}.
-Exo84 is a component of the octameric exocyst complex, which binds
-\PIP{} and regulates membrane trafficking at the plasma membrane.
 We previously showed that male flies homozygous for the \textit{onion rings}
@@
 similar to \sigd{} \citep{wei2008depletion}.
+Exo84 is a component of the octameric exocyst complex, which binds
+\PIP{} and regulates membrane trafficking at the plasma membrane.
 To investigate whether defects in TZ hyperelongation could be explained by
@@
 Although we were not able to determine the localization of Exo84 due to the
-lack of available antibodies,
-we found that Sec6 and Exo70 localized to the plasma membrane as expected,
-but were not enriched at the cilium (Figure 5C).
+lack of available reagents,
+we found that Exo70 localized to centrioles (Figure 4D),
+but not Sec6 (Supplementary figure 2).
+Exo70 can directly bind to \PIP{} \citep{he2007exo70}.
 Our results suggest that the exocyst may act downstream of \PIP{} to
@@
 In the Drosophila male germline, TZ maturation follows the initial
-assembly of TZ proteins on the nascent basal body in the cytoplasm
+assembly of a nascent TZ on the basal body in the cytoplasm
 followed by anchoring at the plasma membrane.
 TZ maturation involves microtubule rearrangements and TZ elongation,
-which leads to cilium-membrane attachment.
-Loss of \PIP{}, a membrane lipid largely at the plasma membrane,
-disrupts this process.
+which leads to cilium-plasma membrane attachment.
+We found that loss of \PIP{}, a membrane lipid enriched at the plasma membrane,
+affects this process of TZ maturation.
 It causes excessive lengthening of the TZ,
 and disrupts membrane-cilium connections.
-Thus, intermediate steps during TZ maturation require \PIP{}.
 

### 2018-02-26 figures/figure-3/plotbayes.R
Minor documentation change

@@ -1,4 +1,5 @@
-#' Perform fully Bayesian linear regression
+#' Perform fully Bayesian linear regression of
+#' the effect of Taxol and PIP2 levels on Cep290 length
 #' and plot Monte Carlo draws
 #'
 
@@ -21,7 +22,6 @@ lm.b <- df$length ~ df$pip2 + df$taxol + df$taxol*df$pip2
 #' @param y response variable,
 #'   which is Cep290 length in our case
 #' @param X model matrix
-#' 
 runStan <- function(y, X) {
   stan("bayeslm.stan",
        data = list(

### 2018-02-26 latex/paper.tex
Various edits

@@
 We did not observe this behaviour with Asterless (CEP152)
-\citep{dzhindzhev2010asterless, blachon2008drosophila},
-another centriolar protein ($p$ <0.01), suggesting that these TZ-distal
+\citep{dzhindzhev2010asterless, blachon2008drosophila} ($p$ <0.01),
+another centriolar protein, suggesting that these TZ-distal
 sites are not fully centriolar in protein composition.
@@
 of ciliopathies such as micrognathia, and a role for the LCCS1 protein
-Gle3 in cilia.
+Gle1 in cilia \citep{}.
 In addition, all three human PIPKI isoforms are highly expressed in testes
@@
   Stages correspond to descriptions in \citep{cenci1994chromatin}.
-\item Paired Ana1-Cep290 lengths in nascent and mature cilia ($n$ \textgreater 30).
+\item Paired Ana1-Cep290 lengths in nascent and mature cilia.
 \item \sigd{} expression induces hyperelongation of other TZ markers, such as Cby, Mks

### 2018-02-27 latex/make.sh
Unnecessary due to switching to latexmk

@@ -1,5 +1,0 @@
-pdflatex paper.tex > /dev/null  
-bibtex paper > /dev/null
-pdflatex paper.tex > /dev/null 
-pdflatex paper.tex > /dev/null 
-date

### 2018-02-27 latex/paper.tex
Additional edits

@@
 \usepackage[numbers]{natbib}
-\usepackage[draft]{graphicx}  %% remove [draft] to compile with pictures
+\usepackage{graphicx}
 \graphicspath{{../figures/}}
@@
 \section{Discussion}
-Cilia are essential for proper human development, and their disruption
-can cause genetic disorders with severities ranging from congenital-
-lethal \citep{}
-to late onset \citep{}.
-A large number of ciliopathies are associated with genes that encode for
-proteins that function at the cilium transition zone (TZ).
+Cilia are tiny organelles that are essential for proper human development
+and cilium-associated developmental disorders are known as ciliopathies.
+A large number of ciliopathies are linked to genes that encode
+transition zone (TZ) proteins.
 Often, a single gene is linked to multiple ciliopathies with
@@
 %%
-%    FIGURE 2
-%
-\textbf{Figure 2. Sktl is important for transition zone maturation and localizes to basal bodies.}
-\begin{enumerate}[label={(\Alph*)}, nolistsep]
-\item Expression of full-length Sktl suppresses \sigd{}-induced TZ hyperelongation.
-\item Quantification of Cep290 and Ana1 lengths from control, \sigd{} and Sktl; \sigd{} ($n$\textgreater 60) from (A).
-\item \textit{sktl}$^{2.3}$ clones exhibit TZ hyperelongation. Cilia are marked using
-  Unc-GFP.
-\item Phylogenetic tree of PIP5Ks showing conservation of cilium-associated functions.
-  The scale bar represents expected amino acid substitutions per site and branch support values are shown in red (a value of 1 indicates maximum support).
-Abbreviations: Cele (\textit{Caenorhabditis elegans}), Spur (\textit{Strongylocentrotus purpuratus}), Amel (\textit{Apis mellifera}), Aaeg (\textit{Aedes aegypti}), Dana (\textit{Drosophila ananassae}), Dmel (\textit{Drosophila melanogaster}), Hsap (\textit{Homo sapiens}), Mmus (\textit{Mus musculus}), Xtro (\textit{Xenopus tropicalis}), Cint (\textit{Ciona intestinalis}), Scer (\textit{Saccharomyces cerevisiae}).
-\end{enumerate}
+%%%%
+%%%    FIGURE 2
+%%%
+%%\textbf{Figure 2. Sktl is important for transition zone maturation and localizes to basal bodies.}
+%%\begin{enumerate}[label={(\Alph*)}, nolistsep]
+%%\item Expression of full-length Sktl suppresses \sigd{}-induced TZ hyperelongation.
+%%\item Quantification of Cep290 and Ana1 lengths from control, \sigd{} and Sktl; \sigd{} ($n$\textgreater 60) from (A).
+%%\item \textit{sktl}$^{2.3}$ clones exhibit TZ hyperelongation. Cilia are marked using
+%%  Unc-GFP.
+%%\item Phylogenetic tree of PIP5Ks showing conservation of cilium-associated functions.
+%%  The scale bar represents expected amino acid substitutions per site and branch support values are shown in red (a value of 1 indicates maximum support).
+%%Abbreviations: Cele (\textit{Caenorhabditis elegans}), Spur (\textit{Strongylocentrotus purpuratus}), Amel (\textit{Apis mellifera}), Aaeg (\textit{Aedes aegypti}), Dana (\textit{Drosophila ananassae}), Dmel (\textit{Drosophila melanogaster}), Hsap (\textit{Homo sapiens}), Mmus (\textit{Mus musculus}), Xtro (\textit{Xenopus tropicalis}), Cint (\textit{Ciona intestinalis}), Scer (\textit{Saccharomyces cerevisiae}).
+%%\end{enumerate}
+%%
+%%\begin{figure}[ht]
+%%  \includegraphics[scale=0.9]{figure-2/figure2.png}
+%%\end{figure}
+%%\newpage
+%%
+%%
+%%%%
+%%%    FIGURE 3
+%%%
+%%\textbf{Figure 3. Hyperelongated transition zones display functional defects.}
+%%\begin{enumerate}[label={(\Alph*)}, nolistsep]
+%%\item
+%%\item
+%%\item
+%%\item
+%%\end{enumerate}
+%%
+%%\begin{figure}[ht]
+%%  \includegraphics[scale=0.8]{figure-3/figure3.png}
+%%\end{figure}
+%%\newpage
+%%
+%%
+%%%%%
+%%%%    FIGURE 4
+%%%%
+%%\textbf{Figure 4. The \textit{onion rings} (\textit{onr}) allele of \textit{d}Exo84 decouples TZ hyperlongation from loss of plasma membrane contacts.}
+%%\begin{enumerate}[label={(\Alph*)}, nolistsep]
+%%\item Cells mutant for \textit{onr} do not display hyperelongated TZs marked with acetylated tubulin.
+%%\item Quantification from (A).
+%%\item Cells mutant for \textit{onr} display loss of plasma membrane tethering.
+%%\end{enumerate}
+%%
+%%\begin{figure}[ht]
+%%  \includegraphics[scale=0.9]{figure-4/figure4.png}
+%%\end{figure}
+%%\newpage
+%%
+%%
+\end{document}
 
-\begin{figure}[ht]
-  \includegraphics[scale=0.9]{figure-2/figure2.png}
-\end{figure}
-\newpage
-
-%%
-%    FIGURE 3
-%
-\textbf{Figure 3. Hyperelongated transition zones display functional defects.}
-\begin{enumerate}[label={(\Alph*)}, nolistsep]
-\item
-\item
-\item
-\item
-\end{enumerate}
-
-\begin{figure}[ht]
-  \includegraphics[scale=0.8]{figure-3/figure3.png}
-\end{figure}
-\newpage
-
-%%%
-%%    FIGURE 4
-%%
-\textbf{Figure 4. The \textit{onion rings} (\textit{onr}) allele of \textit{d}Exo84 decouples TZ hyperlongation from loss of plasma membrane contacts.}
-\begin{enumerate}[label={(\Alph*)}, nolistsep]
-\item Cells mutant for \textit{onr} do not display hyperelongated TZs marked with acetylated tubulin.
-\item Quantification from (A).
-\item Cells mutant for \textit{onr} display loss of plasma membrane tethering.
-\end{enumerate}
-
-\begin{figure}[ht]
-  \includegraphics[scale=0.9]{figure-4/figure4.png}
-\end{figure}
-\newpage
-
-\end{document}
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: t
+%%% End:

### 2018-02-27 latex/make.sh

@@ -1,0 +1,5 @@
+pdflatex paper.tex > /dev/null  
+bibtex paper > /dev/null
+pdflatex paper.tex > /dev/null 
+pdflatex -synctex=1 paper.tex > /dev/null 
+date

### 2018-02-28 figures/figure-3/plotbayes.R
Plot MC draws

@@ -6,7 +6,9 @@
 library(rstan)
 library(shinystan)
 library(magrittr)
+library(RColorBrewer)
 
+set.seed(42)
 rstan_options(auto_write = TRUE)
 options(mc.cores = parallel::detectCores())
 
@@ -36,4 +38,71 @@ runStan <- function(y, X) {
 fit.a <- runStan(df$length, lm.a %>% model.matrix)
 fit.b <- runStan(df$length, lm.b %>% model.matrix)
 
-# TODO plotting
+#'
+#'
+#'
+#'
+#'
+
+
+add.alpha <- function(col, alpha=1) {
+  if (missing(col)) { stop("Please provide a vector of colours.") }
+  apply(sapply(col, col2rgb)/255, 2, function(x)
+    rgb(x[1], x[2], x[3], alpha=alpha))
+}
+
+cols <- brewer.pal(9, "Set1")
+dev.off()
+par(bty="n",
+    mar=c(2, 5, 2, 2),
+    las=1,
+    tcl=-.25,
+    font.main=1,
+    mgp=c(2.5, 0.5, 0),
+    mfrow=c(2, 1))
+
+plot(1,
+     type="n",
+     ylim=c(0, 1000),
+     xlim=c(-1, 2),
+     ylab="Frequency",
+     main="Length = b0 + PIP2 + Taxol")
+
+plotMC <- function(stan.out, str, breaks) {
+  coefs <- rstan::extract(stan.out, str)[[1]]
+  for (i in 1:ncol(coefs)) {
+    hist(coefs[,i],
+         breaks=breaks[i],
+         xlim=c(min(coefs), max(coefs)),
+         col=add.alpha(cols[i], 0.9),
+         lty="blank",
+         add=TRUE)
+  }
+}
+
+plotMC(fit.a, "coeff", rep(30, 3))
+legend("topleft",
+       c("Intercept", "PIP2", "Taxol"),
+       col=cols,
+       lty=1, 
+       lwd=2,
+       cex=0.9,
+       bty="n")
+plot(1,
+     type="n",
+     ylim=c(0, 500),
+     xlim=c(-1, 2),
+     ylab="Frequency",
+     main="Length = b0 + PIP2 + Taxol + PIP2*Taxol")
+
+plotMC(fit.b, "coeff", rep(30, 4))
+
+
+legend("topleft",
+       c("Intercept", "PIP2", "Taxol", "PIP2:Taxol"),
[…]

### 2018-03-01 latex/paper.tex
Various edits

--- 2018-02-26 latex/paper.tex
@@
 \usepackage[numbers]{natbib}
-\usepackage[draft]{graphicx}  %% remove [draft] to compile with pictures
+\usepackage[draft]{graphicx}
 \graphicspath{{../figures/}}
@@
 \section{Discussion}
-Cilia are essential for proper human development, and their disruption
-can cause genetic disorders with severities ranging from congenital-
-lethal \citep{}
-to late onset \citep{}.
-A large number of ciliopathies are associated with genes that encode for
-proteins that function at the cilium transition zone (TZ).
-Often, a single gene is linked to multiple ciliopathies with
-a spectrum of phenotypes and severities.
-For example, \textit{CEP290} is linked to at least six different
-cilium-associated human disorders.
-It is likely that these mutations do not completely abolish CEP290
-function, and may be affected by genetic modifiers in an affected individual
+Cilia are tiny organelles that are essential for proper human development.
+Many human disorders of cilia are associated with genes that encode
+transition zone (TZ) proteins.
+For example, mutations in the conserved TZ protein CEP290
+are linked to more than 6 different ciliopathies,
+ranging on a spectrum of clinical phenotypes and severities.
+Most of these mutations are likely to be hypomorphic
+and may be affected by genetic modifiers in affected individuals.
 \citep{zaghloul2010functional, khanna2009common, leitch2008hypomorphic}.
-Animal models with partial loss of TZ function may therefore provide
-insight on intermediate phenotypes associated with human disease.
-Here, we found that reduced levels of the membrane lipid \PIP{},
-which is known to be enriched at the base of cilia,
-affects TZ maturation, but not assembly,
-leading to hyperelongated TZs that show signs of functional defects, and
-may represent one such modifier for TZ function.
+Animal models with partial loss of TZ function may therefore
+provide insight on intermediate phenotypes associated with human disease
+and their cell biological basis.
+In this paper, we described a novel role for the membrane lipid
+phosphatidylinositol 4,5-bisphosphate (\PIP{}) in regulating TZ function.
 
-In the Drosophila male germline, TZ maturation follows the initial
-assembly of a nascent TZ on the basal body in the cytoplasm
-followed by anchoring at the plasma membrane.
-TZ maturation involves microtubule rearrangements and TZ elongation,
-which leads to cilium-plasma membrane attachment.
-We found that loss of \PIP{}, a membrane lipid enriched at the plasma membrane,
-affects this process of TZ maturation.
-It causes excessive lengthening of the TZ,
-and disrupts membrane-cilium connections.
+The initial steps of ciliogenesis involve the assembly of a nascent
+TZ on the basal body.
+This nascent TZ ``matures'' through sequential assembly of additional
+TZ proteins into a functional TZ capable of acting as a diffusion barrier
+and supporting axoneme elongation and ciliary signalling.
+In the Drosophila male germline, TZ maturation occurs during the
+extended G2 phase in spermatocytes prior to meiosis,
+and is readily observed by an increase in TZ length
+and various microtubule rearrangements.
+Axoneme elongation occurs in telophase II following meiosis in
+spermatids, where a functional TZ detaches from the basal body
+and migrates along the growing axoneme to compartmentalize the distal tip
+in Cep290-dependant manner \citep{basiri2014migrating}.
 
-We found that the type I phosphatidylinositol 4-phosphate kinase (PIPKI) Skittles
-suppresses TZ elongation in \sigd{} cells in a cilium-autonomous
-manner.
-We also found that cells mutant for \textit{sktl} contained hyperelongated
-TZs similar to SigD-expressing cells.
-Sktl also localizes to centrioles,
-and our results suggest that Skittles acts locally at cilia to
-regulate TZ length.
-PIPKI$\gamma$ is linked to lethal congenital contractural syndrome
-type 3 (LCCS3).
-It has previously been suggested that LCCS3 might represent a ciliopathy.
-PIPKI$\gamma$ is linked to LCCS3 with features reminiscent
-of ciliopathies such as micrognathia, and a role for the LCCS1 protein
-Gle1 in cilia \citep{}.
-In addition, all three human PIPKI isoforms are highly expressed in testes
-and PIPKI$\alpha$ and PIPKI$\beta$ are important for fertility in mice
-\citep{hasegawa2012phosphatidylinositol}.
+We found that reduction of \PIP{} levels in the male germline by expression
+of the lipid phosphatase SigD or mutation in the type I PIP kinase
+Skittles (Sktl) lead to much longer TZs by the end of spermatocyte G2 phase.
+Presumably, loss of \PIP{} abolishes a signal to stop TZ lengthening during
+a particular step in maturation.
+We were able rescue TZ hyperelongation by expression of full-length Sktl to
+a large degree.
+Interestingly, some cells showed cilium-autonomous suppression of lengths.
+Development of the Drosophila male germline occurs in syncytial ``cysts''
+of cells which share the same cytoplasm.
+Therefore, our results suggest that Skittles might function \textit{in situ}
+to regulate TZ maturation in these cells.
+
+In humans, \textit{PIPKI$\gamma$} is linked to lethal congenital contractural
+syndrome type 3 (LCCS3), which has been suggested to represent a ciliopathy
+\citep{}.
+The recent discovery of the role of LCCS1-associated GLE3 protein in cilia
+further shows this.
 
@@
 IgG (Molecular Probes) at 1:1000.
-DAPI was used to label chromatin at 1:1000.
+DAPI at 1:1000 was used to label chromatin.
 
@@
 \textbf{Figure 1. SigD expression induces transition zone hyperelongation.}
-\begin{enumerate}[label={(\Alph*)}, nolistsep]
-\item \sigd{} expression induces Cep290 hyperelongation in mature cilia.
-  Stages correspond to descriptions in \citep{cenci1994chromatin}.
-\item Paired Ana1-Cep290 lengths in nascent and mature cilia.
-\item \sigd{} expression induces hyperelongation of other TZ markers, such as Cby, Mks
-  and acetylated tubulin.
+\begin{enumerate}[label={\Alph*.}, nolistsep]
+\item Schematic diagram of the stages of ciliogenesis in the Drosophila male germline.
+  Stages in brackets correspond to those from \citep{cenci1994chromatin}.
+\item \sigd{} expression induces Cep290 hyperelongation in late G2 cilia.
+\item Paired Ana1-Cep290 lengths in early and late G2 phase in spermatocytes.
+  Numbers in red represent correlation between Cep290 and Ana1 lengths.
+\item \sigd{} expression induces hyperelongation of Chibby and Mks1.
 \item TZ hyperelongation persists through meiosis but does not affect
@@
 %%
-%    FIGURE 2
-%
+%%%%
+%%%    FIGURE 2
+%%%
 \textbf{Figure 2. Sktl is important for transition zone maturation and localizes to basal bodies.}
-\begin{enumerate}[label={(\Alph*)}, nolistsep]
+\begin{enumerate}[label={\Alph*.}, nolistsep]
 \item Expression of full-length Sktl suppresses \sigd{}-induced TZ hyperelongation.
@@
 \end{document}
+
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: t
+%%% End:

### 2018-03-01 figures/figure-3/plotbayes.R
Minor fix to plotting and general cleaning up

@@ -38,13 +38,6 @@ runStan <- function(y, X) {
 fit.a <- runStan(df$length, lm.a %>% model.matrix)
 fit.b <- runStan(df$length, lm.b %>% model.matrix)
 
-#'
-#'
-#'
-#'
-#'
-
-
 add.alpha <- function(col, alpha=1) {
   if (missing(col)) { stop("Please provide a vector of colours.") }
   apply(sapply(col, col2rgb)/255, 2, function(x)
@@ -52,7 +45,7 @@ add.alpha <- function(col, alpha=1) {
 }
 
 cols <- brewer.pal(9, "Set1")
-dev.off()
+
 par(bty="n",
     mar=c(2, 5, 2, 2),
     las=1,
@@ -97,9 +90,8 @@ plot(1,
 
 plotMC(fit.b, "coeff", rep(30, 4))
 
-
 legend("topleft",
-       c("Intercept", "PIP2", "Taxol", "PIP2:Taxol"),
+       c("Intercept", "PIP2", "Taxol", "PIP2*Taxol"),
        col=cols,
        lty=1, 
        lwd=2,

### 2018-03-03 figures/figure-3/plotbayes.R
Change placement to top of section

@@ -1,7 +1,6 @@
 #' Perform fully Bayesian linear regression of
 #' the effect of Taxol and PIP2 levels on Cep290 length
 #' and plot Monte Carlo draws
-#'
 
 library(rstan)
 library(shinystan)
@@ -21,8 +20,7 @@ lm.a <- df$length ~ df$pip2 + df$taxol
 lm.b <- df$length ~ df$pip2 + df$taxol + df$taxol*df$pip2
 
 #' Run Monte Carlo simulation
-#' @param y response variable,
-#'   which is Cep290 length in our case
+#' @param y response variable, which is Cep290 length in our case
 #' @param X model matrix
 runStan <- function(y, X) {
   stan("bayeslm.stan",
@@ -44,6 +42,18 @@ add.alpha <- function(col, alpha=1) {
     rgb(x[1], x[2], x[3], alpha=alpha))
 }
 
+plotMC <- function(stan.out, str, breaks) {
+  coefs <- rstan::extract(stan.out, str)[[1]]
+  for (i in 1:ncol(coefs)) {
+    hist(coefs[,i],
+         breaks=breaks[i],
+         xlim=c(min(coefs), max(coefs)),
+         col=add.alpha(cols[i], 0.9),
+         lty="blank",
+         add=TRUE)
+ }
+}
+
 cols <- brewer.pal(9, "Set1")
 
 par(bty="n",
@@ -60,18 +70,6 @@ plot(1,
      xlim=c(-1, 2),
      ylab="Frequency",
      main="Length = b0 + PIP2 + Taxol")
-
-plotMC <- function(stan.out, str, breaks) {
-  coefs <- rstan::extract(stan.out, str)[[1]]
-  for (i in 1:ncol(coefs)) {
-    hist(coefs[,i],
-         breaks=breaks[i],
-         xlim=c(min(coefs), max(coefs)),
-         col=add.alpha(cols[i], 0.9),
-         lty="blank",
-         add=TRUE)
-  }
-}
 
 plotMC(fit.a, "coeff", rep(30, 3))
 legend("topleft",

### 2018-03-03 figures/figure-1/plot.R
Clean up

@@ -93,6 +93,3 @@ lines(c(xat[7], xat[7]), c(yat-offset, (yat)))
 text((xat[5] + xat[7])/2, yat+3*offset, expression(italic('N.S.')), cex=1)
 
 dev.off()
-
-
-

### 2018-03-03 latex/make.sh
Unnecessary

@@ -1,5 +1,0 @@
-pdflatex paper.tex > /dev/null  
-bibtex paper > /dev/null
-pdflatex paper.tex > /dev/null 
-pdflatex -synctex=1 paper.tex > /dev/null 
-date

### 2018-03-03 latex/paper.tex
Fix vertical spacing, change template to 'report' instead of 'article' type

@@
 \documentclass[12pt, twoside, letterpaper]{article}
-\usepackage[margin=0.6in]{geometry}
+\usepackage[margin=0.8in]{geometry}
 \usepackage[parfill]{parskip}
@@
 \usepackage[numbers]{natbib}
-\usepackage[draft]{graphicx}
+\usepackage{graphicx}
 \graphicspath{{../figures/}}
@@
 \usepackage{titlesec}
+\usepackage{lineno}
+\usepackage{setspace}
 
-\bibliographystyle{unsrtapalike}
+% bibliography style
+\bibliographystyle{unsrtcurrbiol}
 
@@
 
-% new commands
+% newcommand
 \newcommand{\PIP}{PIP\textsubscript{2}}
@@
 \newcommand{\sktl}{\textit{sktl}}
+
+% renewcommand
 \renewcommand*{\Affilfont}{\footnotesize \normalfont}
@@
 
-\title{\bfseries\large Phosphatidylinositol 4,5-bisphosphate regulates cilium transition zone maturation in \textit{Drosophila melanogaster}}
+\title{\vspace{-1cm} \bfseries\large Phosphatidylinositol 4,5-bisphosphate regulates cilium transition zone maturation in \textit{Drosophila melanogaster}}
 \author[1,2]{Alind Gupta \thanks{\url{alind.gupta@mail.utoronto.ca}}}
 \author[1,2]{Julie A. Brill \thanks{\url{julie.brill@sickkids.ca} (Corresponding author)}}
+
 \affil[1]{\small Department of Molecular Genetics, University of Toronto, Toronto, ON M5S 1A8, Canada}
 \affil[2]{\small Program in Cell Biology, Hospital for Sick Children, Toronto, ON M5G 1X8, Canada}
-\date{}
+
+\date{\small \today}
 
@@
 \maketitle
-\raggedright
 
-\begin{abstract}
-  \vspace*{-0.7em}
-  Cilia are sensory organelles that are important for human development
-  and physiology.
-  A large number of genetic disorders affecting cilia are associated with
-  mutations in proteins that localize to the transition zone (TZ),
-  a structure at the base of cilia required for ciliogenesis and
-  regulation of trafficking in and out of the cilium.
-  Here, we report that the membrane lipid phosphatidylinositol
-  4,5-bisphosphate(\PIP{}) is essential for proper maturation and function
-  of TZs in the male \textit{Drosophila melanogaster} germline.
+\begin{doublespacing}
+  \begin{linenumbers}
+
+    \section{Summary}
+    Cilia are sensory organelles that are essential for human development
+    and physiology \citep{satir2010primary}.
+    They function primarily by relaying extracellular stimuli to cells
+    \citep{satir2010primary},
+    but can also act as motile propellers in certain cell types
+    \citep{bloodgood2010sensory}.
+    A large number of genetic disorders linked to cilium dysfunction are
+    associated with proteins that localize to the cilium transition zone (TZ),
+    a structure at the base of cilia that regulates trafficking in and out
+    of the cilium \citep{reiter2012base, szymanska2012transition}.
+    Despite numerous efforts to elucidate TZ proteins and their functions,
+    processes underlying maturation of TZs are not well understood.
+    We report a role for the membrane lipid phosphatidylinositol 4,5-bisphosphate
+    (\PIP{}) in TZ maturation and length regulation
+    in the \textit{Drosophila melanogaster} male germline.
     Reduction of cellular \PIP{} levels by expression of the
@@
     the type I phosphatidylinositol phosphate kinase (PIPKI) Skittles (Sktl)
-  induces hyperelongation of TZs following their docking at the plasma
-  membrane.
-  We provide evidence that these hyperelongated TZs are functionally
-  defective, and that the Exo84 mutant \textit{onion rings}
-  \textit{onr} decouples TZ hyperelongation from the role for
-  \PIP{} in cilium-membrane tethering.
-  Our observations reveals a requirement for \PIP{} at the base of cilia
-  in regulating TZ length and function.
-\end{abstract}
+    induced hyperelongation of TZs after they anchor at the plasma membrane.
+    Hyperelongated TZs exhibit signs of functional defects, such as the inability
+    to migrate and loss of membrane tethering.
+    We also report that the Exo84 mutant \textit{onion rings} (\textit{onr})
+    decouples TZ hyperelongation from loss of cilium-plasma membrane tethering.
+    Our results reveal a requirement for \PIP{} in supporting ciliogenesis
+    through TZ maintenance.
 
-\section{Introduction}
+    \section{Results and Discussion}
     Cilia are sensory organelles present on almost all cells in the human body
     \citep{satir2010primary}.
-They function primarily by providing sensory inputs to cells, but can
-also function as motile propellers in certain cells
-\citep{bloodgood2010sensory}.
+    They are important for transducing signalling pathways in response to extracellular
+    cues.
     Consistent with their importance in cell signalling,
@@
     \citep{waters2011ciliopathies}.
-
-A large number of ciliopathies are linked to mutations in proteins that
-localize to the cilium transition zone (referred to herein as TZ).
-The TZ is the proximal-most region of the cilium and
-functions as a diffusion barrier that regulates the
+    Many ciliopathies are associated with mutations in proteins that localize
+    to the cilium transition zone (TZ), the proximal-most region of the cilium that
+    functions as a diffusion barrier and regulates the
     bi-directional transport of protein and lipid cargo at the base of the cilium
     \citep{reiter2012base, szymanska2012transition}.
-The TZ is essential for cilium formation (ciliogenesis) and cilium-based
-signalling.
+    The TZ is essential for cilium formation (ciliogenesis) and function.
     The conserved TZ protein CEP290, for example, is mutated in at least
@@
     studies ranging from single gene analysis to proteomics,
-processes underlying TZ maturation are not as well-studied.
+    processes underlying TZ maturation are relatively understudied.
 
@@
 
-\section{Results}
     \subsection{\PIP{} is essential for transition zone maturation}
@@
 
-\section{Discussion}
-Cilia are tiny organelles that are essential for proper human development.
-Many human disorders of cilia are associated with genes that encode
-transition zone (TZ) proteins.
-For example, mutations in the conserved TZ protein CEP290
-are linked to more than 6 different ciliopathies,
-ranging on a spectrum of clinical phenotypes and severities.
-Most of these mutations are likely to be hypomorphic
-and may be affected by genetic modifiers in affected individuals.
-\citep{zaghloul2010functional, khanna2009common, leitch2008hypomorphic}.
-Animal models with partial loss of TZ function may therefore
-provide insight on intermediate phenotypes associated with human disease
-and their cell biological basis.
-In this paper, we described a novel role for the membrane lipid
-phosphatidylinositol 4,5-bisphosphate (\PIP{}) in regulating TZ function.
-
     The initial steps of ciliogenesis involve the assembly of a nascent
@@
     In humans, \textit{PIPKI$\gamma$} is linked to lethal congenital contractural
-syndrome type 3 (LCCS3), which has been suggested to represent a ciliopathy
-\citep{}.
+    syndrome type 3 (LCCS3), which has been suggested to represent a ciliopathy.
     The recent discovery of the role of LCCS1-associated GLE3 protein in cilia
@@
     \textit{Sp}/\textit{CyO}; Unc-GFP was originally provided by M. Kernan \citep{baker2004mechanosensory}.
-Stocks expressing GFP-tagged Chibby, B9d1, B9d2, Cc2d2a and Mks1 were
+    Stocks expressing GFP-tagged Chibby and Mks1 were
     provided by B. Durand \citep{enjolras2012drosophila, vieillard2016transition}.
@@
 
+    \section{Supplemental information}
+    Includes two figures.
+
+    \section{Acknowledgements}
+    We are grateful to Brian Ciruna for insightful comments on the project,
+    and Bénédicte Durand for providing (at the time of experiments)
+    unpublished fly stocks.
+    This work was supported by a grant from the Canadian Institute for
+    Health and Research to J.A.B (Placeholder for Grant number).
+    A.G. was supported by an Open Fellowship and Ontario Graduate Scholarship.
+
     \section{Author contributions}
@@
 
-\section{Acknowledgements}
-We thank Brian Ciruna for insightful comments on the project
-and Bénédicte Durand for providing unpublished fly stocks.
-This work was supported by a grant from the Canadian Institute for Health Research
-(CIHR) to J.A.B.
+    \section{Declaration of interests}
+    The authors declare no competing interests.
 
-\bibliography{bibttc}
-
-\newpage
     \section{Figures}
 
-%%
-%    FIGURE 1
-%
     \textbf{Figure 1. SigD expression induces transition zone hyperelongation.}
-\begin{enumerate}[label={\Alph*.}, nolistsep]
+    \begin{enumerate}[label={(\Alph*)}, nolistsep]
     \item Schematic diagram of the stages of ciliogenesis in the Drosophila male germline.
-  Stages in brackets correspond to those from \citep{cenci1994chromatin}.
+      Stages in brackets correspond to those in \citep{cenci1994chromatin}.
     \item \sigd{} expression induces Cep290 hyperelongation in late G2 cilia.
     \item Paired Ana1-Cep290 lengths in early and late G2 phase in spermatocytes.
-  Numbers in red represent correlation between Cep290 and Ana1 lengths.
-\item \sigd{} expression induces hyperelongation of Chibby and Mks1.
+    \item \sigd{} expression induces hyperelongation of Chibby and Mks1 in late G2 phase.
     \item TZ hyperelongation persists through meiosis but does not affect
@@
 
-\begin{figure}[ht]
-  \includegraphics[scale=0.9]{figure-1/figure1.png}
-\end{figure}
-\newpage
-
-%%
-%%%%
-%%%    FIGURE 2
-%%%
-\textbf{Figure 2. Sktl is important for transition zone maturation and localizes to basal bodies.}
-\begin{enumerate}[label={\Alph*.}, nolistsep]
+    \textbf{Figure 2. Sktl is important for transition zone maturation.}
+    \begin{enumerate}[label={(\Alph*)}, nolistsep]
     \item Expression of full-length Sktl suppresses \sigd{}-induced TZ hyperelongation.
@@
 
-\begin{figure}[ht]
-  \includegraphics[scale=0.9]{figure-2/figure2.png}
-\end{figure}
-\newpage
-
-%%
-%    FIGURE 3
-%
     \textbf{Figure 3. Hyperelongated transition zones display functional defects.}
@@
 
-\begin{figure}[ht]
-  \includegraphics[scale=0.8]{figure-3/figure3.png}
-\end{figure}
-\newpage
-
-%%%
-%%    FIGURE 4
-%%
     \textbf{Figure 4. The \textit{onion rings} (\textit{onr}) allele of \textit{d}Exo84 decouples TZ hyperlongation from loss of plasma membrane contacts.}
     \begin{enumerate}[label={(\Alph*)}, nolistsep]
-\item Cells mutant for \textit{onr} do not display hyperelongated TZs marked with acetylated tubulin.
-\item Quantification from (A).
-\item Cells mutant for \textit{onr} display loss of plasma membrane tethering.
+    \item Cells expressing \sigd{} do not maintain plasma membrane-cilium tethering. The plasma membrane is marked with CellMask.
+    \item \textit{onr} mutants do not maintain plasma membrane-cilium tethering.
+    \item Cells mutant for \textit{onr} do not display hyperelongated acetylated tubulin signal at the cilium.
+    \item GFP-tagged Exo70 localizes to basal bodies.
     \end{enumerate}
 
-\begin{figure}[ht]
-  \includegraphics[scale=0.9]{figure-4/figure4.png}
-\end{figure}
-\newpage
+  \end{linenumbers}
+\end{doublespacing}
+
+\bibliography{bibttc}
+
+%% 
+% FIGURE 1
+% 
+% \textbf{Figure 1. SigD expression induces transition zone hyperelongation.}
+% \begin{enumerate}[label={(\Alph*.)}, nolistsep]
+% \item Schematic diagram of the stages of ciliogenesis in the Drosophila male germline.
+%   Stages in brackets correspond to those from \citep{cenci1994chromatin}.
+% \item \sigd{} expression induces Cep290 hyperelongation in late G2 cilia.
+% \item Paired Ana1-Cep290 lengths in early and late G2 phase in spermatocytes.
+%   Numbers in red represent correlation between Cep290 and Ana1 lengths.
+% \item \sigd{} expression induces hyperelongation of Chibby and Mks1.
+% \item TZ hyperelongation persists through meiosis but does not affect
+%   axoneme outgrowth.
+% \end{enumerate}
+% 
+% \begin{figure}[ht]
+%   \includegraphics[scale=0.9]{figure-1/figure1.png}
+% \end{figure}
+% \newpage
+% 
+% %% 
+% %%%% 
+% %%% FIGURE 2
+% %%% 
+% \textbf{Figure 2. Sktl is important for transition zone maturation and localizes to basal bodies.}
+% \begin{enumerate}[label={(\Alph*.)}, nolistsep]
+% \item Expression of full-length Sktl suppresses \sigd{}-induced TZ hyperelongation.
+% \item Quantification of Cep290 and Ana1 lengths from control, \sigd{} and Sktl; \sigd{} ($n$\textgreater 60) from (A).
+% \item \textit{sktl}$^{2.3}$ clones exhibit TZ hyperelongation. Cilia are marked using
+%   Unc-GFP.
+% \item Phylogenetic tree of PIP5Ks showing conservation of cilium-associated functions.
+%   The scale bar represents expected amino acid substitutions per site and branch support values are shown in red (a value of 1 indicates maximum support).
+%   Abbreviations: Cele (\textit{Caenorhabditis elegans}), Spur (\textit{Strongylocentrotus purpuratus}), Amel (\textit{Apis mellifera}), Aaeg (\textit{Aedes aegypti}), Dana (\textit{Drosophila ananassae}), Dmel (\textit{Drosophila melanogaster}), Hsap (\textit{Homo sapiens}), Mmus (\textit{Mus musculus}), Xtro (\textit{Xenopus tropicalis}), Cint (\textit{Ciona intestinalis}), Scer (\textit{Saccharomyces cerevisiae}).
+% \end{enumerate}
+% 
+% \begin{figure}[ht]
+%   \includegraphics[scale=0.9]{figure-2/figure2.png}
+% \end{figure}
+% \newpage
+% 
+% 
+% %% 
+% % FIGURE 3
+% % 
+% \textbf{Figure 3. Hyperelongated transition zones display functional defects.}
+% \begin{enumerate}[label={(\Alph*)}, nolistsep]
+% \item
+% \item
+% \item
+% \item
+% \end{enumerate}
+% 
+% \begin{figure}[ht]
+%   \includegraphics[scale=0.8]{figure-3/figure3.png}
+% \end{figure}
+% \newpage
+% 
+% 
+% %%% 
+% %% FIGURE 4
+% %% 
+% \textbf{Figure 4. The \textit{onion rings} (\textit{onr}) allele of \textit{d}Exo84 decouples TZ hyperlongation from loss of plasma membrane contacts.}
+% \begin{enumerate}[label={(\Alph*)}, nolistsep]
+% \item Cells mutant for \textit{onr} do not display hyperelongated TZs marked with acetylated tubulin.
+% \item Quantification from (A).
+% \item Cells mutant for \textit{onr} display loss of plasma membrane tethering.
+% \end{enumerate}
+% 
+% \begin{figure}[ht]
+%   \includegraphics[scale=0.9]{figure-4/figure4.png}
+% \end{figure}
+% \newpage
 
@@
 %%% TeX-master: t
-%%% End:
+%%% End

### 2018-03-06 latex/paper.tex
Edits

@@
 \documentclass[12pt, twoside, letterpaper]{article}
-\usepackage[margin=0.8in]{geometry}
+\usepackage[margin=1in]{geometry}
 \usepackage[parfill]{parskip}
+\usepackage{graphicx}
 \usepackage[utf8]{inputenc}
@@
 \usepackage[numbers]{natbib}
-\usepackage{graphicx}
-\graphicspath{{../figures/}}
 \usepackage{enumitem}
@@
 \usepackage{setspace}
-
-% bibliography style
+\graphicspath{{../figures/}}
 \bibliographystyle{unsrtcurrbiol}
@@
 % line spacing
-\renewcommand{\baselinestretch}{1.1}
+% \renewcommand{\baselinestretch}{1.1}
 
@@
 \affil[2]{\small Program in Cell Biology, Hospital for Sick Children, Toronto, ON M5G 1X8, Canada}
-
 \date{\small \today}
@@
     Cilia are sensory organelles that are essential for human development
-    and physiology \citep{satir2010primary}.
-    They function primarily by relaying extracellular stimuli to cells
+    and physiology \citep{satir2010primary, marshall2006cilia}.
+    They function primarily by relaying extracellular cues to cells
     \citep{satir2010primary},
@@
     of the cilium \citep{reiter2012base, szymanska2012transition}.
-    Despite numerous efforts to elucidate TZ proteins and their functions,
+    Although substantial effort has been undertaken
+    to elucidate TZ proteins and their functions in cilium assembly and function,
     processes underlying maturation of TZs are not well understood.
-    We report a role for the membrane lipid phosphatidylinositol 4,5-bisphosphate
+    Here, we report a role for the membrane lipid
+    phosphatidylinositol 4,5-bisphosphate
     (\PIP{}) in TZ maturation and length regulation
     in the \textit{Drosophila melanogaster} male germline.
-    Reduction of cellular \PIP{} levels by expression of the
-    \textit{Salmonella} phosphoinositide phosphatase SigD or mutation of
-    the type I phosphatidylinositol phosphate kinase (PIPKI) Skittles (Sktl)
-    induced hyperelongation of TZs after they anchor at the plasma membrane.
-    Hyperelongated TZs exhibit signs of functional defects, such as the inability
-    to migrate and loss of membrane tethering.
-    We also report that the Exo84 mutant \textit{onion rings} (\textit{onr})
+    We show that reduction of cellular \PIP{} levels
+    by expression of the Salmonella phosphoinositide phosphatase SigD,
+    or mutation of
+    the type I phosphatidylinositol phosphate kinase (PIPKI) Skittles (Sktl),
+    induces the formation of longer than normal TZs.
+    These hyperelongated TZs exhibit signs of functional defects,
+    such as the inability
+    to be migratory \citep{basiri2014migrating} and loss of membrane tethering.
+    We also report that the \textit{onion rings} (\textit{onr}) allele
+    of the Drosophila Exo84
     decouples TZ hyperelongation from loss of cilium-plasma membrane tethering.
     Our results reveal a requirement for \PIP{} in supporting ciliogenesis
-    through TZ maintenance.
+    by promoting proper TZ maturation.
 
-    \section{Results and Discussion}
-    Cilia are sensory organelles present on almost all cells in the human body
-    \citep{satir2010primary}.
-    They are important for transducing signalling pathways in response to extracellular
-    cues.
+    \section{Results}
+    Cilia are sensory organelles that are present on almost all cells in the human body
+    \citep{satir2010primary, marshall2006cilia}.
+    They function in signal reception and transduction in response to extracellular cues,
+    but also have roles in cellular and extracellular fluid motility
+    \citep{brooks2014multiciliated, marshall2006cilia},
+    for example, as the sperm flagellum.
     Consistent with their importance in cell signalling,
-    defects in cilium formation are associated with genetic disorders
+    defects in cilium formation (i.e. ciliogenesis) are associated with genetic disorders
     known collectively as ciliopathies, which can display
@@
     Many ciliopathies are associated with mutations in proteins that localize
-    to the cilium transition zone (TZ), the proximal-most region of the cilium that
+    to the transition zone (TZ), the proximal-most region of the cilium which
     functions as a diffusion barrier and regulates the
-    bi-directional transport of protein and lipid cargo at the base of the cilium
+    bi-directional transport of protein cargo at the base of the cilium
     \citep{reiter2012base, szymanska2012transition}.
-    The TZ is essential for cilium formation (ciliogenesis) and function.
-    The conserved TZ protein CEP290, for example, is mutated in at least
-    six different ciliopathies with a spectrum of clinical features and severities
-    , and is important for cilium formation
+    The TZ is essential for ciliogenesis and function.
+    For example, the conserved TZ protein CEP290 is mutated in at least
+    six different ciliopathies that lie on a spectrum of clinical features and severities,
+    and is important for cilium formation
     and function in both humans \citep{shimada2017vitro, stowe2012centriolar}
@@
     studies ranging from single gene analysis to proteomics,
-    processes underlying TZ maturation are relatively understudied.
+    the process of maturation of the TZ, through which it is converted from a
+    immature form to one competent at supporting
+    cilium assembly, is relatively understudied.
 
-    Ciliogenesis begins with the assembly of TZ proteins at the tips of
-    the basal body.
+    Ciliogenesis begins with the assembly of a nascent TZ at the tips of
+    the basal body \citep{reiter2012base}.
     This nascent TZ undergoes maturation, during which its structure and protein
-    composition changes, allowing for anchoring of the TZ to the membrane and
-    establishment of a compartmentalized space bounded by the ciliary membrane
-    and the TZ.
+    composition changes, allowing for the
+    establishment of a compartmentalized ciliary space bounded by the ciliary membrane
+    and the TZ in which axoneme assembly and signalling can occur.
+    The axoneme is a microtubule-based structure that forms the core of all cilia and flagella.
     In the Drosophila male germline, nascent TZs first assemble on basal bodies
-    during early G2 phase in spermatocytes and anchor to the plasma membrane.
+    during early G2 phase in spermatocytes \citep{riparbelli2012assembly}.
     This is followed by anchoring of cilia to the plasma membrane,
-    rearrangment of microtubules in the axoneme \citep{gottardo2013cilium},
+    rearrangment of microtubules within the TZ \citep{gottardo2013cilium},
     and establishment of a
-    ciliary membrane that persists through meiosis \citep{riparbelli2012assembly}.
+    ciliary membrane that will persist through meiosis
+    \citep{riparbelli2012assembly} (Figure 1A).
     TZ maturation has been described in
@@
     \textit{Caenorrhabditis elegans} \citep{serwas2017centrioles} and
-    \textit{Drosophila melanogaster} \citep{gottardo2013cilium}
+    \textit{Drosophila melanogaster} \citep{gottardo2013cilium},
     and is most readily observed by an increase in TZ length
@@
 
-    Here, we show that the membrane lipid phosphatidylinositol 4,5-bisphosphate (\PIP{})
-    is essential for proper TZ maturation in developing male germ cells
-    in \textit{D. melanogaster}.
-    \PIP{} is relatively enriched within the plasma membrane and the base of cilia
-    in the male germline.
-    We show that expression of the bacterial PIP phosphatase SigD
-    or inactivation of the PIP 5-kinase Skittles (Sktl) that localizes to cilia
-    induces longer than normal TZs without affecting TZ assembly.
-    These hyperelongated TZs show hallmarks of aberrant function similar to those
-    found in previously studied TZ mutants,
-    including loss of cilium-membrane associations.
-    We also find that the \textit{onion rings} allele of the
-    ciliopathy-associated \textit{EXOC8} gene encoding the human Exo84
-    decouples TZ hyperelongation from loss of cilium-membrane contacts.
-    Our results suggest that the plasma membrane lipid \PIP{} regulates TZ length,
-    maturation and function, thereby acting to support ciliogenesis.
+    We previously showed that the membrane lipid phosphatidylinositol 4,5-bisphosphate
+    (\PIP{}) is essential for the formation of the sperm flagellum in the Drosophila
+    male germline \citep{wei2008depletion, fabian2010phosphatidylinositol}.
+    \PIP{} is one of seven different phosphoinositides (PIPs) present in eukaryotes.
+    It localizes primarily to the plasma membrane, where it is essential for
+    modulation of actin cytoskeleton and vesicle trafficking amongst other things
+    \citep{balla2013phosphoinositides}.
+    \PIP{} has been linked to cilium function in many recent studies.
+    The ciliary membrane has been shown to contain very little \PIP{} due to the action
+    of the cilium resident lipid phosphatase INPP5E \citep{nakatsu2015phosphoinositide}.
+    Inactivation of INPP5E leads to a build up of intraciliary \PIP{}
+    which disrupts transport of certain signalling proteins in both vertebrates
+    \citep{chavez2015modulation, garcia2015phosphoinositides, conduit2017compartmentalized}.
+    and Drosophila \citep{park2015ciliary}.
+    We sought to investigate the defects in axoneme assembly in Drosophila male germ cells
+    with reduced \PIP{} 
+    that we reported previously in light of the current understanding of the roles
+    for \PIP{} in cilia as a modulator of cilium function.
 
+    %
+    %   Results - 1
+    %
     \subsection{\PIP{} is essential for transition zone maturation}
-    To investigate whether reduction of cellular \PIP{} affects ciliogenesis in the
+    To investigate how the reduction of cellular \PIP{} affects ciliogenesis in the
     Drosophila male germline,
     we used transgenic flies expressing the Salmonella phosphoinositide phosphatase SigD
-    under the $\beta$2-tubulin promoter (referred to herein as \sigd{}),
-    which is expressed exclusively in spermatocytes
+    under the spermatocyte-specific $\beta$2-tubulin promoter (referred to herein as \sigd{}),
     \citep{wei2008depletion, fabian2010phosphatidylinositol}.
-    We previously showed that \sigd{} induces male sterility
+    SigD dephosphorylates \PIP{} \textit{in vivo},
+    and we previously showed that \sigd{} induces male sterility
     due in part to defects in flagellar biosynthesis \citep{wei2008depletion}.
-    To examine whether this may be caused by aberrant TZ function,
-    we examined the localization of fluorescently-labelled
+    To examine whether these were caused by aberrant TZ function,
+    we examined the localization of fluorescently-tagged
     centriolar/basal body protein
-    Ana1 (CEP295 homolog) \citep{goshima2007genes, blachon2009proximal}
-    and the TZ protein Cep290 \citep{basiri2014migrating}
-    during early steps of cilium assembly in spermatocytes in
+    Ana1 (homolog of CEP295) \citep{goshima2007genes, blachon2009proximal}
+    and the conserved TZ protein Cep290 \citep{basiri2014migrating}
+    during early steps of cilium assembly in spermatocytes in both
     wild-type controls and \sigd{}.
     As shown in Figure 1,
-    while Cep290 on nascent TZs look similar in wild-type and \sigd{}, 
-    it grew to significantly longer lengths in \sigd{}
-    compared to wild-type controls.
-    Ana1 lengths were not affected, and we did not observe an inverse
-    correlation between Cep290 and Ana1 length.
-    This hyperelongation phenotype was not specific to Cep290;
-    all TZ markers examined showed hyperelongation, including
-    acetylated tubulin \citep{gottardo2013cilium},
-    Chibby \citep{enjolras2012drosophila} and
-    MKS \citep{slaats2015mks1, vieillard2016transition} proteins (Figure 1D).
-    TZ hyperelongation was a highly penetrant phenotype (\textgreater 90\%)
+    while Cep290 looks similar in control and \sigd{} in early G2 phase
+    when TZs are still immature, 
+    it grows to significantly longer lengths in \sigd{}
+    compared to wild-type controls by the end of the G2 phase following
+    the period of TZ maturation in spermatocytes.
+    In contrast to the \textit{cep290} mutant, which contains
+    longer than normal basal bodies \citep{basiri2014migrating},
+    Ana1 length was not affected in \sigd{},
+    and we did not observe a strong
+    correlation between Cep290 and Ana1 lengths (Figure 1C).
+    TZ proteins Chibby (Cby) \citep{enjolras2012drosophila} and
+    Mks1 \citep{vieillard2016transition}
+    showed hyperelongation in \sigd{} (Figure 1D),
+    suggesting that this phenotype is not specific to Cep290 but is shared
+    by other members of the Drosophila TZ.
+    TZ hyperelongation was a highly penetrant phenotype (\textgreater 70\%
+    in spermatocytes at late G2 phase)
     and showed high intra-cyst correlation (\textgreater 0.95) suggestive
@@
     presumably SigD.
-    Hyperelongated TZs persisted through meiosis.
-    Despite TZ hyperlongation, however, axonemes were able to
-    elongate post-meiosis (Figure 1E).
-    As we showed previously, the ultrastructure of these axonemes
+    Despite the persistence of hyperelongated TZs through meiosis,
+    axonemes were able to
+    elongate normally in post-meiotic cells (Figure 1E).
+    However, as we showed previously, the ultrastructure of these axonemes
     was frequently aberrant,
     either lacking symmetry completely or containing triplet microtubules
-    instead of doublets \citep{wei2008depletion}.
+    in addition to the usual doublets \citep{wei2008depletion}.
 
-    \subsection{The type I PIP kinase Skittles localizes to centrioles and regulates TZ length}
+    %
+    %   Results - 2
+    %
+    \subsection{The type I PIP kinase (PIPKI) Skittles (Sktl) regulates TZ length}
     While \PIP{} is the major substrate for SigD in eukaryotic cells \textit{in vivo}
@@
     we attempted to rescue it by
-    co-expressing fluorescently-tagged full-length Sktl (Sktl) with SigD
-    under the same promoter.
-    We found that Sktl expression was able to suppress TZ elongation
+    co-expressing fluorescently-tagged full-length Skittles (Sktl) with SigD
+    using the $\beta$2-tubulin promoter.
+    We found that Sktl expression was able to suppress TZ hyperelongation
     in a cilium-autonomous manner (Figure 2A and B).
-    We also found that \textit{sktl} clones using Flp/FRT-based mitotic recombination
-    showed TZ hyperelongation (Figure 2C).
+    We also found that \textit{sktl} clones made
+    using Flp/FRT-based mitotic recombination and co-expressing the
+    basal body and TZ marker Unc
+    \citep{baker2004mechanosensory, wei2008depletion}
+    exhibited TZ hyperelongation (Figure 2C).
 
-    Since Sktl expression suppressed TZ hyperelongation,
-    we investigated whether Sktl could localize to centrioles or cilia
-    in the Drosophila germline.
-    Similar to the human PIPKI$\gamma$ isoform \citep{xu2014pipkigamma},
-    we found that Sktl localizes to basal bodies in the Drosophila male germline.
-    As shown in Figure 2, Drosophila PIPKIs arose from the recent duplication of
+   % Since Sktl expression suppressed TZ hyperelongation,
+   % we investigated whether Sktl could localize to centrioles or cilia
+   % in the Drosophila germline.
+    A study by Xu \textit{et al}. showed the human PIPKI$\gamma$ to be
+    essential for cilium formation
+    \citep{xu2014pipkigamma}.
+    As shown in Figure 2D, Drosophila PIPKIs arose from the recent duplication of
     the ancestral PIPKI gene,
@@
 
+    %
+    %   Results - 3
+    %
     \subsection{Hyperelongated transition zones exhibit signs of functional defects}
-    While shorter spermatocyte TZs have been reported in mutants of TZ proteins in Drosophila
-    \citep{vieillard2016transition, pratt2016drosophila},
-    no genetic manipulation has been shown to induce hyperelongated TZs.
     We sought to examine whether TZ hyperelongation due to SigD expression
@@
     at the distal-most {\raise.17ex\hbox{$\scriptstyle\sim$}}5$\mu$m where tubulin
-    is presumably incorporated into the axoneme.
+    is presumably incorporated into the axoneme
+    \citep{basiri2014migrating, fabian2012drosophila}.
     We found that
     TZs that assembled in \sigd{} cells are non-migratory despite the growth of the
-    axoneme and the cell membrane, as shown by Unc and Cep290 localization.
+    axoneme and the cell membrane, as shown by Unc and Cep290 localization
+    (Figures 3A and 3B).
     We previously described ``comet-shaped'' localization of Unc-GFP in these cells,
     and we find that these hyperelongated Unc signals persist into cellular elongation
-    despite elongation of the axoneme (Figure 3).
+    despite elongation of the axoneme.
 
-    We previously described the presence of occasional triplet microtubules
-    in electron micrographs of axonemes from \sigd{} \citep{wei2008depletion}.
-    While centrioles and basal bodies contain microtubule triplets,
-    restriction of the C-tubule at the TZ causes the axoneme to
-    consist of microtubule doublets rather than triplets throughout its length.
-    Consistent with a defect in TZ barrier formation and presence of
-    microtubule triplets in axonemes,
-    we observed that a subset of cilia in \sigd{}
+    Normally, centrioles and basal bodies consist of microtubule triplets,
+    whereas the axoneme contains microtubule doublets due to the obstruction of
+    the C-tubule at the TZ \citep{gottardo2013cilium}.
+    Consistent with a defect in TZ barrier formation and the presence of
+    microtubule triplets in axonemes in \sigd{} \citep{wei2008depletion},
+    we observed that a small subset of cilia in SigD-expressing cells
     contained puncta of Ana1, a core centriolar protein, at the tips
-    of TZs marked with Cep290.
-    This TZ-distal Ana1 localization is observed at a relatively low penetrance
-    and high intra-cyst correlation.
+    of TZs marked with Cep290 (Figure 3C).
     We found that treatment of germ cells with Taxol as in \citep{riparbelli2013unique}
-    could increase the penetrance of this phenotype.
+    could increase the penetrance of this phenotype (Figure 3D).
     Taxol treatment stabilizes microtubules and is thought to disrupt TZ maturation
-    by interrupting microtubule rearrangements, and similarly induces much longer cilia
-    \citep{riparbelli2012assembly}.
+    by inhibiting microtubule rearrangements \citep{riparbelli2012assembly}.
     Taxol treatment alone did not induce this phenotype in wild-type controls in our hands
-    at varying concentrations ($p$ <0.01 with 5\% penetrance),
-    suggesting that loss of \PIP{} acts upstream of or prior to microtubule rearrangement.
-    Triplet microtubules within the axoneme are also observed in Taxol-treated cells \citep{riparbelli2013unique}.
-    It is possible that the TZ defect allows C-tubules and some centriolar proteins
-    to migrate to the distal end.
-    We did not observe this behaviour with Asterless (CEP152)
-    \citep{dzhindzhev2010asterless, blachon2008drosophila} ($p$ <0.01),
-    another centriolar protein, suggesting that these TZ-distal
+    at varying concentrations ($p$ <0.01 with 5\% penetrance).
+    Triplet microtubules within the axoneme are also observed in Taxol-treated cells
+    \citep{riparbelli2013unique}, further evidencing a relationship between
+    \PIP{} and microtubule reorganization in TZ maturation.
+    Asterless (homolog of CEP152), another centriolar protein,
+    did not localize to TZ-distal puncta in \sigd{}
+    \citep{dzhindzhev2010asterless, blachon2008drosophila} ($p$ <0.01)
+    suggesting that these TZ-distal
     sites are not fully centriolar in protein composition.
 
+    %
+    %   Results - 4
+    %
     \subsection{The \textit{onion rings} mutant decouples defects found in cells with reduced levels of \PIP{}}
@@
     defective Exo84 function, we examined TZs in \textit{onr} mutants.
-    We found that the \textit{onr} mutant did not display hyperelongated TZs (Figure 5),
+    We found that the \textit{onr} mutant did not display hyperelongated TZs (Figure 5C),
     suggesting that Exo84 is dispensable for TZ maturation.
@@
     to the plasma membrane, they were unable to either establish or maintain
-    membrane connections, and were rendered cytoplasmic (Figure 5) similar to
+    membrane connections, and were rendered cytoplasmic (Figure 5A and B) similar to
     \textit{dila; cby} mutants.
@@
     lack of available reagents,
-    we found that Exo70 localized to centrioles (Figure 4D),
-    but not Sec6 (Supplementary figure 2).
-    Exo70 can directly bind to \PIP{} \citep{he2007exo70}.
+    we found that Exo70 localized to centrioles (Figure 4D).
+    Exo70 can directly bind to \PIP{} and mediates the recruitment of
+    the exocyst complex to the plasma membrane \citep{he2007exo70}.
     Our results suggest that the exocyst may act downstream of \PIP{} to
@@
 
-    The initial steps of ciliogenesis involve the assembly of a nascent
-    TZ on the basal body.
-    This nascent TZ ``matures'' through sequential assembly of additional
-    TZ proteins into a functional TZ capable of acting as a diffusion barrier
-    and supporting axoneme elongation and ciliary signalling.
+    \section{Discussion}
+    The process of maturation of a TZ from a nascent form to a fully functional one,
+    leading ultimately to axoneme assembly and ciliary signalling,
+    requires orchestration of various proteins and cellular pathways
+    \citep{reiter2012base}.
     In the Drosophila male germline, TZ maturation occurs during the
-    extended G2 phase in spermatocytes prior to meiosis,
-    and is readily observed by an increase in TZ length
-    and various microtubule rearrangements.
-    Axoneme elongation occurs in telophase II following meiosis in
-    spermatids, where a functional TZ detaches from the basal body
-    and migrates along the growing axoneme to compartmentalize the distal tip
-    in Cep290-dependant manner \citep{basiri2014migrating}.
+    extended G2 phase in spermatocytes prior to meiosis, and can be readily
+    observed by an increase in TZ length using fluorescence microscopy.
+    Our results suggest that normal execution of this process
+    requires \PIP{}, and that depletion of \PIP{} induces TZs to
+    grow longer than normal.
+    Regulation of TZ length in the Drosophila male germline has been reported
+    previously.
+    For example, \textit{mks1} mutants have shorter TZs \citep{pratt2016drosophila},
+    while
+    \textit{cby; dila} and \textit{cby} mutants display hyperelongated ones
+    \citep{enjolras2012drosophila,vieillard2016transition}.
+    Since both Cby and Mks1 are hyperelongated in \sigd{} cells,
+    \PIP{} seems to be intimately involved in this process as well but it does
+    so independantly of Cby and Mks1.
 
-    We found that reduction of \PIP{} levels in the male germline by expression
-    of the lipid phosphatase SigD or mutation in the type I PIP kinase
-    Skittles (Sktl) lead to much longer TZs by the end of spermatocyte G2 phase.
-    Presumably, loss of \PIP{} abolishes a signal to stop TZ lengthening during
-    a particular step in maturation.
+    The majority of \PIP{} at the plasma membrane is produced by PIPKIs
+    \citep{balla2013phosphoinositides}
+    and these seem to have a conserved role at cilia.
+    In this study, we showed that mutation of the PIPKI Skittles (Sktl)
+    induced hyperelongated TZs, similar to SigD expression.
     We were able rescue TZ hyperelongation by expression of full-length Sktl to
@@
     Interestingly, some cells showed cilium-autonomous suppression of lengths.
-    Development of the Drosophila male germline occurs in syncytial ``cysts''
-    of cells which share the same cytoplasm.
-    Therefore, our results suggest that Skittles might function \textit{in situ}
+    The development of the Drosophila male germline occurs in syncytial ``cysts''
+    of cells which share the same cytoplasm, and
+    our results suggest that Skittles might function \textit{in situ}
     to regulate TZ maturation in these cells.
-
     In humans, \textit{PIPKI$\gamma$} is linked to lethal congenital contractural
     syndrome type 3 (LCCS3), which has been suggested to represent a ciliopathy.
-    The recent discovery of the role of LCCS1-associated GLE3 protein in cilia
-    further shows this.
+    The recent discovery of the role of LCCS1-associated GLE1 protein in cilium
+    function \citep{jao2017role} further supports this hypothesis.
+    Thus, PIPKIs might represent novel ciliopathy-associated genes
+    or genetic modifiers of disease.
 
@@
     The exocyst is known to bind to \PIP{}
-    \citep{he2007exo70, zhang2008membrane}, and we previously described that
+    \citep{he2007exo70, zhang2008membrane}, and we previously showed that
     the \textit{onr} allele of Drosophila \textit{Exo84} phenocopied
@@
     but not TZ hyperelongation.
-    Proper TZ function is required for membrane tethering, as \textit{dila; cby}
-    mutants, which contain abnormal TZs also show cytoplasmic cilia similar to
-    \sigd{} \citep{vieillard2016transition}.
-    Our results suggest that the exocyst is required after the initial stages
-    of TZ assembly and maturation for TZ function.
+    Proper TZ function is required for membrane tethering, as evidenced by
+    \textit{dila; cby} mutants, which contain abnormal TZs
+    and show similar cytoplasmic cilia similar as \sigd{} \citep{vieillard2016transition}.
+    Our results suggest that the exocyst is required for this process,
+    possibly downstream of \PIP{}.
 
@@
     and 50\% humidity.
-    Stocks expressing $\beta$\textit{2t}::\textit{Styp}\textbackslash{SigD} (chromosome \textit{3})
-    and $\beta$\textit{2t}::YFP-Sktl (chromosome \textit{2})
+    Stocks expressing $\beta$\textit{2t}::\textit{Styp}\textbackslash{SigD} (chromosome \textit{3}),
+    $\beta$\textit{2t}::YFP-Sktl (chromosome \textit{2}) and
+    Exo70-GFP
     were described previously \citep{wei2008depletion, fabian2010phosphatidylinositol}.
@@
     at the indicated concentrations -
-    rabbit anti-Tulp (gift from W. McGinnis \citep{ronshaugen2002structure}), 1:500;
     chicken anti-GFP IgY (abcam) 1:1000;
     rat anti-RFP IgG (5F8, ChromoTek), 1:1000;
-    rabbit anti-Sktl (courtesy of P. Raghu), 1:500;
-    rabbit anti-\textit{d}Sec6 (courtesy of U. Tepass), 1:500;
+    rabbit anti-Cp110 (courtesy of J. Raff), 1:500;
     mouse anti-acetylated $\alpha$-tubulin 6-11-B (Sigma-Aldrich), 1:1000.
@@
     We are grateful to Brian Ciruna for insightful comments on the project,
-    and Bénédicte Durand for providing (at the time of experiments)
+    and B{\'e}n{\'e}dicte Durand for providing (at the time of experiments)
     unpublished fly stocks.
@@
 
-    \section{Figures}
+    \section{Figure legends}
 
@@
     \item Expression of full-length Sktl suppresses \sigd{}-induced TZ hyperelongation.
-    \item Quantification of Cep290 and Ana1 lengths from control, \sigd{} and Sktl; \sigd{} ($n$\textgreater 60) from (A).
+    \item Quantification of Cep290 and Ana1 lengths from control, \sigd{} and Sktl; \sigd{} from (A).
     \item \textit{sktl}$^{2.3}$ clones exhibit TZ hyperelongation. Cilia are marked using
@@
     \begin{enumerate}[label={(\Alph*)}, nolistsep]
-    \item 
-    \item
-    \item
-    \item
+    \item GFP-tagged Unc is unable to detach from the basal body and migrate in spermatids expressing \sigd{}.
+    \item Cep290 is unable to detach and migrate from the basal body at the onset of axoneme assembly in \sigd{} spermatids.
+    \item Structured illumination micrographs of \sigd{} cells show TZ-distal puncta of the centriolar protein Ana1.
+    \item Treatment of \sigd{} cells with the microtubule stabilizing drug Taxol increases the penetrance of TZ-distal Ana1.
+    \item Quantification of Cep290 lengths in Taxol-treated control and \sigd{} cells.
+      Inset shows distribution of regression coefficients (i.e. effects of Taxol and SigD on Cep290 length) from a fully Bayesian analysis.
     \end{enumerate}
@@
 
-%% 
-% FIGURE 1
-% 
-% \textbf{Figure 1. SigD expression induces transition zone hyperelongation.}
-% \begin{enumerate}[label={(\Alph*.)}, nolistsep]
-% \item Schematic diagram of the stages of ciliogenesis in the Drosophila male germline.
-%   Stages in brackets correspond to those from \citep{cenci1994chromatin}.
-% \item \sigd{} expression induces Cep290 hyperelongation in late G2 cilia.
-% \item Paired Ana1-Cep290 lengths in early and late G2 phase in spermatocytes.
-%   Numbers in red represent correlation between Cep290 and Ana1 lengths.
-% \item \sigd{} expression induces hyperelongation of Chibby and Mks1.
-% \item TZ hyperelongation persists through meiosis but does not affect
-%   axoneme outgrowth.
-% \end{enumerate}
-% 
-% \begin{figure}[ht]
-%   \includegraphics[scale=0.9]{figure-1/figure1.png}
-% \end{figure}
-% \newpage
-% 
-% %% 
-% %%%% 
-% %%% FIGURE 2
-% %%% 
-% \textbf{Figure 2. Sktl is important for transition zone maturation and localizes to basal bodies.}
-% \begin{enumerate}[label={(\Alph*.)}, nolistsep]
-% \item Expression of full-length Sktl suppresses \sigd{}-induced TZ hyperelongation.
-% \item Quantification of Cep290 and Ana1 lengths from control, \sigd{} and Sktl; \sigd{} ($n$\textgreater 60) from (A).
-% \item \textit{sktl}$^{2.3}$ clones exhibit TZ hyperelongation. Cilia are marked using
-%   Unc-GFP.
-% \item Phylogenetic tree of PIP5Ks showing conservation of cilium-associated functions.
-%   The scale bar represents expected amino acid substitutions per site and branch support values are shown in red (a value of 1 indicates maximum support).
-%   Abbreviations: Cele (\textit{Caenorhabditis elegans}), Spur (\textit{Strongylocentrotus purpuratus}), Amel (\textit{Apis mellifera}), Aaeg (\textit{Aedes aegypti}), Dana (\textit{Drosophila ananassae}), Dmel (\textit{Drosophila melanogaster}), Hsap (\textit{Homo sapiens}), Mmus (\textit{Mus musculus}), Xtro (\textit{Xenopus tropicalis}), Cint (\textit{Ciona intestinalis}), Scer (\textit{Saccharomyces cerevisiae}).
-% \end{enumerate}
-% 
-% \begin{figure}[ht]
-%   \includegraphics[scale=0.9]{figure-2/figure2.png}
-% \end{figure}
-% \newpage
-% 
-% 
-% %% 
-% % FIGURE 3
-% % 
-% \textbf{Figure 3. Hyperelongated transition zones display functional defects.}
-% \begin{enumerate}[label={(\Alph*)}, nolistsep]
-% \item
-% \item
-% \item
-% \item
-% \end{enumerate}
-% 
-% \begin{figure}[ht]
-%   \includegraphics[scale=0.8]{figure-3/figure3.png}
-% \end{figure}
-% \newpage
-% 
-% 
-% %%% 
-% %% FIGURE 4
-% %% 
-% \textbf{Figure 4. The \textit{onion rings} (\textit{onr}) allele of \textit{d}Exo84 decouples TZ hyperlongation from loss of plasma membrane contacts.}
-% \begin{enumerate}[label={(\Alph*)}, nolistsep]
-% \item Cells mutant for \textit{onr} do not display hyperelongated TZs marked with acetylated tubulin.
-% \item Quantification from (A).
-% \item Cells mutant for \textit{onr} display loss of plasma membrane tethering.
-% \end{enumerate}
-% 
-% \begin{figure}[ht]
-%   \includegraphics[scale=0.9]{figure-4/figure4.png}
-% \end{figure}
-% \newpage
+\newpage
+
+\section{Figures}
+
+\textbf{Figure 1}
+\begin{figure}[ht]
+  \includegraphics[scale=0.9]{figure-1/figure1.png}
+\end{figure}
+\newpage
+
+\textbf{Figure 2}
+\begin{figure}[ht]
+  \includegraphics[scale=0.9]{figure-2/figure2.png}
+\end{figure}
+\newpage
+
+\textbf{Figure 3}
+\begin{figure}[ht]
+  \includegraphics[scale=0.8]{figure-3/figure3.png}
+\end{figure}
+\newpage
+
+\textbf{Figure 4}
+\begin{figure}[ht]
+  \includegraphics[scale=0.9]{figure-4/figure4.png}
+\end{figure}
+\newpage
 

### 2018-03-06 latex/paper.tex
Edits

@@
 \usepackage{charter}
+\usepackage[charter]{mathdesign}
 \usepackage[numbers]{natbib}
@@
     we attempted to rescue it by
-    co-expressing fluorescently-tagged full-length Skittles (Sktl) with SigD
-    using the $\beta$2-tubulin promoter.
+    co-expressing SigD with
+    fluorescently-tagged full-length Skittles (Sktl)
+    using the same $\beta$2-tubulin promoter.
     We found that Sktl expression was able to suppress TZ hyperelongation
@@
     We also found that \textit{sktl} clones made
-    using Flp/FRT-based mitotic recombination and co-expressing the
+    using Flp/FRT-based mitotic recombination and expressing the
     basal body and TZ marker Unc
     \citep{baker2004mechanosensory, wei2008depletion}
-    exhibited TZ hyperelongation (Figure 2C).
+    exhibited TZ hyperelongation (Figure 2C),
+    suggesting that Sktl is important for TZ maturation.
 
@@
    % in the Drosophila germline.
-    A study by Xu \textit{et al}. showed the human PIPKI$\gamma$ to be
-    essential for cilium formation
+    Xu \textit{et al}. showed the vertebrate PIPKI$\gamma$ to be
+    important for cilium formation in cultured cell lines
     \citep{xu2014pipkigamma}.
@@
     to be functionally related to PIPKI$\gamma$ in its roles at cilia,
-    as well as the \textit{C. elegans} PPK-1 \citep{xu2014pipkigamma}.
+    as well as the \textit{C. elegans} PPK-1 (See supplementary data in \citep{xu2014pipkigamma}).
     However, unlike the human PIPKI$\gamma$, which functions to license TZ assembly
@@
     regulating TZ length in the Drosophila male germline
-    but not its assembly.
+    but not TZ assembly.
     Cp110 is dispensable for cilium formation in Drosophila \citep{franz2013cp110}
@@
     affected TZ function.
-    During germ cell elongation following meiosis, the TZ detaches from
+    During cell elongation following meiosis, the TZ detaches from
     the basal body and migrates along the growing axoneme, maintaining a ciliary compartment
@@
     and we find that these hyperelongated Unc signals persist into cellular elongation
-    despite elongation of the axoneme.
+    despite elongation of the axoneme (Figure 3A, bottommost panel).
 
-    Normally, centrioles and basal bodies consist of microtubule triplets,
-    whereas the axoneme contains microtubule doublets due to the obstruction of
+    In Drosophila and humans, basal bodies consist of microtubule triplets
+    \citep{jana2016drosophila, lattao2017centrioles}
+    while the axoneme contains microtubule doublets due to the obstruction of
     the C-tubule at the TZ \citep{gottardo2013cilium}.
-    Consistent with a defect in TZ barrier formation and the presence of
+    Consistent with a defect in the TZ barrier and the presence of
     microtubule triplets in axonemes in \sigd{} \citep{wei2008depletion},
-    we observed that a small subset of cilia in SigD-expressing cells
+    we observed that a subset of cilia (<5\%) in SigD-expressing cells
     contained puncta of Ana1, a core centriolar protein, at the tips
@@
     Taxol treatment alone did not induce this phenotype in wild-type controls in our hands
-    at varying concentrations ($p$ <0.01 with 5\% penetrance).
+    at varying concentrations ($p$ <0.01 at 5\% penetrance).
     Triplet microtubules within the axoneme are also observed in Taxol-treated cells
-    \citep{riparbelli2013unique}, further evidencing a relationship between
+    \citep{riparbelli2013unique}, further supporting a relationship between
     \PIP{} and microtubule reorganization in TZ maturation.
@@
     We previously showed that male flies homozygous for the \textit{onion rings}
-    (\textit{onr}) mutant of Drosophila Exo84 were sterile, with phenotypes
-    similar to \sigd{} \citep{wei2008depletion}.
+    (\textit{onr}) mutant of Drosophila Exo84 were sterile, and had phenotypes
+    similar to \sigd{} such as defects in cell polarity \citep{wei2008depletion}.
     Exo84 is a component of the octameric exocyst complex, which binds
@@
     lack of available reagents,
-    we found that Exo70 localized to centrioles (Figure 4D).
+    we found that GFP-tagged Exo70 localized to centrioles (Figure 4D).
     Exo70 can directly bind to \PIP{} and mediates the recruitment of
@@
 
+    The gene \textit{EXOC8}, encoding the human Exo84, has also
+    been linked to Joubert syndrome, a ciliopathy
+    \citep{dixon2012exome}.
     Members of the exocyst complex, such as Sec10 and Sec6, have been shown
@@
     rabbit anti-Cp110 (courtesy of J. Raff), 1:500;
+    rabbit anti-Centrin {Placeholder for origin}, 1:500;
     mouse anti-acetylated $\alpha$-tubulin 6-11-B (Sigma-Aldrich), 1:1000.
@@
     \section{Supplemental information}
-    Includes two figures.
+    Includes two figures. (Pending attachment)
 
@@
       The scale bar represents expected amino acid substitutions per site and branch support values are shown in red (a value of 1 indicates maximum support).
+      Black arrows represent involvement in cilium-associated functions.
       Abbreviations: Cele (\textit{Caenorhabditis elegans}), Spur (\textit{Strongylocentrotus purpuratus}), Amel (\textit{Apis mellifera}), Aaeg (\textit{Aedes aegypti}), Dana (\textit{Drosophila ananassae}), Dmel (\textit{Drosophila melanogaster}), Hsap (\textit{Homo sapiens}), Mmus (\textit{Mus musculus}), Xtro (\textit{Xenopus tropicalis}), Cint (\textit{Ciona intestinalis}), Scer (\textit{Saccharomyces cerevisiae}).
@@
     \item Quantification of Cep290 lengths in Taxol-treated control and \sigd{} cells.
-      Inset shows distribution of regression coefficients (i.e. effects of Taxol and SigD on Cep290 length) from a fully Bayesian analysis.
+      % Inset shows distribution of regression coefficients (i.e. effects of Taxol and SigD on Cep290 length) from a fully Bayesian analysis.
     \end{enumerate}
@@
 
+\textbf{Supplemental figures}
+Cp110 localization (pending attachment).
+
 \end{document}

### 2018-03-07 coverletter/main.tex
Initial commit

\documentclass[12pt, twoside, letterpaper]{letter}
\usepackage[margin=1in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage{charter}
\usepackage{microtype}

\newcommand{\PIP}{PIP\textsubscript{2}}

\signature{Alind Gupta}
\date{\small \today}
\begin{document}

\begin{letter}{Editors \\
    \textit{Current Biology}}

\opening{Dear Editors,}

We are submitting our manuscript titled
``Phosphatidylinositol 4,5-bisphosphate is essential for
cilium transition zone maturation in \textit{Drosophila melanogaster}''
to be considered for publication in \textit{Current Biology}.
In this paper, we demonstrate a novel role for the membrane lipid
phosphatidylinositol 4,5-bisphosphate, or \PIP{},
in the development of the cilium transition zone using
\textit{Drosophila melanogaster} as a model.

The cilium transition zone forms a diffusion barrier that controls
the transport of cargo entering and exiting the cilium.
As a result, it is essential to the assembly of the cilium
and its function as a sensory organelle.

In this paper, we present the following key findings:
\begin{enumerate}
\item We demonstrate that reducing \PIP{} in the Drosophila male germline
  induces the formation of longer than normal transition zones.
\item We show that the type I phosphatidylinositol phosphate kinase
  Skittles regulates transition zone length.
\item We provide evidence that hyperelongated transition zones are
  functionally defective in their ability to form a competent diffusion barrier
  and represent the outcome of an aberrant maturation process.
\item We show that the \textit{onion rings} allele of the Drosophila Exo84,
  a component of the exocyst complex, can decouple transition zone length
  with the loss of plasma membrane-cilium tethering observed in cells
  with reduced \PIP{}.
\end{enumerate}

This article is of broad interest for several reasons.
This is, to our knowledge, the first example of a positive role for the lipid
\PIP{} in cilium assembly through transition zone maturation,
particularly in an animal model.
This is in contrast to the current model
of the PIP code of cilia where \PIP{} is a disruptor of ciliary signalling.
Second, we describe an extrinsic signal for transition zone
development, which is going to be missed by proteomic approaches.
Third, we add to the current understanding of the poorly understood
process by which the transition zone matures into a functional form.
This may be important for our understanding of intermediate phenotypes
and novel modifiers of disease.

Here are the names of six possible reviewers:
\begin{enumerate}
  \item Tomer Avidor-Reiss, University of Toledo (\url{tomer.avidorreiss@utoledo.edu})
  \item
  \item
  \item
  \item
\end{enumerate}

We look forward to you favourable consideration of our manuscript.

\closing{Sincerely,}

\end{letter}
\end{document}

### 2018-03-08 latex/paper.tex
Add package for better word spacing
Edits from B. Durand's review

@@
 \usepackage{setspace}
+\usepackage{microtype}
 \graphicspath{{../figures/}}
@@
     during early G2 phase in spermatocytes \citep{riparbelli2012assembly}.
-    This is followed by anchoring of cilia to the plasma membrane,
+    This occurs concomitantly with the anchoring of cilia to the plasma membrane,
     rearrangment of microtubules within the TZ \citep{gottardo2013cilium},
@@
     under the spermatocyte-specific $\beta$2-tubulin promoter (referred to herein as \sigd{}),
-    \citep{wei2008depletion, fabian2010phosphatidylinositol}.
+    \citep{wei2008depletion}.
+    Note that \sigd{} corresponds to ``SigD-high'' in \citep{fabian2010phosphatidylinositol}.
     SigD dephosphorylates \PIP{} \textit{in vivo},
@@
     correlation between Cep290 and Ana1 lengths (Figure 1C).
+    We previously showed that the structure of basal bodies
+    from electron microscopy was normal, and that the centriolar
+    markers GFP-PACT and Sas-4 \citep{basto2006flies}
+    were normal when immunostained for
+    in controls and \sigd{}.
+    \citep{wei2008depletion}
     TZ proteins Chibby (Cby) \citep{enjolras2012drosophila} and
@@
     but not TZ assembly.
-    Cp110 is dispensable for cilium formation in Drosophila \citep{franz2013cp110}
-    and we found its localization to be unaffected in \sigd{} (Supplementary figure 1).
+    Neither inactivation nor overexpression of \textit{cp110} affects
+    cilium formation in Drosophila, and Cp110
+    and is removed from basal bodies in the earliest stages of G2 phase in the male germline
+    \citep{franz2013cp110}.
 
@@
     defective Exo84 function, we examined TZs in \textit{onr} mutants.
-    We found that the \textit{onr} mutant did not display hyperelongated TZs (Figure 5C),
+    We found that the \textit{onr} mutant did not display hyperelongated TZs (Figure 4C),
     suggesting that Exo84 is dispensable for TZ maturation.
@@
     to the plasma membrane, they were unable to either establish or maintain
-    membrane connections, and were rendered cytoplasmic (Figure 5A and B) similar to
+    membrane connections, and were rendered cytoplasmic (Figure 4A and B) similar to
     \textit{dila; cby} mutants.
@@
     The majority of \PIP{} at the plasma membrane is produced by PIPKIs
-    \citep{balla2013phosphoinositides}
+    \citep{balla2013phosphoinositides, hammond2012pi4p}
     and these seem to have a conserved role at cilia.
@@
     $\beta$\textit{2t}::YFP-Sktl (chromosome \textit{2}) and
-    Exo70-GFP
-    were described previously \citep{wei2008depletion, fabian2010phosphatidylinositol}.
+    % placeholder - Exo70 is from where?
     $\beta$\textit{2t}::mCherry-Sktl was made as in \citep{wei2008depletion},
@@
     with a predefined
-    concentration of Taxol and incubated overnight in a humidified sterile
+    concentration of Taxol (Sigma-Aldrich)
+    and incubated overnight in a humidified sterile
     chamber in the dark at room temperature. They were then squashed
@@
     and colours were added for the purpose of illustration.
-
-    \section{Supplemental information}
-    Includes two figures. (Pending attachment)
 
@@
 
-\textbf{Supplemental figures}
-Cp110 localization (pending attachment).
-
 \end{document}

### 2018-03-13 latex/paper.tex
Edit to address critique from B. Trimble

@@
     TZs that assembled in \sigd{} cells are non-migratory despite the growth of the
-    axoneme and the cell membrane, as shown by Unc and Cep290 localization
+    axoneme (see Figure 1E) and the cell membrane, as shown by Unc and Cep290 localization
     (Figures 3A and 3B).
@@
     We found that treatment of germ cells with Taxol as in \citep{riparbelli2013unique}
-    could increase the penetrance of this phenotype (Figure 3D).
+    could increase the penetrance of this phenotype from <5\% in untreated cells
+    to \textgreater25\% in cells treated with 4 $\mu$M Taxol (Figure 3D)
+    without affecting Cep290 length significantly (Figure 3E).
     Taxol treatment stabilizes microtubules and is thought to disrupt TZ maturation
@@
     the exocyst complex to the plasma membrane \citep{he2007exo70}.
-    Our results suggest that the exocyst may act downstream of \PIP{} to
-    enhance cilium-membrane associations, and that TZ hyperelongation and loss of
+    Our results suggest that exocyst regulates
+    cilium-membrane associations similar to \PIP{}, and that TZ hyperelongation and loss of
     membrane-cilium association are genetically separable phenotypes.
@@
     Interestingly, some cells showed cilium-autonomous suppression of lengths.
-    The development of the Drosophila male germline occurs in syncytial ``cysts''
-    of cells which share the same cytoplasm, and
-    our results suggest that Skittles might function \textit{in situ}
+    Since the development of the Drosophila male germline occurs in syncytial ``cysts''
+    of cells which share the same cytoplasm,
+    cilium-autonomous rescue suggests that Skittles might function \textit{in situ}
     to regulate TZ maturation in these cells.
@@
     function \citep{jao2017role} further supports this hypothesis.
-    Thus, PIPKIs might represent novel ciliopathy-associated genes
-    or genetic modifiers of disease.
+    This is further evidence that PIPKIs might represent ciliopathy-associated genes
+    or genetic modifiers of disease, as previously hypothesized
+    \citep{xu2016phosphatidylinositol}.
 
-    The gene \textit{EXOC8}, encoding the human Exo84, has also
-    been linked to Joubert syndrome, a ciliopathy
-    \citep{dixon2012exome}.
+    In this study, we report two phenotypes associated with
+    hyperelongated TZs which we postulate to be indicators of
+    TZ dysfunction.
+    Firstly, we show that hyperelongated TZs are unable to
+    detach from the basal bodies at the onset of axoneme elongation
+    in spermatids, unlike normal cells \citep{basiri2014migrating, fabian2012drosophila}.
+    However, axonemes can assemble despite the lack of a functional
+    TZ or membrane association in \sigd{} cells.
+    As we previously reported, these axonemes have frequently aberrant
+    ultrastructure \citep{wei2008depletion}.
+    This is similar to \textit{cep290} \citep{basiri2014migrating}
+    and \textit{dila}; \textit{cby} \citep{vieillard2016transition}
+    mutants,
+    both of which can assemble spermatid axonemes despite lacking
+    functional TZs.
+    We also report a novel phenotype of TZ-distal Ana1 localization
+    in \sigd{} cells.
+    In flies, Ana1 is important for centriole elongation
+    \citep{saurya2016drosophila}.
+    The human ortholog of Ana1 called CEP295 regulates
+    centriole elongation by building the distal centriole and
+    enhancing post-translational modification of the centriolar
+    microtubules \citep{chang2016cep295}.
+    The observation that Drosophila \textit{cep290} mutants,
+    which lack a functional TZ diffusion barrier
+    \citep{basiri2014migrating},
+    contain hyperelongated centrioles suggests that the
+    TZ normally suppresses centriole length.
+    Our results of Ana1 being present at the tips of hyperelongated TZs
+    without an increase in centriole length suggest that \sigd{} expression
+    does not entirely disrupt the TZ diffusion barrier, but certain aspects of it,
+    such as the inability to restrict C-tubules and Ana1.
+    We found that
+    Asterless (Asl), a peri-centriolar protein
+    \citep{blachon2008drosophila}
+    important for centrosome formation and centriole duplication, did not
+    exhibit this TZ-distal localization.
+    This may be due to many reasons, such as the different dynamics of Ana1 and Asl
+    loading onto centrioles \citep{fu2016conserved, saurya2016drosophila} and the
+    more peripheral nature of Asl within the centriole \citep{blachon2008drosophila}
+
     Members of the exocyst complex, such as Sec10 and Sec6, have been shown
     to be important for cilium formation in cultured cell lines and zebrafish
-    \citep{zuo2009exocyst, lobo2017exocyst, seixas2016arl13b}.
-    The exocyst is known to bind to \PIP{}
-    \citep{he2007exo70, zhang2008membrane}, and we previously showed that
+    \citep{zuo2009exocyst, lobo2017exocyst, seixas2016arl13b},
+    but their precise roles in ciliogenesis are not well-understood.
+    The subunits Sec3 and Exo70 regulate exocyst targeting to the plasma
+    membrane through a direct interaction with \PIP{}
+    \citep{he2007exo70, zhang2008membrane}.
+    We previously showed that
     the \textit{onr} allele of Drosophila \textit{Exo84} phenocopied
-    male germline defects observed in \sigd{} \citep{fabian2010phosphatidylinositol}.
+    defects in cell polarity and elongation observed in \sigd{}
+    \citep{fabian2010phosphatidylinositol}.
     In this paper, we show that the \textit{onr} allele of the Drosophila Exo84
-    phenocopies the loss of cilium-membrane contacts in \sigd{},
+    phenocopies the loss of cilium-membrane contacts in \sigd{} similar to
+    \textit{dila; cby} mutants \citep{vieillard2016transition},
     but not TZ hyperelongation.
-    Proper TZ function is required for membrane tethering, as evidenced by
-    \textit{dila; cby} mutants, which contain abnormal TZs
-    and show similar cytoplasmic cilia similar as \sigd{} \citep{vieillard2016transition}.
-    Our results suggest that the exocyst is required for this process,
-    possibly downstream of \PIP{}.
+    Thus, TZ dysfunction is not a prerequisite for lack of
+    cilium-plasma membrane association in male germ cells,
+    and Exo84 uniquely regulates the latter process.
+    This result is supported by the Drosophila \textit{cep290} mutant,
+    which lacks a functional TZ but retains cilium-plasma membrane
+    association \cite{basiri2014migrating}.
+    Notably, \textit{EXOC8}, which encodes the human Exo84, has
+    been linked to the ciliopathy Joubert syndrome
+    \citep{dixon2012exome},
+    and a similar process might underlie defects in humans with
+    mutations in \textit{EXOC8}.
 
@@
     \item GFP-tagged Unc is unable to detach from the basal body and migrate in spermatids expressing \sigd{}.
+      Cell elongation in spermatids is concomitant with elongation of the mitochondrial derivative (dark organelles in the phase contrast images).
     \item Cep290 is unable to detach and migrate from the basal body at the onset of axoneme assembly in \sigd{} spermatids.

### 2018-03-13 figures/figure-1/runStan.R
Initial commit; run model.stan

@@ -1,0 +1,18 @@
+library("rstan")
+rstan_options(auto_write = TRUE)
+options(mc.cores = parallel::detectCores())
+
+df <- read.csv('x.csv')
+y <- df$cep290
+
+out <- stan('model.stan',
+            data=list(y = y,
+                      N = length(y),
+                      K = 3,
+                      J = 2,
+                      d_hyp = c(1, 1, 1),
+                      var_hyp= 0.1),
+            chains = 4,
+            iter = 1000)
+
+rstan::extract(out, 'y_pred')[[1]][1:length(y)] %>% hist

### 2018-03-14 latex/paper.tex
Edits from J. Brill

@@
 \newcommand{\sktl}{\textit{sktl}}
+\makeatletter
+\renewcommand\@biblabel[1]{#1.}
+\makeatother
 
@@
     \textit{Paramecium} \citep{aubusson2015transition}
-    \textit{Caenorrhabditis elegans} \citep{serwas2017centrioles} and
+    \textit{Caenorhabditis elegans} \citep{serwas2017centrioles} and
     \textit{Drosophila melanogaster} \citep{gottardo2013cilium},
@@
     All $t$-tests were unpaired and two-sided.
+    $n$ represents the pooled number of samples from multiple biological replicates.
     A significance level of 0.01 was fixed \textit{a priori} for all classical analysis.
@@
     \item Schematic diagram of the stages of ciliogenesis in the Drosophila male germline.
-      Stages in brackets correspond to those in \citep{cenci1994chromatin}.
-    \item \sigd{} expression induces Cep290 hyperelongation in late G2 cilia.
-    \item Paired Ana1-Cep290 lengths in early and late G2 phase in spermatocytes.
+      Stages in brackets correspond to those from \citep{cenci1994chromatin}.
+    \item \sigd{} expression induces Cep290 hyperelongation in cilia at late G2 phase (white arrowheads).
+    \item Paired Ana1-Cep290 lengths in early and late G2 phase in spermatocytes ($n$ >30 and >65 respectively).
     \item \sigd{} expression induces hyperelongation of Chibby and Mks1 in late G2 phase.
@@
     \item \textit{sktl}$^{2.3}$ clones exhibit TZ hyperelongation. Cilia are marked using
-      Unc-GFP.
+      Unc-GFP. The plot on the right shows quantification of Unc-GFP lengths in control and \sigd{}
+      spermatocytes at late G2 phase ($n$ >30).
     \item Phylogenetic tree of PIP5Ks showing conservation of cilium-associated functions.
@@
       Cell elongation in spermatids is concomitant with elongation of the mitochondrial derivative (dark organelles in the phase contrast images).
+      Insets show phase contrast images corresponding to the region shown in the fluorescence images.
     \item Cep290 is unable to detach and migrate from the basal body at the onset of axoneme assembly in \sigd{} spermatids.
-    \item Structured illumination micrographs of \sigd{} cells show TZ-distal puncta of the centriolar protein Ana1.
-    \item Treatment of \sigd{} cells with the microtubule stabilizing drug Taxol increases the penetrance of TZ-distal Ana1.
-    \item Quantification of Cep290 lengths in Taxol-treated control and \sigd{} cells.
+      Insets show phase contrast images corresponding to the region shown in the fluorescence images with the
+      elongating mitochondria delineated by a yellow dashed line.
+    \item Structured illumination micrographs of \sigd{} cells show TZ-distal puncta of the centriolar protein Ana1 (yellow arrowheads).
+    \item Treatment of \sigd{} cells with the microtubule stabilizing drug Taxol increases the penetrance of TZ-distal Ana1 (white arrowheads)
+      but does not affect length.
+    \item Quantification of Cep290 lengths in Taxol-treated control and \sigd{} cells from (D).
       % Inset shows distribution of regression coefficients (i.e. effects of Taxol and SigD on Cep290 length) from a fully Bayesian analysis.
@@
     \begin{enumerate}[label={(\Alph*)}, nolistsep]
-    \item Cells expressing \sigd{} do not maintain plasma membrane-cilium tethering. The plasma membrane is marked with CellMask.
+    \item Cells expressing \sigd{} do not maintain plasma membrane-cilium tethering despite initially anchoring to the plasma membrane.
+      The plasma membrane is marked with CellMask, a cell impermeable dye.
     \item \textit{onr} mutants do not maintain plasma membrane-cilium tethering.
-    \item Cells mutant for \textit{onr} do not display hyperelongated acetylated tubulin signal at the cilium.
-    \item GFP-tagged Exo70 localizes to basal bodies.
+    \item Cells mutant for \textit{onr} do not display hyperelongated acetylated tubulin signal (white arrowheads) at the cilium.
+      Acetylated tubulin marks the axoneme, which fully overlaps with the TZ in spermatocytes \citep{pratt2016drosophila}.
+    \item GFP-tagged Exo70 localizes to basal bodies in late G2 spermatocytes.
     \end{enumerate}

### 2018-03-14 coverletter/main.tex
Edits to address J. Brill's critique

@@
 
-\signature{Alind Gupta}
+\signature{Julie Brill}
 \date{\small \today}
@@
 We are submitting our manuscript titled
-``Phosphatidylinositol 4,5-bisphosphate is essential for
+``Phosphatidylinositol 4,5-bisphosphate regulates
 cilium transition zone maturation in \textit{Drosophila melanogaster}''
@@
 in the development of the cilium transition zone using
-\textit{Drosophila melanogaster} as a model.
+the male germline of \textit{Drosophila melanogaster} as a model.
 
-The cilium transition zone forms a diffusion barrier that controls
-the transport of cargo entering and exiting the cilium.
-As a result, it is essential to the assembly of the cilium
+The transition zone forms a diffusion barrier
+at the base of the cilium, thereby controlling
+the transport of cargo entering and exiting this organelle.
+As a result, the proper formation and maturation of the transition zone
+is essential for the assembly of the cilium
 and its function as a sensory organelle.
@@
 \item We provide evidence that hyperelongated transition zones are
-  functionally defective in their ability to form a competent diffusion barrier
-  and represent the outcome of an aberrant maturation process.
-\item We show that the \textit{onion rings} allele of the Drosophila Exo84,
+  functionally defective.
+\item We show that the \textit{onion rings} allele of Drosophila Exo84,
   a component of the exocyst complex, can decouple transition zone length
-  with the loss of plasma membrane-cilium tethering observed in cells
-  with reduced \PIP{}.
+  from the loss of plasma membrane-cilium tethering observed in cells
+  with reduced levels of \PIP{}.
 \end{enumerate}
@@
 This article is of broad interest for several reasons.
-This is, to our knowledge, the first example of a positive role for the lipid
-\PIP{} in cilium assembly through transition zone maturation,
-particularly in an animal model.
-This is in contrast to the current model
-of the PIP code of cilia where \PIP{} is a disruptor of ciliary signalling.
-Second, we describe an extrinsic signal for transition zone
-development, which is going to be missed by proteomic approaches.
-Third, we add to the current understanding of the poorly understood
-process by which the transition zone matures into a functional form.
-This may be important for our understanding of intermediate phenotypes
-and novel modifiers of disease.
+First, we show that the poorly understood process of
+transition zone maturation, by which a nascent transition zone
+matures into a fully functional one,
+is regulated by the lipid \PIP{}, which is known to be enriched
+at the base of cilia from multiple studies.
+Second, we show that the Drosophila type I phosphatidylinositol
+phosphate kinase Skittles regulates transition zone
+maturation, and that it does so \textit{in situ},
+providing further evidence that these enzymes may be genetic
+modifiers of diseases of cilia.
+Third, we show that the exocyst, which has been shown to be important for
+cilium formation in multiple studies, regulates cilium maintenance
+by enabling plasma membrane-cilium attachment but not transition zone maturation.
 
@@
 \begin{enumerate}
+  \item B{\'e}n{\'e}dicte Durand, Université Claude Bernard Lyon-1 (\url{benedicte.durand@univ-lyon1.fr})
+  \item Daniel Eberl, University of Iowa (\url{daniel-eberl@uiowa.edu})
+  \item Yukiko Yamashita, University of Michigan (\url{yukikomy@umich.edu})
+  \item Timothy Megraw, Florida State University (\url{timothy.megraw@med.fsu.edu})
   \item Tomer Avidor-Reiss, University of Toledo (\url{tomer.avidorreiss@utoledo.edu})
-  \item
-  \item
-  \item
-  \item
+    \item Andrew Jarman, University of Edinburgh (\url{andrew.jarman@ed.ac.uk})
 \end{enumerate}
 
-We look forward to you favourable consideration of our manuscript.
+We look forward to your favourable consideration of our manuscript.
 

### 2018-03-15 latex/paper.tex
Edits from Brill's thorough critique

@@
 \documentclass[12pt, twoside, letterpaper]{article}
-\usepackage[margin=1in]{geometry}
+\usepackage[margin=0.9in]{geometry}
 \usepackage[parfill]{parskip}
@@
 \usepackage{charter}
-\usepackage[charter]{mathdesign}
+%\usepackage[charter]{mathdesign} % I hate how charter greeks look
 \usepackage[numbers]{natbib}
 \usepackage{enumitem}
-\usepackage{hyperref}
+\usepackage[hidelinks]{hyperref}
 \usepackage{titlesec}
@@
 \newcommand{\PIP}{PIP\textsubscript{2}}
-\newcommand{\sigd}{$\beta$\textit{2t}-SigD}
+\newcommand{\sigd}{$\beta$\textsubscript{2}t-SigD}
 \newcommand{\sktl}{\textit{sktl}}
@@
 \author[1,2]{Alind Gupta \thanks{\url{alind.gupta@mail.utoronto.ca}}}
+\author[2]{Lacramioara Fabian \thanks{\url{lacramioara.fabian@sickkids.ca}}}
 \author[1,2]{Julie A. Brill \thanks{\url{julie.brill@sickkids.ca} (Corresponding author)}}
@@
 \affil[2]{\small Program in Cell Biology, Hospital for Sick Children, Toronto, ON M5G 1X8, Canada}
-\date{\small \today}
+\date{}
 
@@
 \maketitle
+\raggedbottom
 
@@
     skeletal abnormalities \citep{hammarsjo2017novel},
-    and infertility \citep{inaba2016sperm} in addition to other phenotypes
+    and infertility \citep{inaba2016sperm}, in addition to other phenotypes
     \citep{waters2011ciliopathies}.
     Many ciliopathies are associated with mutations in proteins that localize
-    to the transition zone (TZ), the proximal-most region of the cilium which
+    to the transition zone (TZ), the proximal-most region of the cilium that
     functions as a diffusion barrier and regulates the
-    bi-directional transport of protein cargo at the base of the cilium
+    bidirectional transport of protein cargo at the base of the cilium
     \citep{reiter2012base, szymanska2012transition}.
@@
     For example, the conserved TZ protein CEP290 is mutated in at least
-    six different ciliopathies that lie on a spectrum of clinical features and severities,
+    six different ciliopathies that lie on a spectrum of clinical features and severities
     and is important for cilium formation
@@
     studies ranging from single gene analysis to proteomics,
-    the process of maturation of the TZ, through which it is converted from a
+    the process of maturation of the TZ, through which it is converted from an
     immature form to one competent at supporting
@@
 
-    Ciliogenesis begins with the assembly of a nascent TZ at the tips of
+    Ciliogenesis begins with assembly of a nascent TZ at the tip of
     the basal body \citep{reiter2012base}.
@@
     composition changes, allowing for the
-    establishment of a compartmentalized ciliary space bounded by the ciliary membrane
-    and the TZ in which axoneme assembly and signalling can occur.
+    establishment of a compartmentalized ciliary space, bounded by the ciliary membrane
+    and the TZ, in which axoneme assembly and signalling can occur.
     The axoneme is a microtubule-based structure that forms the core of all cilia and flagella.
@@
     during early G2 phase in spermatocytes \citep{riparbelli2012assembly}.
-    This occurs concomitantly with the anchoring of cilia to the plasma membrane,
+    This occurs concomitantly with anchoring of cilia to the plasma membrane,
     rearrangment of microtubules within the TZ \citep{gottardo2013cilium},
@@
     TZ maturation has been described in
-    \textit{Paramecium} \citep{aubusson2015transition}
+    \textit{Paramecium} \citep{aubusson2015transition},
     \textit{Caenorhabditis elegans} \citep{serwas2017centrioles} and
@@
     We previously showed that the membrane lipid phosphatidylinositol 4,5-bisphosphate
-    (\PIP{}) is essential for the formation of the sperm flagellum in the Drosophila
+    (\PIP{}) is essential for formation of the sperm flagellum in the Drosophila
     male germline \citep{wei2008depletion, fabian2010phosphatidylinositol}.
@@
     It localizes primarily to the plasma membrane, where it is essential for
-    modulation of actin cytoskeleton and vesicle trafficking amongst other things
-    \citep{balla2013phosphoinositides}.
-    \PIP{} has been linked to cilium function in many recent studies.
-    The ciliary membrane has been shown to contain very little \PIP{} due to the action
-    of the cilium resident lipid phosphatase INPP5E \citep{nakatsu2015phosphoinositide}.
-    Inactivation of INPP5E leads to a build up of intraciliary \PIP{}
-    which disrupts transport of certain signalling proteins in both vertebrates
-    \citep{chavez2015modulation, garcia2015phosphoinositides, conduit2017compartmentalized}.
-    and Drosophila \citep{park2015ciliary}.
-    We sought to investigate the defects in axoneme assembly in Drosophila male germ cells
-    with reduced \PIP{} 
-    that we reported previously in light of the current understanding of the roles
-    for \PIP{} in cilia as a modulator of cilium function.
+    modulation of the actin cytoskeleton and vesicle trafficking, as well as numerous
+    other processes \citep{balla2013phosphoinositides}.
+    \PIP{} has been linked to cilium function in recent studies.
+    While the ciliary membrane has been found to contain very little \PIP{} due to the action
+    of the cilium resident PIP phosphatase INPP5E,
+    the base of the cilium is enriched in \PIP{}
+    \citep{nakatsu2015phosphoinositide}.
+    Inactivation of INPP5E leads to a build up of intraciliary \PIP{},
+    which disrupts transport of components of the Hedgehog signalling pathway in vertebrates
+    \citep{chavez2015modulation, garcia2015phosphoinositides, conduit2017compartmentalized}
+    and ion channels involved in mechanotransduction in Drosophila \citep{park2015ciliary}.
+    In light of this current understanding of the role
+    for \PIP{} as a modulator of cilium function,
+    we sought to investigate the cause of defects in axoneme assembly in Drosophila male germ cells
+    with reduced levels of \PIP{} from \citep{wei2008depletion}.
 
@@
     \subsection{\PIP{} is essential for transition zone maturation}
-    To investigate how the reduction of cellular \PIP{} affects ciliogenesis in the
+    To investigate how reduction of cellular \PIP{} affects ciliogenesis in the
     Drosophila male germline,
     we used transgenic flies expressing the Salmonella phosphoinositide phosphatase SigD
-    under the spermatocyte-specific $\beta$2-tubulin promoter (referred to herein as \sigd{}),
+    under the control of spermatocyte-specific $\beta$\textsubscript{2}-tubulin promoter (referred to herein as \sigd{}),
     \citep{wei2008depletion}.
@@
     due in part to defects in flagellar biosynthesis \citep{wei2008depletion}.
-    To examine whether these were caused by aberrant TZ function,
-    we examined the localization of fluorescently-tagged
+    To examine whether these defects were caused by aberrant TZ function,
+    we examined the localization of fluorescently-tagged versions of the
     centriolar/basal body protein
@@
     and the conserved TZ protein Cep290 \citep{basiri2014migrating}
-    during early steps of cilium assembly in spermatocytes in both
-    wild-type controls and \sigd{}.
-    As shown in Figure 1,
-    while Cep290 looks similar in control and \sigd{} in early G2 phase
-    when TZs are still immature, 
-    it grows to significantly longer lengths in \sigd{}
+    during early steps of cilium assembly in spermatocytes.
+    Cep290 distribution appeared similar in control and \sigd{} in early G2 phase
+    when TZs are still immature.
+    In contrast, Cep290-labelled TZs were significantly longer in \sigd{}
     compared to wild-type controls by the end of the G2 phase following
-    the period of TZ maturation in spermatocytes.
-    In contrast to the \textit{cep290} mutant, which contains
+    the period of TZ maturation in spermatocytes (Figure 1B and 1C).
+    Unlike Drosophila \textit{cep290} mutants, which contain
     longer than normal basal bodies \citep{basiri2014migrating},
@@
     We previously showed that the structure of basal bodies
-    from electron microscopy was normal, and that the centriolar
-    markers GFP-PACT and Sas-4 \citep{basto2006flies}
-    were normal when immunostained for
-    in controls and \sigd{}.
-    \citep{wei2008depletion}
-    TZ proteins Chibby (Cby) \citep{enjolras2012drosophila} and
+    from electron microscopy is normal, and that the localization of the centriolar
+    marker GFP-PACT \citep{basto2006flies}
+    is similar in controls and \sigd{} \citep{wei2008depletion}.
+    In contrast, TZ proteins Chibby (Cby) \citep{enjolras2012drosophila} and
     Mks1 \citep{vieillard2016transition}
-    showed hyperelongation in \sigd{} (Figure 1D),
+    exhibited hyperelongation in \sigd{} (Figure 1D),
     suggesting that this phenotype is not specific to Cep290 but is shared
@@
     Despite the persistence of hyperelongated TZs through meiosis,
-    axonemes were able to
+    axonemes, visualized by staining for acetylated tubulin, were able to
     elongate normally in post-meiotic cells (Figure 1E).
     However, as we showed previously, the ultrastructure of these axonemes
-    was frequently aberrant,
+    is frequently aberrant,
     either lacking symmetry completely or containing triplet microtubules
@@
     \subsection{The type I PIP kinase (PIPKI) Skittles (Sktl) regulates TZ length}
-    While \PIP{} is the major substrate for SigD in eukaryotic cells \textit{in vivo}
+    Whereas \PIP{} is the major substrate for SigD in eukaryotic cells \textit{in vivo}
     \citep{terebiznik2002elimination, zhou2001salmonella, sengupta2013depletion},
@@
     physiologically relevant phenotype in response to decreased \PIP{},
-    we attempted to rescue it by
-    co-expressing SigD with
-    fluorescently-tagged full-length Skittles (Sktl)
-    using the same $\beta$2-tubulin promoter.
+    we attempted to rescue the TZ phenotype by
+    co-expressing \sigd{} with
+    fluorescently-tagged Skittles (Sktl)
+    using the same $\beta$\textsubscript{2}-tubulin promoter.
     We found that Sktl expression was able to suppress TZ hyperelongation
@@
 
-   % Since Sktl expression suppressed TZ hyperelongation,
-   % we investigated whether Sktl could localize to centrioles or cilia
-   % in the Drosophila germline.
-    Xu \textit{et al}. showed the vertebrate PIPKI$\gamma$ to be
+    A previous report showed the vertebrate PIPKI$\gamma$ to be
     important for cilium formation in cultured cell lines
     \citep{xu2014pipkigamma}.
-    As shown in Figure 2D, Drosophila PIPKIs arose from the recent duplication of
+    Drosophila PIPKIs arose from the recent duplication of
     the ancestral PIPKI gene,
-    and are not orthologous to specific vertebrate PIPKI isoforms.
+    and are not orthologous to specific vertebrate PIPKI isoforms (Figure 2D).
     Sktl has diverged more than its paralog PIP5K59B, and seems
-    to be functionally related to PIPKI$\gamma$ in its roles at cilia,
-    as well as the \textit{C. elegans} PPK-1 (See supplementary data in \citep{xu2014pipkigamma}).
-    However, unlike the human PIPKI$\gamma$, which functions to license TZ assembly
+    to be functionally related to PIPKI$\gamma$
+    and the \textit{C. elegans} PPK-1 in having roles at cilia \citep{xu2014pipkigamma}.
+    However, unlike the human PIPKI$\gamma$, which licenses TZ assembly
     by promoting CP110 removal from basal bodies \citep{xu2016phosphatidylinositol},
     our results suggest that Sktl functions in
-    regulating TZ length in the Drosophila male germline
+    regulating TZ length in the Drosophila male germline,
     but not TZ assembly. 
-    Neither inactivation nor overexpression of \textit{cp110} affects
+    Notably, neither inactivation nor overexpression of \textit{cp110} affects
     cilium formation in Drosophila, and Cp110
-    and is removed from basal bodies in the earliest stages of G2 phase in the male germline
+    and is removed from basal bodies in the earliest stages of G2 phase in the Drosophila male germline
     \citep{franz2013cp110}.
@@
     \citep{basiri2014migrating, fabian2012drosophila}.
-    We found that
-    TZs that assembled in \sigd{} cells are non-migratory despite the growth of the
-    axoneme (see Figure 1E) and the cell membrane, as shown by Unc and Cep290 localization
+    As shown by Unc and Cep290 localization,
+    TZs that assembled in \sigd{} cells were frequently incapable of detaching from
+    the basal body and migrating along the axoneme despite
+    axoneme elongation (Figure 1E) and cellular elongation
     (Figures 3A and 3B).
     We previously described ``comet-shaped'' localization of Unc-GFP in these cells,
-    and we find that these hyperelongated Unc signals persist into cellular elongation
-    despite elongation of the axoneme (Figure 3A, bottommost panel).
+    and we find that these hyperelongated Unc signals persist during cellular elongation
+    despite elongation of the axoneme (Figure 3A bottommost panel and Figure 1E).
 
     In Drosophila and humans, basal bodies consist of microtubule triplets
-    \citep{jana2016drosophila, lattao2017centrioles}
-    while the axoneme contains microtubule doublets due to the obstruction of
+    \citep{jana2016drosophila, lattao2017centrioles},
+    whereas the axoneme contains microtubule doublets due to obstruction of
     the C-tubule at the TZ \citep{gottardo2013cilium}.
@@
     of TZs marked with Cep290 (Figure 3C).
-    We found that treatment of germ cells with Taxol as in \citep{riparbelli2013unique}
+    We found that treatment of germ cells with Taxol, as in \citep{riparbelli2013unique},
     could increase the penetrance of this phenotype from <5\% in untreated cells
@@
     \PIP{} and microtubule reorganization in TZ maturation.
-    Asterless (homolog of CEP152), another centriolar protein,
-    did not localize to TZ-distal puncta in \sigd{}
-    \citep{dzhindzhev2010asterless, blachon2008drosophila} ($p$ <0.01)
+    Fluorescently-tagged Asterless (homolog of CEP152), a pericentriolar protein
+    \citep{blachon2008drosophila, dzhindzhev2010asterless},
+    did not localize to TZ-distal puncta in \sigd{} ($p$ <0.01)
     suggesting that these TZ-distal
@@
     defective Exo84 function, we examined TZs in \textit{onr} mutants.
-    We found that the \textit{onr} mutant did not display hyperelongated TZs (Figure 4C),
+    Unlike \sigd{}, the \textit{onr} mutant did not display hyperelongated TZs (Figure 4C),
     suggesting that Exo84 is dispensable for TZ maturation.
 
-    Due to the involvement of exocyst in membrane trafficking at the plasma membrane,
-    we examined whether cilium-associated membrane dynamics were affected in \sigd{}
-    or \textit{onr} mutants similar to \textit{dila; cby} mutants
+    Due to involvement of exocyst in membrane trafficking at the plasma membrane,
+    we examined whether cilium-associated membranes were affected in \sigd{}
+    or \textit{onr} mutants in a manner similar to \textit{dila; cby} mutants
     \citep{vieillard2016transition}.
-    We found that while TZs in \sigd{} and \textit{onr} cells anchored properly
+    Whereas TZs in \sigd{} and \textit{onr} cells anchored properly
     to the plasma membrane, they were unable to either establish or maintain
@@
     the exocyst complex to the plasma membrane \citep{he2007exo70}.
-    Our results suggest that exocyst regulates
-    cilium-membrane associations similar to \PIP{}, and that TZ hyperelongation and loss of
+    Our results suggest that the exocyst, and Exo84 in particular, regulates
+    cilium-membrane associations, similar to \PIP{}, and that TZ hyperelongation and loss of
     membrane-cilium association are genetically separable phenotypes.
@@
     For example, \textit{mks1} mutants have shorter TZs \citep{pratt2016drosophila},
-    while
-    \textit{cby; dila} and \textit{cby} mutants display hyperelongated ones
+    whereas
+    \textit{cby; dila} and \textit{cby} mutants display hyperelongated TZs
     \citep{enjolras2012drosophila,vieillard2016transition}.
     Since both Cby and Mks1 are hyperelongated in \sigd{} cells,
-    \PIP{} seems to be intimately involved in this process as well but it does
+    \PIP{} seems to be intimately involved in this process as well, but it does
     so independantly of Cby and Mks1.
@@
     induced hyperelongated TZs, similar to SigD expression.
-    We were able rescue TZ hyperelongation by expression of full-length Sktl to
-    a large degree.
-    Interestingly, some cells showed cilium-autonomous suppression of lengths.
-    Since the development of the Drosophila male germline occurs in syncytial ``cysts''
-    of cells which share the same cytoplasm,
-    cilium-autonomous rescue suggests that Skittles might function \textit{in situ}
+    We were able rescue TZ hyperelongation in \sigd{} by expression of full-length Sktl.
+    Interestingly, some cells showed cilium-autonomous suppression of TZ length.
+    Because the development of the Drosophila male germline occurs in syncytial cysts
+    of cells that share the same cytoplasm,
+    cilium-autonomous rescue suggests Skittles might function \textit{in situ}
     to regulate TZ maturation in these cells.
@@
     function \citep{jao2017role} further supports this hypothesis.
-    This is further evidence that PIPKIs might represent ciliopathy-associated genes
-    or genetic modifiers of disease, as previously hypothesized
+    Our data support the idea that PIPKIs might represent ciliopathy-associated genes
+    or genetic modifiers of disease, as previously postulated
     \citep{xu2016phosphatidylinositol}.
@@
     In this study, we report two phenotypes associated with
-    hyperelongated TZs which we postulate to be indicators of
+    hyperelongated TZs that we postulate to be indicators of
     TZ dysfunction.
     Firstly, we show that hyperelongated TZs are unable to
-    detach from the basal bodies at the onset of axoneme elongation
-    in spermatids, unlike normal cells \citep{basiri2014migrating, fabian2012drosophila}.
-    However, axonemes can assemble despite the lack of a functional
+    detach from basal bodies at the onset of axoneme elongation
+    in spermatids, unlike TZs in normal cells \citep{basiri2014migrating, fabian2012drosophila}.
+    Nonetheless, axonemes can assemble despite the lack of a functional
     TZ or membrane association in \sigd{} cells.
-    As we previously reported, these axonemes have frequently aberrant
+    As we previously reported, these axonemes frequently exhibit aberrant
     ultrastructure \citep{wei2008depletion}.
@@
     mutants,
-    both of which can assemble spermatid axonemes despite lacking
+    which can assemble spermatid axonemes despite lacking
     functional TZs.
+
     We also report a novel phenotype of TZ-distal Ana1 localization
@@
     \citep{saurya2016drosophila}.
-    The human ortholog of Ana1 called CEP295 regulates
+    The human ortholog of Ana1, called CEP295, regulates
     centriole elongation by building the distal centriole and
-    enhancing post-translational modification of the centriolar
+    enhancing post-translational modification of centriolar
     microtubules \citep{chang2016cep295}.
@@
     TZ normally suppresses centriole length.
-    Our results of Ana1 being present at the tips of hyperelongated TZs
+    Our observations of Ana1 at the tips of hyperelongated TZs
     without an increase in centriole length suggest that \sigd{} expression
-    does not entirely disrupt the TZ diffusion barrier, but certain aspects of it,
+    does not entirely disrupt the TZ diffusion barrier, but only certain aspects,
     such as the inability to restrict C-tubules and Ana1.
     We found that
-    Asterless (Asl), a peri-centriolar protein
+    Asterless (Asl), a pericentriolar protein
     \citep{blachon2008drosophila}
@@
     exhibit this TZ-distal localization.
-    This may be due to many reasons, such as the different dynamics of Ana1 and Asl
+    This may be due to several reasons, such as different dynamics of Ana1 and Asl
     loading onto centrioles \citep{fu2016conserved, saurya2016drosophila} and the
-    more peripheral nature of Asl within the centriole \citep{blachon2008drosophila}
+    more peripheral nature of Asl within the centriole \citep{blachon2008drosophila}.
 
-    Members of the exocyst complex, such as Sec10 and Sec6, have been shown
-    to be important for cilium formation in cultured cell lines and zebrafish
+    Members of the exocyst complex, such as Sec10 and Sec6, are
+    important for cilium formation in cultured cell lines and zebrafish
     \citep{zuo2009exocyst, lobo2017exocyst, seixas2016arl13b},
@@
     \citep{fabian2010phosphatidylinositol}.
-    In this paper, we show that the \textit{onr} allele of the Drosophila Exo84
-    phenocopies the loss of cilium-membrane contacts in \sigd{} similar to
+    Here, we show that the \textit{onr} allele of the Drosophila Exo84
+    phenocopies the loss of cilium-membrane contacts in \sigd{}, similar to
     \textit{dila; cby} mutants \citep{vieillard2016transition},
     but not TZ hyperelongation.
-    Thus, TZ dysfunction is not a prerequisite for lack of
+    Thus, TZ hyperelongation is not a prerequisite for the failure of
     cilium-plasma membrane association in male germ cells,
-    and Exo84 uniquely regulates the latter process.
+    and Exo84 uniquely regulates the latter process,
+    potentially by supplying membrane required to maintain cilium-plasma membrane
+    association.
     This result is supported by the Drosophila \textit{cep290} mutant,
@@
     and 50\% humidity.
-    Stocks expressing $\beta$\textit{2t}::\textit{Styp}\textbackslash{SigD} (chromosome \textit{3}),
-    $\beta$\textit{2t}::YFP-Sktl (chromosome \textit{2}) and
-    % placeholder - Exo70 is from where?
-    $\beta$\textit{2t}::mCherry-Sktl was made as in \citep{wei2008depletion},
-    and a \textit{P}-element insertion on chromosome \textit{2} was used for rescue using the low-level
-    expression vector \textit{tv3} \citep{wong2005pip2}.
+    Stocks expressing $\beta$\textsubscript{2}t::\textit{Styp}\textbackslash{SigD} (chromosome \textit{3}) and
+    $\beta$\textsubscript{2}t::YFP-Sktl (chromosome \textit{2}) were described previously \citep{wei2008depletion}.
+    GFP-Exo70 was cloned into the low-level expression vector \textit{tv3} \citep{wong2005pip2}
+    and transgenic flies were generated using standard \textit{P} element-mediated transformation.
     Ana1-tdTomato (chromosome \textit{2}) and Cep290-GFP (chromosome \textit{3}) were provided
@@
     The following primary antibodies were used for immunofluorescence
-    at the indicated concentrations -
+    at the indicated concentrations ---
     chicken anti-GFP IgY (abcam) 1:1000;
     rat anti-RFP IgG (5F8, ChromoTek), 1:1000;
-    rabbit anti-Cp110 (courtesy of J. Raff), 1:500;
-    rabbit anti-Centrin {Placeholder for origin}, 1:500;
+    rabbit anti-Centrin (C7736, Sigma-Aldrich), 1:500;
     mouse anti-acetylated $\alpha$-tubulin 6-11-B (Sigma-Aldrich), 1:1000.
@@
     IgG (Molecular Probes) at 1:1000.
-    DAPI at 1:1000 was used to label chromatin.
+    DAPI at 1:1000 was used to stain for DNA.
 
     \subsection{Fluorescence microscopy}
-    For live imaging, testes were dissected in phosphate bufferd saline (PBS).
-    If staining for chromatin, intact testes were incubated in PBS with
-    Hoechst (1:5000) for 5 minutes at this point.
+    For live imaging, testes were dissected in phosphate buffered saline (PBS).
+    To stain for DNA, intact testes were incubated in PBS with
+    Hoechst (1:5000) for 5 minutes.
     Testes were transferred to a polylysine-coated glass slide in a drop of PBS,
@@
     The edges of the coverslip were sealed with nail polish
-    and the specimen was visualized immediately using an epifluorescence microscope.
+    and the specimen was visualized using an epifluorescence microscope.
 
@@
     and incubated overnight in a humidified sterile
-    chamber in the dark at room temperature. They were then squashed
-    in PBS and imaged live.
+    chamber in the dark at room temperature.
+    These were then squashed in PBS and imaged live.
 
     For CellMask staining, cells were spilled from testes in M3 medium onto
-    a sterilized glass-bottom dish that was pre-treated with sterile polylysine solution
+    a sterilized glass-bottom dish pre-treated with sterile polylysine solution
     to enable cells to adhere.
@@
     ruptured with a needle, squashed and frozen in liquid nitrogen for 5 minutes.
-    The slides were transferred to ice-cold methanol for 5-10 minutes for pre-fixation.
-    For staining with the anti-Sktl antibody, this pre-fixation step
-    was omitted to preserve cellular membranes.
-    Samples were fixed in 4\% paraformaldehyde in PBS,
-    permeabilized and blocked in PBS with 0.1\% Triton-X and 0.3\% bovine
-    serum albumin and incubated with primary antibodies overnight at 4$^{\circ}$C.
-    followed by three 5-minute washes with PBS and 1 hour incubation
-    with secondary antibodies and three 5-minute washes with PBS.
+    These slides were transferred to ice-cold methanol for 5-10 minutes for fixation.
+    Samples were then permeabilized and blocked in PBS with 0.1\% Triton-X and 0.3\% bovine
+    serum albumin, and incubated with primary antibodies overnight at 4$^{\circ}$C,
+    followed by three 5-minute washes with PBS, 1 hour incubation
+    with secondary antibodies, and three 5-minute washes with PBS.
     Samples were mounted in Dako (Agilent) and imaged with
@@
     results in Figures 1 and 2 for clearer visualization of trends,
-    but raw data was used for all analysis.
-    Statistical tests for ``absence of phenotype'' were computed under a
-    hypothesis assuming binomial likelihood (i.e. assuming a fixed probability of the
-    phenotype occurring).
-    All $t$-tests were unpaired and two-sided.
+    but raw data was used for all analyses.
+    Statistical tests for ``absence of phenotype'' were computed using a binomial test
+    under the assumption that the probability of the phenotype occuring was fixed.
+    All $t$-tests were unpaired and two-sided with Welch's correction for unequal variances.
     $n$ represents the pooled number of samples from multiple biological replicates.
-    A significance level of 0.01 was fixed \textit{a priori} for all classical analysis.
+    A significance level of 0.01 was fixed \textit{a priori} for all classical analyses.
     All raw data and code for analysis and plotting can be found online
@@
     \subsection{Phylogenetic analysis}
-    Candidate orthologs of Skittles or PIP5K9B were queried
-    from Inparanoid and FlyBase (version 8.0).
+    Candidate orthologs of Skittles and PIP5K9B were queried
+    from Inparanoid (version 8.0) and FlyBase (version 2.0).
     Poorly annotated protein sequences were confirmed
@@
     kinases using reciprocal BLAST search.
-    Phylogeny.fr (\url{http://www.phylogeny.fr}) was used for
+    Phylogeny.fr (\url{http://www.phylogeny.fr}) \citep{dereeper2008phylogeny} was used for
     phylogenetic reconstruction with T-Coffee for multiple alignment
@@
     \section{Acknowledgements}
-    We are grateful to Brian Ciruna for insightful comments on the project,
-    and B{\'e}n{\'e}dicte Durand for providing (at the time of experiments)
-    unpublished fly stocks.
-    This work was supported by a grant from the Canadian Institute for
-    Health and Research to J.A.B (Placeholder for Grant number).
-    A.G. was supported by an Open Fellowship and Ontario Graduate Scholarship.
+    We are grateful to Brian Ciruna for insightful discussions,
+    B{\'e}n{\'e}dicte Durand for providing (at the time of experiments)
+    unpublished fly stocks, and to
+    B{\'e}n{\'e}dicte Durand and Bill Trimble
+    for comments on the manuscript.
+    This research was supported by a grant from the Canadian Institutes for
+    Health and Research to J.A.B (MOP ???).
+    A.G. was supported by a
+    University of Toronto Open Fellowship and
+    an Ontario Graduate Scholarship.
 
@@
     A.G. performed all the experiments and analysis, and wrote the manuscript.
-    J.A.B. supervised the project.
+    L.F. generated GFP-Exo70 flies.
+    J.A.B. edited the manuscript and supervised the project.
 
@@
     \end{enumerate}
-
+    \bigskip
     \textbf{Figure 2. Sktl is important for transition zone maturation.}
@@
     \end{enumerate}
-
+    \bigskip
     \textbf{Figure 3. Hyperelongated transition zones display functional defects.}
@@
     \end{enumerate}
-
+    \bigskip
     \textbf{Figure 4. The \textit{onion rings} (\textit{onr}) allele of \textit{d}Exo84 decouples TZ hyperlongation from loss of plasma membrane contacts.}

### 2018-03-15 figures/figure-2/plot2.R
Add missing significance bar

@@ -80,5 +80,11 @@ lines(c(xat[1], xat[1]), c(yat+offset, yat))
 lines(c(xat[2], xat[2]), c(yat+offset, yat))
 text((xat[1] + xat[2])/2, yat-2*offset, expression(italic('p')<0.01), cex=1)
 
+yat <- 1.65
+lines(c(xat[2], xat[3]), c(yat, yat))
+lines(c(xat[2], xat[2]), c(yat+offset, yat))
+lines(c(xat[3], xat[3]), c(yat+offset+0.1, yat))
+text((xat[2] + xat[3])/2, yat-2*offset, expression(italic('p')<0.01), cex=1)
+
 dev.off()
 

### 2018-03-16 latex/paper.tex
Edits from personal reading and Brill's comments

@@
 \titleformat*{\section}{\large\bfseries}
-\titleformat*{\subsection}{\normalsize\bfseries}
+\titleformat*{\subsection}{\normalsize\bfseries\itshape}
 
@@
 
-    \section{Summary}
+    \section*{Summary}
     Cilia are sensory organelles that are essential for human development
@@
     They function primarily by relaying extracellular cues to cells
-    \citep{satir2010primary},
+    \citep{satir2010primary, bloodgood2010sensory},
     but can also act as motile propellers in certain cell types
-    \citep{bloodgood2010sensory}.
+    \citep{eley2005cilia}.
     A large number of genetic disorders linked to cilium dysfunction are
@@
     Although substantial effort has been undertaken
-    to elucidate TZ proteins and their functions in cilium assembly and function,
+    to elucidate TZ proteins and their functions in cilium assembly and function
+    \citep{gonccalves2017ciliary},
     processes underlying maturation of TZs are not well understood.
@@
     such as the inability
-    to be migratory \citep{basiri2014migrating} and loss of membrane tethering.
+    to be migratory \citep{basiri2014migrating} and loss of plasma membrane tethering.
     We also report that the \textit{onion rings} (\textit{onr}) allele
@@
 
-    \section{Results}
+    \section*{Results}
     Cilia are sensory organelles that are present on almost all cells in the human body
@@
     but also have roles in cellular and extracellular fluid motility
-    \citep{brooks2014multiciliated, marshall2006cilia},
+    \citep{marshall2006cilia, eley2005cilia, brooks2014multiciliated},
     for example, as the sperm flagellum.
@@
     For example, the conserved TZ protein CEP290 is mutated in at least
-    six different ciliopathies that lie on a spectrum of clinical features and severities
+    six different ciliopathies
+    \citep{rachel2012photoreceptor} that lie on a spectrum of clinical features and severities
     and is important for cilium formation
@@
     Although the protein composition of TZs has been investigated in various
-    studies ranging from single gene analysis to proteomics,
+    studies ranging from single gene analysis to proteomics \citep{gonccalves2017ciliary},
     the process of maturation of the TZ, through which it is converted from an
@@
     TZ maturation has been described in
-    \textit{Paramecium} \citep{aubusson2015transition},
+    Paramecium \citep{aubusson2015transition},
     \textit{Caenorhabditis elegans} \citep{serwas2017centrioles} and
@@
     %
-    \subsection{\PIP{} is essential for transition zone maturation}
+    \subsection*{\PIP{} is essential for transition zone maturation}
     To investigate how reduction of cellular \PIP{} affects ciliogenesis in the
@@
     we used transgenic flies expressing the Salmonella phosphoinositide phosphatase SigD
-    under the control of spermatocyte-specific $\beta$\textsubscript{2}-tubulin promoter (referred to herein as \sigd{}),
+    under the control of spermatocyte-specific $\beta$\textsubscript{2}-tubulin promoter
+    (referred to herein as \sigd{})
     \citep{wei2008depletion}.
@@
     In contrast, Cep290-labelled TZs were significantly longer in \sigd{}
-    compared to wild-type controls by the end of the G2 phase following
+    compared to wild-type controls by the end of G2 phase following
     the period of TZ maturation in spermatocytes (Figure 1B and 1C).
@@
     correlation between Cep290 and Ana1 lengths (Figure 1C).
-    We previously showed that the structure of basal bodies
+    We previously showed that the structure of basal bodies in \sigd{}
     from electron microscopy is normal, and that the localization of the centriolar
@@
     %
-    \subsection{The type I PIP kinase (PIPKI) Skittles (Sktl) regulates TZ length}
+    \subsection*{The type I PIP kinase (PIPKI) Skittles (Sktl) regulates TZ length}
     Whereas \PIP{} is the major substrate for SigD in eukaryotic cells \textit{in vivo}
@@
     We found that Sktl expression was able to suppress TZ hyperelongation
-    in a cilium-autonomous manner (Figure 2A and B).
+    in a cilium-autonomous manner (Figure 2A and 2B).
     We also found that \textit{sktl} clones made
@@
     \citep{baker2004mechanosensory, wei2008depletion}
-    exhibited TZ hyperelongation (Figure 2C),
+    exhibited TZ hyperelongation at a low penetrance (Figure 2C),
     suggesting that Sktl is important for TZ maturation.
+    Note that the \textit{sktl}$^{2.3}$ allele used for making mitotic clones
+    is a hypomorph \citep{gervais2008pip5k}.
 
@@
     \citep{xu2014pipkigamma}.
-    Drosophila PIPKIs arose from the recent duplication of
+    The two Drosophila PIPKIs, namely Sktl and PIP5K59B,
+    arose from the recent duplication of
     the ancestral PIPKI gene,
@@
     %
-    \subsection{Hyperelongated transition zones exhibit signs of functional defects}
+    \subsection*{Hyperelongated transition zones exhibit signs of functional defects}
     We sought to examine whether TZ hyperelongation due to SigD expression
     affected TZ function.
-    During cell elongation following meiosis, the TZ detaches from
+    During cell elongation following meiosis in the Drosophila male germline, the TZ detaches from
     the basal body and migrates along the growing axoneme, maintaining a ciliary compartment
@@
     (Figures 3A and 3B).
-    We previously described ``comet-shaped'' localization of Unc-GFP in these cells,
+    We previously described ``comet-shaped'' localization of Unc-GFP in these cells
+    \citep{wei2008depletion},
     and we find that these hyperelongated Unc signals persist during cellular elongation
@@
     %
-    \subsection{The \textit{onion rings} mutant decouples defects found in cells with reduced levels of \PIP{}}
+    \subsection*{The onion rings mutant decouples defects found in cells with reduced levels of \PIP{}}
     We previously showed that male flies homozygous for the \textit{onion rings}
@@
     Whereas TZs in \sigd{} and \textit{onr} cells anchored properly
-    to the plasma membrane, they were unable to either establish or maintain
+    to the plasma membrane, they were unable to maintain
     membrane connections, and were rendered cytoplasmic (Figure 4A and B) similar to
@@
 
-    \section{Discussion}
+    \section*{Discussion}
     The process of maturation of a TZ from a nascent form to a fully functional one,
@@
     requires orchestration of various proteins and cellular pathways
-    \citep{reiter2012base}.
+    \citep{reiter2012base, gonccalves2017ciliary}.
     In the Drosophila male germline, TZ maturation occurs during the
@@
     In this study, we report two phenotypes associated with
-    hyperelongated TZs that we postulate to be indicators of
-    TZ dysfunction.
+    hyperelongated TZs that we hypothesize to be indicators of
+    dysfunction.
     Firstly, we show that hyperelongated TZs are unable to
@@
 
-    \section{Methods}
-    \subsection{Transgenic flies}
+    \section*{Methods}
+    \subsection*{Transgenic flies}
     Drosophila stocks were cultured on cornmeal molasses agar medium at 25$^{\circ}$C
@@
 
-    \subsection{Antibodies}
+    \subsection*{Antibodies}
     The following primary antibodies were used for immunofluorescence
@@
 
-    \subsection{Fluorescence microscopy}
+    \subsection*{Fluorescence microscopy}
     For live imaging, testes were dissected in phosphate buffered saline (PBS).
@@
     and the specimen was visualized using an epifluorescence microscope.
+    Cells were examined live whenever possible to avoid artefacts from immunostaining.
 
@@
 
-    \subsection{Statistical methods}
+    \subsection*{Statistical methods}
     Statistical analysis and graphing was performed using R (version 3.4)
@@
 
-    \subsection{Phylogenetic analysis}
+    \subsection*{Phylogenetic analysis}
     Candidate orthologs of Skittles and PIP5K9B were queried
@@
 
-    \section{Acknowledgements}
+    \section*{Acknowledgements}
     We are grateful to Brian Ciruna for insightful discussions,
@@
     This research was supported by a grant from the Canadian Institutes for
-    Health and Research to J.A.B (MOP ???).
+    Health and Research to J.A.B (MOP \#130437).
     A.G. was supported by a
@@
 
-    \section{Author contributions}
+    \section*{Author contributions}
     A.G. and J.A.B. conceived the project.
@@
 
-    \section{Declaration of interests}
+    \section*{Declaration of interests}
     The authors declare no competing interests.
 
-    \section{Figure legends}
+    \section*{Figure legends}
 
-    \textbf{Figure 1. SigD expression induces transition zone hyperelongation.}
+    \textbf{\itshape Figure 1. SigD expression induces transition zone hyperelongation.}
     \begin{enumerate}[label={(\Alph*)}, nolistsep]
     \item Schematic diagram of the stages of ciliogenesis in the Drosophila male germline.
-      Stages in brackets correspond to those from \citep{cenci1994chromatin}.
+      Stages in parentheses correspond to those from \citep{cenci1994chromatin}.
     \item \sigd{} expression induces Cep290 hyperelongation in cilia at late G2 phase (white arrowheads).
-    \item Paired Ana1-Cep290 lengths in early and late G2 phase in spermatocytes ($n$ >30 and >65 respectively).
-    \item \sigd{} expression induces hyperelongation of Chibby and Mks1 in late G2 phase.
+    \item Quantification of paired Ana1-Cep290 lengths in early and late G2 phase in spermatocytes ($n$ >30 and >65 respectively).
+    \item \sigd{} expression induces hyperelongation of Chibby (Cby) and Mks1 in late G2 phase.
     \item TZ hyperelongation persists through meiosis but does not affect
-      axoneme outgrowth.
+      axoneme outgrowth. Acetylated tubulin (AcTub) labels the axoneme.
     \end{enumerate}
     \bigskip
-    \textbf{Figure 2. Sktl is important for transition zone maturation.}
+    \textbf{\itshape Figure 2. Sktl is important for transition zone maturation.}
     \begin{enumerate}[label={(\Alph*)}, nolistsep]
-    \item Expression of full-length Sktl suppresses \sigd{}-induced TZ hyperelongation.
-    \item Quantification of Cep290 and Ana1 lengths from control, \sigd{} and Sktl; \sigd{} from (A).
-    \item \textit{sktl}$^{2.3}$ clones exhibit TZ hyperelongation. Cilia are marked using
+    \item Expression of full-length Sktl can suppress \sigd{}-induced TZ hyperelongation in a cilium-autonomous manner.
+      Images were chosen to demonstrate varying levels of rescue of Cep290-GFP length in YFP-Sktl; SigD.
+      White arrowheads mark rescued Cep290 distribution for comparison.
+    \item Quantification of Cep290 and Ana1 lengths from control, \sigd{} and $\beta$\textsubscript{2}t-YFP-Sktl; \sigd{} from (A).
+    \item \textit{sktl}$^{2.3}$ clones exhibit TZ hyperelongation (white arrowheads). Cilia are marked using
       Unc-GFP. The plot on the right shows quantification of Unc-GFP lengths in control and \sigd{}
@@
     \item Phylogenetic tree of PIP5Ks showing conservation of cilium-associated functions.
-      The scale bar represents expected amino acid substitutions per site and branch support values are shown in red (a value of 1 indicates maximum support).
-      Black arrows represent involvement in cilium-associated functions.
+      The scale bar (bottom) represents expected amino acid substitutions per site and branch support values are shown in red (a value of 1 indicates maximum support).
+      Black arrows represent previous evidence of involvement in cilium-associated functions from \citep{xu2016phosphatidylinositol}.
       Abbreviations: Cele (\textit{Caenorhabditis elegans}), Spur (\textit{Strongylocentrotus purpuratus}), Amel (\textit{Apis mellifera}), Aaeg (\textit{Aedes aegypti}), Dana (\textit{Drosophila ananassae}), Dmel (\textit{Drosophila melanogaster}), Hsap (\textit{Homo sapiens}), Mmus (\textit{Mus musculus}), Xtro (\textit{Xenopus tropicalis}), Cint (\textit{Ciona intestinalis}), Scer (\textit{Saccharomyces cerevisiae}).
@@
     \bigskip
-    \textbf{Figure 3. Hyperelongated transition zones display functional defects.}
+    \textbf{\itshape Figure 3. Hyperelongated transition zones display functional defects.}
     \begin{enumerate}[label={(\Alph*)}, nolistsep]
-    \item GFP-tagged Unc is unable to detach from the basal body and migrate in spermatids expressing \sigd{}.
+    \item GFP-tagged Unc is unable to detach from the basal body and migrate (white arrowhead) in spermatids expressing \sigd{}.
       Cell elongation in spermatids is concomitant with elongation of the mitochondrial derivative (dark organelles in the phase contrast images).
@@
       Insets show phase contrast images corresponding to the region shown in the fluorescence images with the
-      elongating mitochondria delineated by a yellow dashed line.
-    \item Structured illumination micrographs of \sigd{} cells show TZ-distal puncta of the centriolar protein Ana1 (yellow arrowheads).
-    \item Treatment of \sigd{} cells with the microtubule stabilizing drug Taxol increases the penetrance of TZ-distal Ana1 (white arrowheads)
-      but does not affect length.
+      elongating mitochondrial derivative delineated by a yellow dashed line.
+    \item Structured illumination micrographs of \sigd{} cells showing TZ-distal puncta of the centriolar protein Ana1 (yellow arrowheads).
+    \item Treatment of control and \sigd{} cells with the microtubule stabilizing drug Taxol.
+      Images were chosen to demonstrate the variety in Cep290 distribution.
+      White arrowheads mark TZ-distal Ana1 localization.
     \item Quantification of Cep290 lengths in Taxol-treated control and \sigd{} cells from (D).
@@
     \bigskip
-    \textbf{Figure 4. The \textit{onion rings} (\textit{onr}) allele of \textit{d}Exo84 decouples TZ hyperlongation from loss of plasma membrane contacts.}
+    \textbf{\itshape Figure 4. The \textit{onion rings} (\textit{onr}) allele of Exo84 decouples TZ hyperlongation from loss of plasma membrane contacts.}
     \begin{enumerate}[label={(\Alph*)}, nolistsep]
-    \item Cells expressing \sigd{} do not maintain plasma membrane-cilium tethering despite initially anchoring to the plasma membrane.
+    \item Cells expressing \sigd{} fail to maintain plasma membrane-cilium tethering despite initially anchoring to the plasma membrane.
       The plasma membrane is marked with CellMask, a cell impermeable dye.
@@
     \item Cells mutant for \textit{onr} do not display hyperelongated acetylated tubulin signal (white arrowheads) at the cilium.
-      Acetylated tubulin marks the axoneme, which fully overlaps with the TZ in spermatocytes \citep{pratt2016drosophila}.
-    \item GFP-tagged Exo70 localizes to basal bodies in late G2 spermatocytes.
+      Acetylated tubulin marks the axoneme, which colocalizes with the TZ in spermatocytes \citep{pratt2016drosophila}.
+    \item GFP-tagged Exo70 localizes to basal bodies in spermatocytes.
     \end{enumerate}
@@
 
-\section{Figures}
+\section*{Figures}
 

### 2018-03-17 latex/paper.tex
Final edits from Brill's suggestions

@@
 \raggedbottom
-
+\vspace{-0.5cm}
 \begin{doublespacing}
   \begin{linenumbers}
-
     \section*{Summary}
@@
     A large number of genetic disorders linked to cilium dysfunction are
-    associated with proteins that localize to the cilium transition zone (TZ),
+    associated with proteins that localize to the ciliary transition zone (TZ),
     a structure at the base of cilia that regulates trafficking in and out
@@
     Although substantial effort has been undertaken
-    to elucidate TZ proteins and their functions in cilium assembly and function
+    to elucidate TZ proteins and their roles in cilium assembly and function
     \citep{gonccalves2017ciliary},
@@
     We show that reduction of cellular \PIP{} levels
-    by expression of the Salmonella phosphoinositide phosphatase SigD,
+    by expression of the Salmonella phosphoinositide phosphatase SigD
     or mutation of
-    the type I phosphatidylinositol phosphate kinase (PIPKI) Skittles (Sktl),
+    the type I phosphatidylinositol phosphate kinase (PIPKI) Skittles (Sktl)
     induces the formation of longer than normal TZs.
@@
     We also report that the \textit{onion rings} (\textit{onr}) allele
-    of the Drosophila Exo84
+    of Drosophila Exo84
     decouples TZ hyperelongation from loss of cilium-plasma membrane tethering.
@@
     Consistent with their importance in cell signalling,
-    defects in cilium formation (i.e. ciliogenesis) are associated with genetic disorders
+    defects in cilium formation (i.e., ciliogenesis) are associated with genetic disorders
     known collectively as ciliopathies, which can display
@@
     This nascent TZ undergoes maturation, during which its structure and protein
-    composition changes, allowing for the
+    composition changes, allowing for
     establishment of a compartmentalized ciliary space, bounded by the ciliary membrane
@@
     for \PIP{} as a modulator of cilium function,
-    we sought to investigate the cause of defects in axoneme assembly in Drosophila male germ cells
-    with reduced levels of \PIP{} from \citep{wei2008depletion}.
+    we sought to investigate the cause of defects we had observed
+    in axoneme assembly in Drosophila male germ cells
+    with reduced levels of \PIP{} \citep{wei2008depletion, fabian2010phosphatidylinositol}.
 
@@
     Drosophila male germline,
-    we used transgenic flies expressing the Salmonella phosphoinositide phosphatase SigD
+    we used transgenic flies expressing the Salmonella PIP phosphatase SigD
     under the control of spermatocyte-specific $\beta$\textsubscript{2}-tubulin promoter
@@
     and we previously showed that \sigd{} induces male sterility
-    due in part to defects in flagellar biosynthesis \citep{wei2008depletion}.
+    associated with defects in flagellar biosynthesis \citep{wei2008depletion}.
     To examine whether these defects were caused by aberrant TZ function,
-    we examined the localization of fluorescently-tagged versions of the
+    we examined localization of fluorescently-tagged versions of the
     centriolar/basal body protein
@@
     In contrast, Cep290-labelled TZs were significantly longer in \sigd{}
-    compared to wild-type controls by the end of G2 phase following
+    compared to wild-type controls by the end of G2 phase, following
     the period of TZ maturation in spermatocytes (Figure 1B and 1C).
@@
     correlation between Cep290 and Ana1 lengths (Figure 1C).
-    We previously showed that the structure of basal bodies in \sigd{}
-    from electron microscopy is normal, and that the localization of the centriolar
+    We previously showed that ultrastructure of basal bodies in \sigd{}
+    is normal, and that localization of the centriolar
     marker GFP-PACT \citep{basto2006flies}
@@
     presumably SigD.
-    Despite the persistence of hyperelongated TZs through meiosis,
+    Despite persistence of hyperelongated TZs through meiosis,
     axonemes, visualized by staining for acetylated tubulin, were able to
@@
     is frequently aberrant,
-    either lacking symmetry completely or containing triplet microtubules
+    either lacking nine-fold symmetry or containing triplet microtubules
     in addition to the usual doublets \citep{wei2008depletion}.
@@
     in a cilium-autonomous manner (Figure 2A and 2B).
-    We also found that \textit{sktl} clones made
-    using Flp/FRT-based mitotic recombination and expressing the
+    We also found that \textit{sktl} clones, made
+    using FLP/FRT-based mitotic recombination and expressing the
     basal body and TZ marker Unc
-    \citep{baker2004mechanosensory, wei2008depletion}
+    \citep{baker2004mechanosensory, wei2008depletion},
     exhibited TZ hyperelongation at a low penetrance (Figure 2C),
@@
     Note that the \textit{sktl}$^{2.3}$ allele used for making mitotic clones
-    is a hypomorph \citep{gervais2008pip5k}.
+    is hypomorphic \citep{gervais2008pip5k}.
 
@@
     cilium formation in Drosophila, and Cp110
-    and is removed from basal bodies in the earliest stages of G2 phase in the Drosophila male germline
+    is removed from basal bodies in the earliest stages of G2 phase in the Drosophila male germline
     \citep{franz2013cp110}.
@@
     and we find that these hyperelongated Unc signals persist during cellular elongation
-    despite elongation of the axoneme (Figure 3A bottommost panel and Figure 1E).
+    (Figure 3A, bottommost panel)
+    despite elongation of the axoneme (Figure 1E).
 
@@
     could increase the penetrance of this phenotype from <5\% in untreated cells
-    to \textgreater25\% in cells treated with 4 $\mu$M Taxol (Figure 3D)
+    to \textgreater25\% in cells treated with 4 $\mu$M Taxol (arrowheads in Figure 3D)
     without affecting Cep290 length significantly (Figure 3E).
-    Taxol treatment stabilizes microtubules and is thought to disrupt TZ maturation
-    by inhibiting microtubule rearrangements \citep{riparbelli2012assembly}.
-    Taxol treatment alone did not induce this phenotype in wild-type controls in our hands
-    at varying concentrations ($p$ <0.01 at 5\% penetrance).
-    Triplet microtubules within the axoneme are also observed in Taxol-treated cells
-    \citep{riparbelli2013unique}, further supporting a relationship between
+    Wild-type controls treated with Taxol did not exhibit TZ-distal Ana1 puncta ($p$ <0.01 at 5\% penetrance).
+    Taxol, a microtubule-stablizing drug, has been hypothesized to disrupt TZ maturation
+    by inhibiting microtubule rearrangements in the Drosophila male germline \citep{riparbelli2012assembly, riparbelli2013unique}.
+    Taxol-treated male germ cells assemble extremely long axonemes as assessed by acetylated tubulin staining \citep{riparbelli2013unique}.
+    Similar to \sigd{}, these axonemes contain triplet microtubules
+    \citep{riparbelli2013unique}, further indicating a functional relationship between
     \PIP{} and microtubule reorganization in TZ maturation.
@@
     defective Exo84 function, we examined TZs in \textit{onr} mutants.
-    Unlike \sigd{}, the \textit{onr} mutant did not display hyperelongated TZs (Figure 4C),
+    Unlike \sigd{}, \textit{onr} did not display hyperelongated TZs (Figure 4C),
     suggesting that Exo84 is dispensable for TZ maturation.
 
-    Due to involvement of exocyst in membrane trafficking at the plasma membrane,
+    Due to involvement of the exocyst in membrane trafficking at the plasma membrane,
     we examined whether cilium-associated membranes were affected in \sigd{}
-    or \textit{onr} mutants in a manner similar to \textit{dila; cby} mutants
+    or \textit{onr} mutants in a manner similar to \textit{dilatory; cby} mutants
     \citep{vieillard2016transition}. 
-    Whereas TZs in \sigd{} and \textit{onr} cells anchored properly
-    to the plasma membrane, they were unable to maintain
-    membrane connections, and were rendered cytoplasmic (Figure 4A and B) similar to
+    Dilatory (Dila) is a conserved TZ protein that cooperates with Cby to assemble the TZ in
+    the Drosophila male germline \citep{vieillard2016transition}.
+    Whereas TZs in \sigd{} and \textit{onr} cells were able to dock
+    at the plasma membrane initially, they were unable to maintain
+    membrane connections, and were rendered cytoplasmic (Figure 4A and B) similar to TZs in
     \textit{dila; cby} mutants.
@@
     we found that GFP-tagged Exo70 localized to centrioles (Figure 4D).
-    Exo70 can directly bind to \PIP{} and mediates the recruitment of
+    Exo70 can directly bind to \PIP{} and mediates recruitment of
     the exocyst complex to the plasma membrane \citep{he2007exo70}.
@@
     In the Drosophila male germline, TZ maturation occurs during the
-    extended G2 phase in spermatocytes prior to meiosis, and can be readily
+    extended G2 phase in mature primary spermatocytes prior to meiosis, and can be readily
     observed by an increase in TZ length using fluorescence microscopy.
     Our results suggest that normal execution of this process
-    requires \PIP{}, and that depletion of \PIP{} induces TZs to
+    requires \PIP{} and that depletion of \PIP{} induces TZs to
     grow longer than normal.
@@
     whereas
-    \textit{cby; dila} and \textit{cby} mutants display hyperelongated TZs
+    \textit{dila; cby} and \textit{cby} mutants display hyperelongated TZs
     \citep{enjolras2012drosophila,vieillard2016transition}.
-    Since both Cby and Mks1 are hyperelongated in \sigd{} cells,
+    Because both Cby and Mks1 are hyperelongated in \sigd{} cells,
     \PIP{} seems to be intimately involved in this process as well, but it does
-    so independantly of Cby and Mks1.
+    so independently of an effect on Cby or Mks1 recruitment.
 
@@
     and these seem to have a conserved role at cilia.
-    In this study, we showed that mutation of the PIPKI Skittles (Sktl)
+    In this study, we showed that mutation of the PIPKI Sktl
     induced hyperelongated TZs, similar to SigD expression.
@@
     The recent discovery of the role of LCCS1-associated GLE1 protein in cilium
-    function \citep{jao2017role} further supports this hypothesis.
+    function \citep{jao2017role} corroborates this hypothesis.
     Our data support the idea that PIPKIs might represent ciliopathy-associated genes
@@
     in spermatids, unlike TZs in normal cells \citep{basiri2014migrating, fabian2012drosophila}.
-    Nonetheless, axonemes can assemble despite the lack of a functional
+    Nonetheless, axonemes can assemble, albeit with aberrant ultrastructure \citep{wei2008depletion},
+    despite the lack of a functional
     TZ or membrane association in \sigd{} cells.
-    As we previously reported, these axonemes frequently exhibit aberrant
-    ultrastructure \citep{wei2008depletion}.
     This is similar to \textit{cep290} \citep{basiri2014migrating}
@@
     in \sigd{} cells.
-    In flies, Ana1 is important for centriole elongation
+    In Drosophila, Ana1 is important for centriole elongation
     \citep{saurya2016drosophila}.
@@
     This may be due to several reasons, such as different dynamics of Ana1 and Asl
-    loading onto centrioles \citep{fu2016conserved, saurya2016drosophila} and the
+    loading onto centrioles \citep{fu2016conserved, saurya2016drosophila} or the
     more peripheral nature of Asl within the centriole \citep{blachon2008drosophila}.
 
-    Members of the exocyst complex, such as Sec10 and Sec6, are
+    Members of the exocyst complex such as Sec10 and Sec8 are
     important for cilium formation in cultured cell lines and zebrafish
     \citep{zuo2009exocyst, lobo2017exocyst, seixas2016arl13b},
-    but their precise roles in ciliogenesis are not well-understood.
+    but their precise roles in ciliogenesis are not well understood.
     The subunits Sec3 and Exo70 regulate exocyst targeting to the plasma
@@
     We previously showed that
-    the \textit{onr} allele of Drosophila \textit{Exo84} phenocopied
+    the \textit{onr} allele of Drosophila \textit{Exo84} phenocopies
     defects in cell polarity and elongation observed in \sigd{}
@@
     at the indicated concentrations ---
-    chicken anti-GFP IgY (abcam) 1:1000;
+    chicken anti-GFP IgY (abcam), 1:1000;
     rat anti-RFP IgG (5F8, ChromoTek), 1:1000;
@@
     To stain for DNA, intact testes were incubated in PBS with
-    Hoechst (1:5000) for 5 minutes.
-    Testes were transferred to a polylysine-coated glass slide in a drop of PBS,
+    Hoechst 33342 (1:5000) for 5 minutes.
+    Testes were transferred to a polylysine-coated glass slide (Thermo Fisher Scientific) in a drop of PBS,
     ruptured using a syringe needle and
@@
     The edges of the coverslip were sealed with nail polish
-    and the specimen was visualized using an epifluorescence microscope.
+    and the specimen was visualized using an epifluorescence microscope (Zeiss Axioplan 2)
+    with an Axiocam CCD camera.
     Cells were examined live whenever possible to avoid artefacts from immunostaining.
@@
     with a predefined
-    concentration of Taxol (Sigma-Aldrich)
+    concentration of Taxol (Sigma-Aldrich) in DMSO
     and incubated overnight in a humidified sterile
@@
 
-    For immunochemistry, testes were dissected in PBS,
+    For immunocytochemistry, testes were dissected in PBS,
     transferred to a polylysine-coated glass slide in a drop of PBS,
     ruptured with a needle, squashed and frozen in liquid nitrogen for 5 minutes.
-    These slides were transferred to ice-cold methanol for 5-10 minutes for fixation.
+    Slides were transferred to ice-cold methanol for 5-10 minutes for fixation.
     Samples were then permeabilized and blocked in PBS with 0.1\% Triton-X and 0.3\% bovine
@@
     Samples were mounted in Dako (Agilent) and imaged with
-    a Leica widefield microscope
+    a Zeiss Axioplan 2 epifluorescence microscope
     or Nikon A1R scanning confocal microscope (SickKids imaging facility).
@@
     Candidate orthologs of Skittles and PIP5K9B were queried
-    from Inparanoid (version 8.0) and FlyBase (version 2.0).
+    from Inparanoid (version 8.0) and FlyBase (version FB2017\_05).
     Poorly annotated protein sequences were confirmed
@@
     \item \textit{sktl}$^{2.3}$ clones exhibit TZ hyperelongation (white arrowheads). Cilia are marked using
-      Unc-GFP. The plot on the right shows quantification of Unc-GFP lengths in control and \sigd{}
+      Unc-GFP. The plot on the right shows quantification of Unc-GFP lengths in control, \textit{sktl}$^{2.3}$ and \sigd{}
       spermatocytes at late G2 phase ($n$ >30).
@@
       The scale bar (bottom) represents expected amino acid substitutions per site and branch support values are shown in red (a value of 1 indicates maximum support).
-      Black arrows represent previous evidence of involvement in cilium-associated functions from \citep{xu2016phosphatidylinositol}.
+      Black arrows represent previous evidence of involvement in cilium-associated functions (from \citep{xu2016phosphatidylinositol}).
       Abbreviations: Cele (\textit{Caenorhabditis elegans}), Spur (\textit{Strongylocentrotus purpuratus}), Amel (\textit{Apis mellifera}), Aaeg (\textit{Aedes aegypti}), Dana (\textit{Drosophila ananassae}), Dmel (\textit{Drosophila melanogaster}), Hsap (\textit{Homo sapiens}), Mmus (\textit{Mus musculus}), Xtro (\textit{Xenopus tropicalis}), Cint (\textit{Ciona intestinalis}), Scer (\textit{Saccharomyces cerevisiae}).
@@
     \begin{enumerate}[label={(\Alph*)}, nolistsep]
-    \item GFP-tagged Unc is unable to detach from the basal body and migrate (white arrowhead) in spermatids expressing \sigd{}.
-      Cell elongation in spermatids is concomitant with elongation of the mitochondrial derivative (dark organelles in the phase contrast images).
-      Insets show phase contrast images corresponding to the region shown in the fluorescence images.
+    \item GFP-tagged Unc is unable to detach from the basal body and migrate in spermatids expressing \sigd{} (white arrowhead).
+      Cell elongation in spermatids is concomitant with elongation of the mitochondrial derivative (dark organelles in the phase-contrast images).
+      Insets show phase-contrast images corresponding to the region shown in the fluorescence images.
     \item Cep290 is unable to detach and migrate from the basal body at the onset of axoneme assembly in \sigd{} spermatids.
-      Insets show phase contrast images corresponding to the region shown in the fluorescence images with the
+      Insets show phase contrast images corresponding to the region shown in the fluorescence images, with the
       elongating mitochondrial derivative delineated by a yellow dashed line.
@@
     \item \textit{onr} mutants do not maintain plasma membrane-cilium tethering.
-    \item Cells mutant for \textit{onr} do not display hyperelongated acetylated tubulin signal (white arrowheads) at the cilium.
+    \item Cells mutant for \textit{onr} do not display hyperelongated acetylated tubulin signal at the cilium (white arrowhead).
       Acetylated tubulin marks the axoneme, which colocalizes with the TZ in spermatocytes \citep{pratt2016drosophila}.

### 2018-03-19 figures/figure-1/analyze/analyze.R
Initial commit

@@ -1,0 +1,49 @@
+library(rstan)
+library(dplyr)
+library(magrittr)
+
+set.seed(1)
+
+rstan_options(auto_write = TRUE)
+options(mc.cores = parallel::detectCores())
+iters <- 2000
+
+df <- read.csv("quantification.csv")
+
+func <- function(x, col.name, sigd.flag, mature.flag) {
+  #' This function prepares the data frame read from 'quantification.csv'
+  #' to be converted into long format.
+  temp <- select(x, matches(col.name))
+  colnames(temp) <- c("cep290", "ana1")
+  temp <- mutate(temp, sigd=sigd.flag, mature=mature.flag)
+  return(temp[complete.cases(temp),])
+}
+
+df.long <- do.call(rbind, 
+                   list(func(df, "wtcepearly|wtanaearly", 0, 0),
+                        func(df, "r19cepearly|r19anaearly", 1, 0),
+                        func(df, "wtceplate|wtanalate", 0, 1),
+                        func(df, "r19ceplate|r19analate", 1, 1)))
+
+y <- df.long$cep290
+stan.out <- stan('mixture.stan',
+                 data=list(y = y,
+                           N = length(y),
+                           K = 3,
+                           J = 2,
+                           htheta = c(1, 1, 1),
+                           hvar = 0.1),
+                 chains = 4,
+                 iter = iters)
+
+mu.pred <- rstan::extract(stan.out, "mu_pred")[[1]]
+mask <- rmultinom(iters, 1, rstan::extract(stan.out, "theta")[[1]])
+
+y.pred <- rep(0, iters)
+for (i in 1:iters) {
+  y.pred[i] <- sum(mask[,i] * mu.pred[i,])
+}
+
+par(mfrow=c(2,1))
+hist(y)
+hist(y.pred)

### 2018-04-06 latex/paper.tex
Edits from Brill's comments + switch to biblatex

@@
 \usepackage{charter}
-%\usepackage[charter]{mathdesign} % I hate how charter greeks look
-\usepackage[numbers]{natbib}
+% \usepackage[charter]{mathdesign} % I hate how charter greeks look
+%\usepackage[numbers]{natbib}
 \usepackage{enumitem}
@@
 \graphicspath{{../figures/}}
-\bibliographystyle{unsrtcurrbiol}
-
+\usepackage[style=authoryear-icomp,maxbibnames=9,maxcitenames=2,backend=biber]{biblatex}
+%\bibliographystyle{unsrtapalike}
+%\bibliography{bibttc.bib}
+\addbibresource{\jobname.bib}
 % title font size
@@
 % newcommand
+\newcommand\tab[1][1cm]{\hspace*{#1}}
 \newcommand{\PIP}{PIP\textsubscript{2}}
@@
 \newcommand{\sktl}{\textit{sktl}}
+\newcommand{\ie}{\textit{i}.\textit{e}.}
 \makeatletter
@@
 \author[2]{Lacramioara Fabian \thanks{\url{lacramioara.fabian@sickkids.ca}}}
-\author[1,2]{Julie A. Brill \thanks{\url{julie.brill@sickkids.ca} (Corresponding author)}}
+\author[1,2,3]{Julie A. Brill \thanks{\url{julie.brill@sickkids.ca}}}
 
-\affil[1]{\small Department of Molecular Genetics, University of Toronto, Toronto, ON M5S 1A8, Canada}
-\affil[2]{\small Program in Cell Biology, Hospital for Sick Children, Toronto, ON M5G 1X8, Canada}
+\affil[1]{\small Department of Molecular Genetics, University of Toronto, Toronto, Ontario, M5S 1A8, Canada}
+\affil[2]{\small Cell Biology Program, The Hospital for Sick Children, Toronto, Ontario, M5G 0A4, Canada}
+\affil[3]{\small Institute of Medical Science, University of Toronto, Toronto, Ontario, M5S 1A8, Canada}
 \date{}
@@
 \raggedbottom
+\vspace{2em}
+  To whom correspondence should be addressed: \\
+  \begin{tabular}{l}
+    Julie A. Brill \\
+    Cell Biology Program \\ 
+    The Hospital for Sick Children \\
+    PGCRL Building, 15th Floor \\
+    686 Bay Street, Room 15.9716 \\
+    Toronto, Ontario M5G 0A4 \\ Canada\\
+    Phone: (416) 813-8863 \\
+    Email: \url{julie.brill@sickkids.ca} \\
+  \end{tabular}
+
+\vspace{2em}
+\textbf{Short title}: \PIP{} regulates the ciliary TZ
+
+\textbf{Keywords}: Phosphatidylinositol 4,5-bisphosphate, Skittles, Cep290, cilia, transition zone
+
+\textbf{Brief summary statement}: The authors show that the membrane phospholipid \PIP{},
+and the kinase that produces \PIP{} called Skittles, are needed for
+normal ciliary transition zone morphology and function in the Drosophila male germline.
+\newpage
+
 \vspace{-0.5cm}
@@
   \begin{linenumbers}
-    \section*{Summary}
+    \section*{Abstract}
     Cilia are sensory organelles that are essential for human development
-    and physiology \citep{satir2010primary, marshall2006cilia}.
-    They function primarily by relaying extracellular cues to cells
-    \citep{satir2010primary, bloodgood2010sensory},
-    but can also act as motile propellers in certain cell types
-    \citep{eley2005cilia}.
+    and physiology.
     A large number of genetic disorders linked to cilium dysfunction are
@@
     a structure at the base of cilia that regulates trafficking in and out
-    of the cilium \citep{reiter2012base, szymanska2012transition}.
-    Although substantial effort has been undertaken
-    to elucidate TZ proteins and their roles in cilium assembly and function
-    \citep{gonccalves2017ciliary},
+    of the cilium.
+    Despite substantial effort to identify TZ proteins and their roles
+    in cilium assembly and function,
     processes underlying maturation of TZs are not well understood.
@@
     phosphatidylinositol 4,5-bisphosphate
-    (\PIP{}) in TZ maturation and length regulation
+    (\PIP{}) in TZ maturation
     in the \textit{Drosophila melanogaster} male germline.
     We show that reduction of cellular \PIP{} levels
-    by expression of the Salmonella phosphoinositide phosphatase SigD
+    by ectopic expression of a phosphoinositide phosphatase
     or mutation of
-    the type I phosphatidylinositol phosphate kinase (PIPKI) Skittles (Sktl)
-    induces the formation of longer than normal TZs.
-    These hyperelongated TZs exhibit signs of functional defects,
-    such as the inability
-    to be migratory \citep{basiri2014migrating} and loss of plasma membrane tethering.
+    the type I phosphatidylinositol phosphate kinase Skittles
+    induces formation of longer than normal TZs.
+    These hyperelongated TZs exhibit functional defects,
+    including loss of plasma membrane tethering.
     We also report that the \textit{onion rings} (\textit{onr}) allele
@@
     by promoting proper TZ maturation.
+    \newpage
 
-    \section*{Results}
-    Cilia are sensory organelles that are present on almost all cells in the human body
-    \citep{satir2010primary, marshall2006cilia}.
-    They function in signal reception and transduction in response to extracellular cues,
-    but also have roles in cellular and extracellular fluid motility
-    \citep{marshall2006cilia, eley2005cilia, brooks2014multiciliated},
-    for example, as the sperm flagellum.
-    Consistent with their importance in cell signalling,
-    defects in cilium formation (i.e., ciliogenesis) are associated with genetic disorders
-    known collectively as ciliopathies, which can display
-    neurological defects \citep{valente2014primary},
-    skeletal abnormalities \citep{hammarsjo2017novel},
-    and infertility \citep{inaba2016sperm}, in addition to other phenotypes
-    \citep{waters2011ciliopathies}.
+    \section*{Introduction}
+    Cilia are sensory organelles that are important for
+    signalling in response to extracellular cues,
+    and for cellular and extracellular fluid motility
+    \citep{satir2010primary, marshall2006cilia, eley2005cilia, brooks2014multiciliated}.
+    Consistent with their importance,
+    defects in cilium formation (\ie{} ciliogenesis) are associated with genetic disorders
+    known as ciliopathies, which can display
+    neurological, skeletal and fertility defects, in addition to other phenotypes
+    \citep{waters2011ciliopathies, valente2014primary, hammarsjo2017novel, inaba2016sperm}.
     Many ciliopathies are associated with mutations in proteins that localize
@@
     functions as a diffusion barrier and regulates the
-    bidirectional transport of protein cargo at the base of the cilium
+    bidirectional transport of protein cargo at the cilium base
     \citep{reiter2012base, szymanska2012transition}.
-    The TZ is essential for ciliogenesis and function.
     For example, the conserved TZ protein CEP290 is mutated in at least
     six different ciliopathies
-    \citep{rachel2012photoreceptor} that lie on a spectrum of clinical features and severities
+    \citep{rachel2012photoreceptor}
     and is important for cilium formation
-    and function in both humans \citep{shimada2017vitro, stowe2012centriolar}
+    and function in humans \citep{shimada2017vitro, stowe2012centriolar}
     and Drosophila \citep{basiri2014migrating}.
     Although the protein composition of TZs has been investigated in various
-    studies ranging from single gene analysis to proteomics \citep{gonccalves2017ciliary},
-    the process of maturation of the TZ, through which it is converted from an
+    studies \citep{gonccalves2017ciliary},
+    the process of TZ maturation, through which it is converted from an
     immature form to one competent at supporting
@@
     Ciliogenesis begins with assembly of a nascent TZ at the tip of
-    the basal body \citep{reiter2012base}.
-    This nascent TZ undergoes maturation, during which its structure and protein
-    composition changes, allowing for
-    establishment of a compartmentalized ciliary space, bounded by the ciliary membrane
-    and the TZ, in which axoneme assembly and signalling can occur.
-    The axoneme is a microtubule-based structure that forms the core of all cilia and flagella.
-    In the Drosophila male germline, nascent TZs first assemble on basal bodies
-    during early G2 phase in spermatocytes \citep{riparbelli2012assembly}.
-    This occurs concomitantly with anchoring of cilia to the plasma membrane,
-    rearrangment of microtubules within the TZ \citep{gottardo2013cilium},
+    the basal body (BB) \citep{reiter2012base}.
+    During TZ maturation, its structure and protein
+    composition change, allowing for
+    establishment of a compartmentalized space, bounded by the ciliary membrane
+    and the TZ, where assembly of the axoneme, a microtubule-based structure
+    that forms the core of cilia,
+    and signalling can occur.
+    In Drosophila, nascent TZs first assemble on BBs
+    during early G2 phase in primary spermatocytes \citep{riparbelli2012assembly}.
+    This occurs concomitantly with anchoring of cilia to the plasma membrane (PM),
+    microtubule remodelling within the TZ \citep{gottardo2013cilium},
     and establishment of a
@@
     \textit{Caenorhabditis elegans} \citep{serwas2017centrioles} and
-    \textit{Drosophila melanogaster} \citep{gottardo2013cilium},
+    Drosophila \citep{gottardo2013cilium},
     and is most readily observed by an increase in TZ length
@@
     We previously showed that the membrane lipid phosphatidylinositol 4,5-bisphosphate
-    (\PIP{}) is essential for formation of the sperm flagellum in the Drosophila
+    (\PIP{}) is essential for formation of the axoneme in the Drosophila
     male germline \citep{wei2008depletion, fabian2010phosphatidylinositol}.
-    \PIP{} is one of seven different phosphoinositides (PIPs) present in eukaryotes.
-    It localizes primarily to the plasma membrane, where it is essential for
-    modulation of the actin cytoskeleton and vesicle trafficking, as well as numerous
+    \PIP{}, one of seven different phosphoinositides (PIPs) present in eukaryotes,
+    localizes primarily to the PM, where it is required for
+    vesicle trafficking, among
     other processes \citep{balla2013phosphoinositides}.
-    \PIP{} has been linked to cilium function in recent studies.
-    While the ciliary membrane has been found to contain very little \PIP{} due to the action
+    \PIP{} has recently been linked to cilium function.
+    Although the ciliary membrane contains very little \PIP{} due to the action
     of the cilium resident PIP phosphatase INPP5E,
@@
     \citep{nakatsu2015phosphoinositide}.
-    Inactivation of INPP5E leads to a build up of intraciliary \PIP{},
-    which disrupts transport of components of the Hedgehog signalling pathway in vertebrates
+    Inactivation of INPP5E causes a build up of intraciliary \PIP{},
+    which disrupts transport of Hedgehog signalling proteins in vertebrates
     \citep{chavez2015modulation, garcia2015phosphoinositides, conduit2017compartmentalized}
     and ion channels involved in mechanotransduction in Drosophila \citep{park2015ciliary}.
-    In light of this current understanding of the role
+    In light of the current understanding of the role
     for \PIP{} as a modulator of cilium function,
@@
 
+    \section*{Results}
     % 
@@
     we used transgenic flies expressing the Salmonella PIP phosphatase SigD
-    under the control of spermatocyte-specific $\beta$\textsubscript{2}-tubulin promoter
-    (referred to herein as \sigd{})
+    under control of spermatocyte-specific $\beta$\textsubscript{2}-tubulin promoter
+    (hereafter \sigd{})
     \citep{wei2008depletion}.
-    Note that \sigd{} corresponds to ``SigD-high'' in \citep{fabian2010phosphatidylinositol}.
-    SigD dephosphorylates \PIP{} \textit{in vivo},
-    and we previously showed that \sigd{} induces male sterility
-    associated with defects in flagellar biosynthesis \citep{wei2008depletion}.
-    To examine whether these defects were caused by aberrant TZ function,
-    we examined localization of fluorescently-tagged versions of the
-    centriolar/basal body protein
-    Ana1 (homolog of CEP295) \citep{goshima2007genes, blachon2009proximal}
-    and the conserved TZ protein Cep290 \citep{basiri2014migrating}
-    during early steps of cilium assembly in spermatocytes.
-    Cep290 distribution appeared similar in control and \sigd{} in early G2 phase
+    To examine whether axoneme defects in \sigd{}
+    \citep{wei2008depletion}
+    were caused by aberrant TZ function,
+    we examined localization of fluorescently-tagged
+    centriolar/BB protein
+    Ana1 (CEP295 homolog) \citep{goshima2007genes, blachon2009proximal}
+    and conserved TZ protein Cep290 \citep{basiri2014migrating}
+    during early steps of cilium assembly.
+    Cep290 distribution appeared similar in control and \sigd{} in early G2 phase,
     when TZs are still immature.
     In contrast, Cep290-labelled TZs were significantly longer in \sigd{}
-    compared to wild-type controls by the end of G2 phase, following
-    the period of TZ maturation in spermatocytes (Figure 1B and 1C).
+    compared to controls by late G2 phase, following
+    the period of TZ maturation (Figure 1B and 1C).
     Unlike Drosophila \textit{cep290} mutants, which contain
-    longer than normal basal bodies \citep{basiri2014migrating},
+    longer than normal BBs \citep{basiri2014migrating},
     Ana1 length was not affected in \sigd{},
     and we did not observe a strong
-    correlation between Cep290 and Ana1 lengths (Figure 1C).
-    We previously showed that ultrastructure of basal bodies in \sigd{}
-    is normal, and that localization of the centriolar
+    correlation between Cep290 and Ana1 lengths (Figure 1D).
+    Consistent with this result, the ultrastructure of BBs in \sigd{}
+    is normal, and localization of the centriolar
     marker GFP-PACT \citep{basto2006flies}
@@
     In contrast, TZ proteins Chibby (Cby) \citep{enjolras2012drosophila} and
-    Mks1 \citep{vieillard2016transition}
-    exhibited hyperelongation in \sigd{} (Figure 1D),
-    suggesting that this phenotype is not specific to Cep290 but is shared
-    by other members of the Drosophila TZ.
-    TZ hyperelongation was a highly penetrant phenotype (\textgreater 70\%
-    in spermatocytes at late G2 phase)
-    and showed high intra-cyst correlation (\textgreater 0.95) suggestive
-    of a dosage-based response to a shared cellular factor,
+    Mks1 \citep{vieillard2016transition, pratt2016drosophila}
+    exhibited hyperelongation in \sigd{} (Figure 1E),
+    indicating that this phenotype is not unique to Cep290.
+    TZ hyperelongation was a highly penetrant phenotype (\textgreater 70\%)
+    and showed high correlation (\textgreater 0.95)
+    within syncytial germ cell cysts,
+    suggestive of a dosage-based response to a shared cellular factor,
     presumably SigD.
     Despite persistence of hyperelongated TZs through meiosis,
-    axonemes, visualized by staining for acetylated tubulin, were able to
-    elongate normally in post-meiotic cells (Figure 1E).
-    However, as we showed previously, the ultrastructure of these axonemes
+    axonemes were able to
+    elongate normally in post-meiotic cells (Figure 1F).
+    Nonetheless, the ultrastructure of these axonemes
     is frequently aberrant,
@@
     \subsection*{The type I PIP kinase (PIPKI) Skittles (Sktl) regulates TZ length}
-    Whereas \PIP{} is the major substrate for SigD in eukaryotic cells \textit{in vivo}
+    Although \PIP{} is its major substrate in eukaryotic cells \textit{in vivo}
     \citep{terebiznik2002elimination, zhou2001salmonella, sengupta2013depletion},
-    SigD can also dephosphorylate other PIPs \textit{in vitro}
+    SigD can dephosphorylate multiple PIPs \textit{in vitro}
     \citep{norris1998sopb}.
     To address whether TZ hyperelongation observed in \sigd{} represented a
-    physiologically relevant phenotype in response to decreased \PIP{},
-    we attempted to rescue the TZ phenotype by
+    physiologically relevant phenotype due to decreased \PIP{},
+    we attempted to rescue it by
     co-expressing \sigd{} with
     fluorescently-tagged Skittles (Sktl)
-    using the same $\beta$\textsubscript{2}-tubulin promoter.
+    under control of $\beta$\textsubscript{2}-tubulin promoter.
     We found that Sktl expression was able to suppress TZ hyperelongation
     in a cilium-autonomous manner (Figure 2A and 2B).
-    We also found that \textit{sktl} clones, made
-    using FLP/FRT-based mitotic recombination and expressing the
-    basal body and TZ marker Unc
+    Furthermore, the BB/TZ protein Unc-GFP
     \citep{baker2004mechanosensory, wei2008depletion},
-    exhibited TZ hyperelongation at a low penetrance (Figure 2C),
-    suggesting that Sktl is important for TZ maturation.
-    Note that the \textit{sktl}$^{2.3}$ allele used for making mitotic clones
-    is hypomorphic \citep{gervais2008pip5k}.
+    exhibited TZ hyperelongation at a low penetrance in \textit{sktl}$^{2.3}$
+    mutant clones (Figure 2C),
+    indicating that Sktl is important for TZ maturation.
 
-    A previous report showed the vertebrate PIPKI$\gamma$ to be
-    important for cilium formation in cultured cell lines
-    \citep{xu2014pipkigamma}.
-    The two Drosophila PIPKIs, namely Sktl and PIP5K59B,
-    arose from the recent duplication of
+    Vertebrate PIPKI$\gamma$ is important for cilium formation in cultured cells
+    \citep{xu2016phosphatidylinositol}.
+    The two Drosophila PIPKIs, Sktl and PIP5K59B,
+    arose from recent duplication of
     the ancestral PIPKI gene,
@@
     However, unlike the human PIPKI$\gamma$, which licenses TZ assembly
-    by promoting CP110 removal from basal bodies \citep{xu2016phosphatidylinositol},
+    by promoting CP110 removal from BBs \citep{xu2016phosphatidylinositol},
     our results suggest that Sktl functions in
-    regulating TZ length in the Drosophila male germline,
-    but not TZ assembly. 
+    regulating TZ length but not TZ assembly. 
     Notably, neither inactivation nor overexpression of \textit{cp110} affects
     cilium formation in Drosophila, and Cp110
-    is removed from basal bodies in the earliest stages of G2 phase in the Drosophila male germline
+    is removed from BBs in early primary spermatocytes
     \citep{franz2013cp110}.
@@
     \subsection*{Hyperelongated transition zones exhibit signs of functional defects}
-    We sought to examine whether TZ hyperelongation due to SigD expression
+    We next sought to examine whether TZ hyperelongation due to SigD expression
     affected TZ function.
-    During cell elongation following meiosis in the Drosophila male germline, the TZ detaches from
-    the basal body and migrates along the growing axoneme, maintaining a ciliary compartment
+    Following meiosis in the Drosophila male germline, TZs detach from
+    the BB and migrate along the growing axoneme, maintaining a ciliary compartment
     at the distal-most {\raise.17ex\hbox{$\scriptstyle\sim$}}5$\mu$m where tubulin
-    is presumably incorporated into the axoneme
+    is incorporated into the axoneme
     \citep{basiri2014migrating, fabian2012drosophila}.
     As shown by Unc and Cep290 localization,
-    TZs that assembled in \sigd{} cells were frequently incapable of detaching from
-    the basal body and migrating along the axoneme despite
-    axoneme elongation (Figure 1E) and cellular elongation
+    TZs in \sigd{} were frequently incapable of detaching from
+    BBs and migrating along axonemes despite
+    axoneme elongation (Figure 1E) and cell elongation
     (Figures 3A and 3B).
-    We previously described ``comet-shaped'' localization of Unc-GFP in these cells
-    \citep{wei2008depletion},
-    and we find that these hyperelongated Unc signals persist during cellular elongation
+    The previously reported ``comet-shaped'' Unc-GFP localization in \sigd{}
+    \citep{wei2008depletion}
+    persists during cell elongation after meiosis
     (Figure 3A, bottommost panel)
@@
 
-    In Drosophila and humans, basal bodies consist of microtubule triplets
+    In Drosophila and humans, BBs consist of microtubule triplets
     \citep{jana2016drosophila, lattao2017centrioles},
-    whereas the axoneme contains microtubule doublets due to obstruction of
-    the C-tubule at the TZ \citep{gottardo2013cilium}.
-    Consistent with a defect in the TZ barrier and the presence of
+    whereas axonemes contain microtubule doublets due to obstruction of
+    C-tubules at the TZ \citep{gottardo2013cilium}.
+    Consistent with a defect in this barrier and the presence of
     microtubule triplets in axonemes in \sigd{} \citep{wei2008depletion},
-    we observed that a subset of cilia (<5\%) in SigD-expressing cells
-    contained puncta of Ana1, a core centriolar protein, at the tips
-    of TZs marked with Cep290 (Figure 3C).
-    We found that treatment of germ cells with Taxol, as in \citep{riparbelli2013unique},
-    could increase the penetrance of this phenotype from <5\% in untreated cells
+    a subset of cilia (<5\%) in \sigd{}
+    contained puncta of the core centriolar protein Ana1 at the distal
+    tips of TZs (Figure 3C).
+    Treatment of germ cells with the microtubule-stabilizing drug
+    Taxol increased the penetrance of this phenotype from <5\% in untreated cells
     to \textgreater25\% in cells treated with 4 $\mu$M Taxol (arrowheads in Figure 3D)
-    without affecting Cep290 length significantly (Figure 3E).
-    Wild-type controls treated with Taxol did not exhibit TZ-distal Ana1 puncta ($p$ <0.01 at 5\% penetrance).
-    Taxol, a microtubule-stablizing drug, has been hypothesized to disrupt TZ maturation
-    by inhibiting microtubule rearrangements in the Drosophila male germline \citep{riparbelli2012assembly, riparbelli2013unique}.
-    Taxol-treated male germ cells assemble extremely long axonemes as assessed by acetylated tubulin staining \citep{riparbelli2013unique}.
-    Similar to \sigd{}, these axonemes contain triplet microtubules
-    \citep{riparbelli2013unique}, further indicating a functional relationship between
-    \PIP{} and microtubule reorganization in TZ maturation.
-    Fluorescently-tagged Asterless (homolog of CEP152), a pericentriolar protein
+    without significantly affecting Cep290 length (Figure 3E).
+    Taxol-treated controls did not exhibit TZ-distal Ana1 puncta ($p$ <0.01 at 5\% penetrance).
+    Fluorescently-tagged pericentriolar protein Asterless (CEP152 homolog)
     \citep{blachon2008drosophila, dzhindzhev2010asterless},
@@
     sites are not fully centriolar in protein composition.
+    Taxol has been hypothesized to disrupt TZ maturation
+    by inhibiting microtubule remodelling in the Drosophila male germline \citep{riparbelli2012assembly, riparbelli2013unique}.
+    Similar to \sigd{},
+    Taxol-treated male germ cells assemble extremely long axonemes
+    that contain triplet microtubules
+    \citep{riparbelli2013unique}, further supporting a functional relationship between
+    \PIP{} and microtubule reorganization in TZ maturation.
 
@@
     % 
-    \subsection*{The onion rings mutant decouples defects found in cells with reduced levels of \PIP{}}
-    We previously showed that male flies homozygous for the \textit{onion rings}
-    (\textit{onr}) mutant of Drosophila Exo84 were sterile, and had phenotypes
-    similar to \sigd{} such as defects in cell polarity \citep{wei2008depletion}.
+    \subsection*{The onion rings (\textit{onr}) mutant decouples defects found in cells with reduced levels of \PIP{}}
+    Male flies homozygous for the \textit{onion rings}
+    (\textit{onr}) mutant of Drosophila Exo84 are sterile and exhibit defects
+    in cell elongation and polarity
+    similar to \sigd{} \citep{wei2008depletion}.
     Exo84 is a component of the octameric exocyst complex, which binds
-    \PIP{} and regulates membrane trafficking at the plasma membrane.
+    \PIP{} and regulates membrane trafficking at the PM 
+    \citep{he2007exo70}.
     To investigate whether defects in TZ hyperelongation could be explained by
     defective Exo84 function, we examined TZs in \textit{onr} mutants.
-    Unlike \sigd{}, \textit{onr} did not display hyperelongated TZs (Figure 4C),
+    Unlike \sigd{}, \textit{onr} did not display hyperelongated TZs (Figure 4A),
     suggesting that Exo84 is dispensable for TZ maturation.
 
-    Due to involvement of the exocyst in membrane trafficking at the plasma membrane,
+    Due to involvement of the exocyst in trafficking at the PM,
     we examined whether cilium-associated membranes were affected in \sigd{}
@@
     \citep{vieillard2016transition}. 
-    Dilatory (Dila) is a conserved TZ protein that cooperates with Cby to assemble the TZ in
+    Dilatory (Dila), a conserved TZ protein, cooperates with Cby to assemble TZs in
     the Drosophila male germline \citep{vieillard2016transition}.
     Whereas TZs in \sigd{} and \textit{onr} cells were able to dock
-    at the plasma membrane initially, they were unable to maintain
-    membrane connections, and were rendered cytoplasmic (Figure 4A and B) similar to TZs in
+    at the PM initially, they were unable to maintain
+    membrane connections, and were rendered cytoplasmic (Figure 4B and C) similar to TZs in
     \textit{dila; cby} mutants.
-    Although we were not able to determine the localization of Exo84 due to the
-    lack of available reagents,
-    we found that GFP-tagged Exo70 localized to centrioles (Figure 4D).
-    Exo70 can directly bind to \PIP{} and mediates recruitment of
-    the exocyst complex to the plasma membrane \citep{he2007exo70}.
+    We found that fluorescently-tagged Exo70, a \PIP{}-binding exocyst subunit,
+    localized to BBs (Figure 4D).
     Our results suggest that the exocyst, and Exo84 in particular, regulates
@@
     grow longer than normal.
-    Regulation of TZ length in the Drosophila male germline has been reported
-    previously.
-    For example, \textit{mks1} mutants have shorter TZs \citep{pratt2016drosophila},
-    whereas
-    \textit{dila; cby} and \textit{cby} mutants display hyperelongated TZs
-    \citep{enjolras2012drosophila,vieillard2016transition}.
+    Similar to \sigd{}, Drosophila \textit{dila; cby} and \textit{cby}
+    mutants display hyperelongated TZs
+    \citep{enjolras2012drosophila,vieillard2016transition},
+    whereas \textit{mks1} mutants have shorter TZs \citep{pratt2016drosophila}.
     Because both Cby and Mks1 are hyperelongated in \sigd{} cells,
-    \PIP{} seems to be intimately involved in this process as well, but it does
-    so independently of an effect on Cby or Mks1 recruitment.
+    \PIP{} seems to regulate TZ length independently of an effect on Cby or Mks1 recruitment.
 
-    The majority of \PIP{} at the plasma membrane is produced by PIPKIs
-    \citep{balla2013phosphoinositides, hammond2012pi4p}
-    and these seem to have a conserved role at cilia.
+    We also show that hyperelongated TZs are dysfunctional.
+    Similar to \textit{dila}; \textit{cby} \citep{vieillard2016transition} and
+    \textit{cep290} \citep{basiri2014migrating}
+    mutants, axonemes can assemble in \sigd{}, albeit
+    with aberrant ultrastructure
+    \citep{wei2008depletion}, despite the lack of functional TZs
+    or membrane association.
+    The presence of TZ-distal Ana1 puncta in \sigd{} cells, without an increase
+    in BB length seen in \textit{cep290} mutants lacking a functional TZ barrier,
+    suggests that \sigd{} expression selectively disrupts the ability of TZs to restrict C-tubules and
+    Ana1 without abolishing the TZ barrier entirely.
+    CEP295, the human Ana1 ortholog, regulates
+    post-translational modification of centriolar
+    microtubules \citep{chang2016cep295}, which may explain the presence of Ana1 along with
+    supernumerary microtubules in \sigd{} cells.
+    Asterless (Asl), a pericentriolar protein
+    important for centrosome formation and centriole duplication
+    \citep{blachon2008drosophila, dzhindzhev2010asterless}, did not
+    exhibit this TZ-distal localization, possibly due to different dynamics of Ana1 and Asl
+    loading onto centrioles \citep{fu2016conserved, saurya2016drosophila} and the
+    more peripheral nature of Asl within the centriole \citep{blachon2008drosophila}.
+
+    The majority of \PIP{} at the PM is produced by PIPKIs
+    \citep{balla2013phosphoinositides, hammond2012pi4p}.
     In this study, we showed that mutation of the PIPKI Sktl
-    induced hyperelongated TZs, similar to SigD expression.
-    We were able rescue TZ hyperelongation in \sigd{} by expression of full-length Sktl.
-    Interestingly, some cells showed cilium-autonomous suppression of TZ length.
-    Because the development of the Drosophila male germline occurs in syncytial cysts
-    of cells that share the same cytoplasm,
-    cilium-autonomous rescue suggests Skittles might function \textit{in situ}
-    to regulate TZ maturation in these cells.
+    induced hyperelongated TZs
+    and that expression of Sktl could suppress TZ hyperelongation in \sigd{},
+    with some cells showing cilium-autonomous suppression,
+    suggesting Skittles might function \textit{in situ} to regulate TZ length.
     In humans, \textit{PIPKI$\gamma$} is linked to lethal congenital contractural
-    syndrome type 3 (LCCS3), which has been suggested to represent a ciliopathy.
-    The recent discovery of the role of LCCS1-associated GLE1 protein in cilium
+    syndrome type 3 (LCCS3), which has been suggested to represent a ciliopathy
+    \citep{xu2016phosphatidylinositol}.
+    The recent discovery of a role for LCCS1-associated GLE1 protein in cilium
     function \citep{jao2017role} corroborates this hypothesis.
     Our data support the idea that PIPKIs might represent ciliopathy-associated genes
-    or genetic modifiers of disease, as previously postulated
-    \citep{xu2016phosphatidylinositol}.
-
-    In this study, we report two phenotypes associated with
-    hyperelongated TZs that we hypothesize to be indicators of
-    dysfunction.
-    Firstly, we show that hyperelongated TZs are unable to
-    detach from basal bodies at the onset of axoneme elongation
-    in spermatids, unlike TZs in normal cells \citep{basiri2014migrating, fabian2012drosophila}.
-    Nonetheless, axonemes can assemble, albeit with aberrant ultrastructure \citep{wei2008depletion},
-    despite the lack of a functional
-    TZ or membrane association in \sigd{} cells.
-    This is similar to \textit{cep290} \citep{basiri2014migrating}
-    and \textit{dila}; \textit{cby} \citep{vieillard2016transition}
-    mutants,
-    which can assemble spermatid axonemes despite lacking
-    functional TZs.
-
-    We also report a novel phenotype of TZ-distal Ana1 localization
-    in \sigd{} cells.
-    In Drosophila, Ana1 is important for centriole elongation
-    \citep{saurya2016drosophila}.
-    The human ortholog of Ana1, called CEP295, regulates
-    centriole elongation by building the distal centriole and
-    enhancing post-translational modification of centriolar
-    microtubules \citep{chang2016cep295}.
-    The observation that Drosophila \textit{cep290} mutants,
-    which lack a functional TZ diffusion barrier
-    \citep{basiri2014migrating},
-    contain hyperelongated centrioles suggests that the
-    TZ normally suppresses centriole length.
-    Our observations of Ana1 at the tips of hyperelongated TZs
-    without an increase in centriole length suggest that \sigd{} expression
-    does not entirely disrupt the TZ diffusion barrier, but only certain aspects,
-    such as the inability to restrict C-tubules and Ana1.
-    We found that
-    Asterless (Asl), a pericentriolar protein
-    \citep{blachon2008drosophila}
-    important for centrosome formation and centriole duplication, did not
-    exhibit this TZ-distal localization.
-    This may be due to several reasons, such as different dynamics of Ana1 and Asl
-    loading onto centrioles \citep{fu2016conserved, saurya2016drosophila} or the
-    more peripheral nature of Asl within the centriole \citep{blachon2008drosophila}.
+    or genetic modifiers of disease.
 
@@
     We previously showed that
-    the \textit{onr} allele of Drosophila \textit{Exo84} phenocopies
+    the \textit{onr} allele of Drosophila \textit{exo84} phenocopies
     defects in cell polarity and elongation observed in \sigd{}
     \citep{fabian2010phosphatidylinositol}.
-    Here, we show that the \textit{onr} allele of the Drosophila Exo84
+    Here, we show that the \textit{onr} mutation
     phenocopies the loss of cilium-membrane contacts in \sigd{}, similar to
@@
     Thus, TZ hyperelongation is not a prerequisite for the failure of
-    cilium-plasma membrane association in male germ cells,
+    cilium-PM association in male germ cells,
     and Exo84 uniquely regulates the latter process,
-    potentially by supplying membrane required to maintain cilium-plasma membrane
+    potentially by supplying membrane required to maintain cilium-PM
     association.
     This result is supported by the Drosophila \textit{cep290} mutant,
-    which lacks a functional TZ but retains cilium-plasma membrane
+    which lacks a functional TZ but retains cilium-PM
     association \cite{basiri2014migrating}.
@@
     A. Guichet \citep{gervais2008pip5k}.
+    Clones were induced by heat shock for two hours on days 3, 4 and 5 after egg laying.
     \textit{w}\textsuperscript{1118} was used as the wild-type control.
@@
     All $t$-tests were unpaired and two-sided with Welch's correction for unequal variances.
-    $n$ represents the pooled number of samples from multiple biological replicates.
+    $n$ represents the pooled number of samples (individual cilia) from multiple flies.
     A significance level of 0.01 was fixed \textit{a priori} for all classical analyses.
@@
     \item Quantification of paired Ana1-Cep290 lengths in early and late G2 phase in spermatocytes ($n$ >30 and >65 respectively).
-    \item \sigd{} expression induces hyperelongation of Chibby (Cby) and Mks1 in late G2 phase.
+    \item Lengths of Ana1-tdTomato versus Cep290-GFP in control and \sigd{} cells at late G2 phase from (C) showing negligible correlation.
+      Regression lines are plotted in red, and the Pearson correlation coefficient ($r$) is indicated on the bottom-left.
+    \item \sigd{} expression induces hyperelongation of the TZ proteins Chibby (Cby) and Mks1 in late G2 phase (white arrowheads).
     \item TZ hyperelongation persists through meiosis but does not affect
@@
       White arrowheads mark rescued Cep290 distribution for comparison.
-    \item Quantification of Cep290 and Ana1 lengths from control, \sigd{} and $\beta$\textsubscript{2}t-YFP-Sktl; \sigd{} from (A).
+    \item Quantification of Cep290 and Ana1 lengths from control, \sigd{} from (A) and $\beta$\textsubscript{2}t-YFP-Sktl; \sigd{} ($n$ = 100).
     \item \textit{sktl}$^{2.3}$ clones exhibit TZ hyperelongation (white arrowheads). Cilia are marked using
-      Unc-GFP. The plot on the right shows quantification of Unc-GFP lengths in control, \textit{sktl}$^{2.3}$ and \sigd{}
-      spermatocytes at late G2 phase ($n$ >30).
+      Unc-GFP. The plot on the right shows quantification of Unc-GFP lengths in control ($n$ = 53), \textit{sktl}$^{2.3}$ ($n$ = 31) and \sigd{}  ($n$ = 51)
+      spermatocytes at late G2 phase.
     \item Phylogenetic tree of PIP5Ks showing conservation of cilium-associated functions.
@@
       Black arrows represent previous evidence of involvement in cilium-associated functions (from \citep{xu2016phosphatidylinositol}).
+      Black arrowhead indicates Sktl.
       Abbreviations: Cele (\textit{Caenorhabditis elegans}), Spur (\textit{Strongylocentrotus purpuratus}), Amel (\textit{Apis mellifera}), Aaeg (\textit{Aedes aegypti}), Dana (\textit{Drosophila ananassae}), Dmel (\textit{Drosophila melanogaster}), Hsap (\textit{Homo sapiens}), Mmus (\textit{Mus musculus}), Xtro (\textit{Xenopus tropicalis}), Cint (\textit{Ciona intestinalis}), Scer (\textit{Saccharomyces cerevisiae}).
@@
       Insets show phase-contrast images corresponding to the region shown in the fluorescence images.
-    \item Cep290 is unable to detach and migrate from the basal body at the onset of axoneme assembly in \sigd{} spermatids.
+    \item Cep290 is unable to detach and migrate from the basal body at the onset of axoneme assembly in \sigd{} spermatids (white arrowhead).
       Insets show phase contrast images corresponding to the region shown in the fluorescence images, with the
@@
       Images were chosen to demonstrate the variety in Cep290 distribution.
-      White arrowheads mark TZ-distal Ana1 localization.
-    \item Quantification of Cep290 lengths in Taxol-treated control and \sigd{} cells from (D).
+      Yellow arrowheads mark TZ-distal Ana1 localization.
+    \item Quantification of Cep290 lengths in Taxol-treated control and \sigd{} cells from (D) ($n$ is between 30 and 40).
       % Inset shows distribution of regression coefficients (i.e. effects of Taxol and SigD on Cep290 length) from a fully Bayesian analysis.
@@
   \end{linenumbers}
+
+    \section*{List of Abbreviations}
+    \begin{tabular}{ll}
+       \sigd{} & SigD driven by the male germline-specific $\beta$\textsubscript{2}-tubulin promoter \\
+       \PIP{} & phosphatidylinositol 4,5-bisphosphate \\
+      PIP & phosphoinositide, also known as phosphatidylinositol phosphate \\
+       TZ & transition zone \\
+       BB & basal body \\
+       PM & plasma membrane \\ 
+       \textit{onr} & \textit{onion rings} (an allele of \textit{exo84})
+    \end{tabular}
 \end{doublespacing}
 
-\bibliography{bibttc}
+%\bibliography{bibttc}
+\printbibliography
 

### 2018-04-06 latex/paper.tex
Remove biblatex usage
Final edits from Brill's suggestions

@@
 \usepackage{charter}
-% \usepackage[charter]{mathdesign} % I hate how charter greeks look
-%\usepackage[numbers]{natbib}
+%\usepackage[charter]{mathdesign} % I hate how charter greeks look
+\usepackage[numbers]{natbib}
 \usepackage{enumitem}
@@
 \graphicspath{{../figures/}}
-\usepackage[style=authoryear-icomp,maxbibnames=9,maxcitenames=2,backend=biber]{biblatex}
-%\bibliographystyle{unsrtapalike}
-%\bibliography{bibttc.bib}
-\addbibresource{\jobname.bib}
+\bibliographystyle{unsrtapalike}
+
 % title font size
@@
 
-\textbf{Keywords}: Phosphatidylinositol 4,5-bisphosphate, Skittles, Cep290, cilia, transition zone
+\textbf{Keywords}: PtdIns(4,5)P\textsubscript{2}, Skittles, Cep290, cilia, transition zone, basal body
 
@@
     \section*{Abstract}
-    Cilia are sensory organelles that are essential for human development
+    Cilia are cellular antennae that are essential for human development
     and physiology.
@@
     We also report that the \textit{onion rings} (\textit{onr}) allele
-    of Drosophila Exo84
+    of Drosophila \textit{exo84}
     decouples TZ hyperelongation from loss of cilium-plasma membrane tethering.
@@
     During TZ maturation, its structure and protein
-    composition change, allowing for
+    constituents change, allowing for
     establishment of a compartmentalized space, bounded by the ciliary membrane
     and the TZ, where assembly of the axoneme, a microtubule-based structure
-    that forms the core of cilia,
+    that forms the ciliary core,
     and signalling can occur.
@@
     male germline \citep{wei2008depletion, fabian2010phosphatidylinositol}.
-    \PIP{}, one of seven different phosphoinositides (PIPs) present in eukaryotes,
+    \PIP{}, which is one of seven different phosphoinositides (PIPs) present in eukaryotes,
     localizes primarily to the PM, where it is required for
@@
     and ion channels involved in mechanotransduction in Drosophila \citep{park2015ciliary}.
-    In light of the current understanding of the role
-    for \PIP{} as a modulator of cilium function,
+    In light of the current understanding of \PIP{} as a modulator of cilium function,
     we sought to investigate the cause of defects we had observed
@@
     were caused by aberrant TZ function,
-    we examined localization of fluorescently-tagged
-    centriolar/BB protein
+    we examined localization of fluorescently-tagged versions of the
+    core centriolar/BB protein
     Ana1 (CEP295 homolog) \citep{goshima2007genes, blachon2009proximal}
-    and conserved TZ protein Cep290 \citep{basiri2014migrating}
+    and the conserved TZ protein Cep290 \citep{basiri2014migrating}
     during early steps of cilium assembly.
@@
     marker GFP-PACT \citep{basto2006flies}
-    is similar in controls and \sigd{} \citep{wei2008depletion}.
+    is similar, in controls and \sigd{} \citep{wei2008depletion}.
     In contrast, TZ proteins Chibby (Cby) \citep{enjolras2012drosophila} and
@@
     % 
-    \subsection*{The type I PIP kinase (PIPKI) Skittles (Sktl) regulates TZ length}
+    \subsection*{The type I PIP kinase Skittles regulates TZ length}
     Although \PIP{} is its major substrate in eukaryotic cells \textit{in vivo}
@@
     physiologically relevant phenotype due to decreased \PIP{},
-    we attempted to rescue it by
+    we attempted to rescue this phenotype by
     co-expressing \sigd{} with
@@
 
-    Vertebrate PIPKI$\gamma$ is important for cilium formation in cultured cells
+    Vertebrate type I PIP kinase PIPKI$\gamma$ is important for cilium formation in cultured cells
     \citep{xu2016phosphatidylinositol}.
@@
     and are not orthologous to specific vertebrate PIPKI isoforms (Figure 2D).
-    Sktl has diverged more than its paralog PIP5K59B, and seems
+    Sktl has diverged more than its paralog PIP5K59B and seems
     to be functionally related to PIPKI$\gamma$
@@
     BBs and migrating along axonemes despite
-    axoneme elongation (Figure 1E) and cell elongation
-    (Figures 3A and 3B).
-    The previously reported ``comet-shaped'' Unc-GFP localization in \sigd{}
+    axoneme and cell elongation
+    (Figures 1E, 3A and 3B).
+    Indeed, the previously reported ``comet-shaped'' Unc-GFP localization in \sigd{}
     \citep{wei2008depletion}
@@
     a subset of cilia (<5\%) in \sigd{}
-    contained puncta of the core centriolar protein Ana1 at the distal
+    contained puncta of Ana1 at the distal
     tips of TZs (Figure 3C).
@@
     Taxol-treated controls did not exhibit TZ-distal Ana1 puncta ($p$ <0.01 at 5\% penetrance).
-    Fluorescently-tagged pericentriolar protein Asterless (CEP152 homolog)
+    Fluorescently-tagged Asterless (CEP152 homolog), a pericentriolar protein
     \citep{blachon2008drosophila, dzhindzhev2010asterless},
@@
     at the PM initially, they were unable to maintain
-    membrane connections, and were rendered cytoplasmic (Figure 4B and C) similar to TZs in
+    membrane connections, and were rendered cytoplasmic (Figure 4B and C), similar to TZs in
     \textit{dila; cby} mutants.
@@
     Our results suggest that the exocyst, and Exo84 in particular, regulates
-    cilium-membrane associations, similar to \PIP{}, and that TZ hyperelongation and loss of
-    membrane-cilium association are genetically separable phenotypes.
+    cilium-PM associations, similar to \PIP{}, and that TZ hyperelongation and loss of
+    cilium-PM association are genetically separable phenotypes.
 
     \section*{Discussion}
-    The process of maturation of a TZ from a nascent form to a fully functional one,
+    The process of maturation of a TZ from a nascent form to a fully functional state,
     leading ultimately to axoneme assembly and ciliary signalling,
@@
     \citep{reiter2012base, gonccalves2017ciliary}.
-    In the Drosophila male germline, TZ maturation occurs during the
-    extended G2 phase in mature primary spermatocytes prior to meiosis, and can be readily
-    observed by an increase in TZ length using fluorescence microscopy.
-    Our results suggest that normal execution of this process
+    Our results indicate that normal execution of this process
     requires \PIP{} and that depletion of \PIP{} induces TZs to
@@
     Because both Cby and Mks1 are hyperelongated in \sigd{} cells,
-    \PIP{} seems to regulate TZ length independently of an effect on Cby or Mks1 recruitment.
+    \PIP{} regulates TZ length independently of an effect on Cby or Mks1 recruitment.
 
@@
     or membrane association.
-    The presence of TZ-distal Ana1 puncta in \sigd{} cells, without an increase
+    The presence of TZ-distal Ana1 puncta in \sigd{} cells, without the increase
     in BB length seen in \textit{cep290} mutants lacking a functional TZ barrier,
@@
     \citep{blachon2008drosophila, dzhindzhev2010asterless}, did not
-    exhibit this TZ-distal localization, possibly due to different dynamics of Ana1 and Asl
-    loading onto centrioles \citep{fu2016conserved, saurya2016drosophila} and the
+    exhibit this TZ-distal localization, possibly due to differences dynamics of Ana1 and Asl
+    loading onto centrioles \citep{fu2016conserved, saurya2016drosophila} or the
     more peripheral nature of Asl within the centriole \citep{blachon2008drosophila}.
@@
     Stocks expressing $\beta$\textsubscript{2}t::\textit{Styp}\textbackslash{SigD} (chromosome \textit{3}) and
-    $\beta$\textsubscript{2}t::YFP-Sktl (chromosome \textit{2}) were described previously \citep{wei2008depletion}.
+    $\beta$\textsubscript{2}t::YFP-Sktl (chromosome \textit{2}) were described previously \citep{wei2008depletion, wong2005pip2}.
     GFP-Exo70 was cloned into the low-level expression vector \textit{tv3} \citep{wong2005pip2}
@@
     The following primary antibodies were used for immunofluorescence
-    at the indicated concentrations ---
+    at the indicated concentrations: 
     chicken anti-GFP IgY (abcam), 1:1000;
@@
     a Zeiss Axioplan 2 epifluorescence microscope
-    or Nikon A1R scanning confocal microscope (SickKids imaging facility).
+    or a Nikon A1R scanning confocal microscope (SickKids imaging facility).
 
@@
     We are grateful to Brian Ciruna for insightful discussions,
-    B{\'e}n{\'e}dicte Durand for providing (at the time of experiments)
+    B{\'e}n{\'e}dicte Durand, Tomer Avidor-Reiss, Antoine Guichet and Maurice Kernan for providing
     unpublished fly stocks, and to
@@
     \item \sigd{} expression induces hyperelongation of the TZ proteins Chibby (Cby) and Mks1 in late G2 phase (white arrowheads).
-    \item TZ hyperelongation persists through meiosis but does not affect
+    \item TZ hyperelongation persists through meiosis (white arrowhead) but does not affect
       axoneme outgrowth. Acetylated tubulin (AcTub) labels the axoneme.
@@
     \item Expression of full-length Sktl can suppress \sigd{}-induced TZ hyperelongation in a cilium-autonomous manner.
-      Images were chosen to demonstrate varying levels of rescue of Cep290-GFP length in YFP-Sktl; SigD.
+      Images were chosen to demonstrate varying levels of rescue of Cep290-GFP length in $\beta$\textsubscript{2}t-YFP-Sktl; \sigd{}.
       White arrowheads mark rescued Cep290 distribution for comparison.
     \item Quantification of Cep290 and Ana1 lengths from control, \sigd{} from (A) and $\beta$\textsubscript{2}t-YFP-Sktl; \sigd{} ($n$ = 100).
-    \item \textit{sktl}$^{2.3}$ clones exhibit TZ hyperelongation (white arrowheads). Cilia are marked using
-      Unc-GFP. The plot on the right shows quantification of Unc-GFP lengths in control ($n$ = 53), \textit{sktl}$^{2.3}$ ($n$ = 31) and \sigd{}  ($n$ = 51)
-      spermatocytes at late G2 phase.
+    \item \textit{sktl}$^{2.3}$ clones exhibit TZ hyperelongation (white arrowheads), as marked by
+      Unc-GFP (left). Quantification of Unc-GFP lengths in control ($n$ = 53), \textit{sktl}$^{2.3}$ ($n$ = 31) and \sigd{}  ($n$ = 51)
+      spermatocytes at late G2 phase (right).
     \item Phylogenetic tree of PIP5Ks showing conservation of cilium-associated functions.
-      The scale bar (bottom) represents expected amino acid substitutions per site and branch support values are shown in red (a value of 1 indicates maximum support).
+      Scale bar (bottom) represents expected amino acid substitutions per site. Branch support values are shown in red (a value of 1 indicates maximum support).
       Black arrows represent previous evidence of involvement in cilium-associated functions (from \citep{xu2016phosphatidylinositol}).
@@
     \item Treatment of control and \sigd{} cells with the microtubule stabilizing drug Taxol.
-      Images were chosen to demonstrate the variety in Cep290 distribution.
-      Yellow arrowheads mark TZ-distal Ana1 localization.
+      Images demonstrate the variety in Cep290 distribution.
+      Yellow arrowheads mark TZ-distal Ana1.
     \item Quantification of Cep290 lengths in Taxol-treated control and \sigd{} cells from (D) ($n$ is between 30 and 40).
@@
     \begin{enumerate}[label={(\Alph*)}, nolistsep]
-    \item Cells expressing \sigd{} fail to maintain plasma membrane-cilium tethering despite initially anchoring to the plasma membrane.
-      The plasma membrane is marked with CellMask, a cell impermeable dye.
-    \item \textit{onr} mutants do not maintain plasma membrane-cilium tethering.
     \item Cells mutant for \textit{onr} do not display hyperelongated acetylated tubulin signal at the cilium (white arrowhead).
       Acetylated tubulin marks the axoneme, which colocalizes with the TZ in spermatocytes \citep{pratt2016drosophila}.
-    \item GFP-tagged Exo70 localizes to basal bodies in spermatocytes.
+    \item Cells expressing \sigd{} fail to maintain cilium-PM tethering despite initially anchoring to the PM.
+      The PM is marked with CellMask, a cell impermeable dye.
+    \item \textit{onr} mutants do not maintain PM-cilium tethering.
+    \item GFP-tagged Exo70 localizes to BBs in spermatocytes.
     \end{enumerate}
@@
 
-%\bibliography{bibttc}
-\printbibliography
+\bibliography{bibttc}
+%\printbibliography
 

### 2018-04-07 latex/paper.tex
Minor edits from me

@@
     This occurs concomitantly with anchoring of cilia to the plasma membrane (PM),
-    microtubule remodelling within the TZ \citep{gottardo2013cilium},
+    microtubule remodelling within the TZ \citep{riparbelli2013unique, gottardo2013cilium},
     and establishment of a
@@
 
-    Vertebrate type I PIP kinase PIPKI$\gamma$ is important for cilium formation in cultured cells
+    Vertebrate type I PIP kinase PIPKI$\gamma$ has previously been shown to be important for cilium formation in cultured cells
     \citep{xu2016phosphatidylinositol}.
@@
     % 
-    \subsection*{Hyperelongated transition zones exhibit signs of functional defects}
+    \subsection*{Hyperelongated transition zones exhibit functional defects}
     We next sought to examine whether TZ hyperelongation due to SigD expression
@@
     Taxol has been hypothesized to disrupt TZ maturation
-    by inhibiting microtubule remodelling in the Drosophila male germline \citep{riparbelli2012assembly, riparbelli2013unique}.
+    by inhibiting microtubule remodelling in the Drosophila male germline \citep{riparbelli2013unique}.
     Similar to \sigd{},
@@
     Male flies homozygous for the \textit{onion rings}
-    (\textit{onr}) mutant of Drosophila Exo84 are sterile and exhibit defects
+    (\textit{onr}) mutant of Drosophila \textit{exo84} are sterile and exhibit defects
     in cell elongation and polarity
@@
     with some cells showing cilium-autonomous suppression,
-    suggesting Skittles might function \textit{in situ} to regulate TZ length.
+    suggesting Sktl might function \textit{in situ} to regulate TZ length.
     In humans, \textit{PIPKI$\gamma$} is linked to lethal congenital contractural
@@
     \subsection*{Statistical methods}
-    Statistical analysis and graphing was performed using R (version 3.4)
-    \citep{r}.
+    Statistical analysis and graphing was performed using R (version 3.4).
     A Gaussian jitter was applied when plotting
@@
     We are grateful to Brian Ciruna for insightful discussions,
-    B{\'e}n{\'e}dicte Durand, Tomer Avidor-Reiss, Antoine Guichet and Maurice Kernan for providing
-    unpublished fly stocks, and to
+    to B{\'e}n{\'e}dicte Durand, Tomer Avidor-Reiss, Antoine Guichet and Maurice Kernan for providing
+    fly stocks, and to
     B{\'e}n{\'e}dicte Durand and Bill Trimble
-    for comments on the manuscript.
+    for critical comments on the manuscript.
     This research was supported by a grant from the Canadian Institutes for
@@
     A.G. and J.A.B. conceived the project.
-    A.G. performed all the experiments and analysis, and wrote the manuscript.
+    A.G. performed all the experiments and analyses, and wrote the manuscript.
     L.F. generated GFP-Exo70 flies.
@@
       spermatocytes at late G2 phase (right).
-    \item Phylogenetic tree of PIP5Ks showing conservation of cilium-associated functions.
+    \item Phylogenetic tree of PIP5Ks showing evolutionary conservation of cilium-associated functions.
       Scale bar (bottom) represents expected amino acid substitutions per site. Branch support values are shown in red (a value of 1 indicates maximum support).
@@
     \begin{enumerate}[label={(\Alph*)}, nolistsep]
-    \item GFP-tagged Unc is unable to detach from the basal body and migrate in spermatids expressing \sigd{} (white arrowhead).
+    \item Unc-GFP is unable to detach from the basal body and migrate in spermatids expressing \sigd{} (white arrowhead).
       Cell elongation in spermatids is concomitant with elongation of the mitochondrial derivative (dark organelles in the phase-contrast images).
@@
     \bigskip
-    \textbf{\itshape Figure 4. The \textit{onion rings} (\textit{onr}) allele of Exo84 decouples TZ hyperlongation from loss of plasma membrane contacts.}
+    \textbf{\itshape Figure 4. The \textit{onion rings} (\textit{onr}) allele of \textit{exo84} decouples TZ hyperlongation from loss of plasma membrane contacts.}
     \begin{enumerate}[label={(\Alph*)}, nolistsep]
-    \item Cells mutant for \textit{onr} do not display hyperelongated acetylated tubulin signal at the cilium (white arrowhead).
+    \item \textit{onr} mutant cells do not display hyperelongated acetylated tubulin signal at the cilium (white arrowhead).
       Acetylated tubulin marks the axoneme, which colocalizes with the TZ in spermatocytes \citep{pratt2016drosophila}.
